### 2015-10-26 paper/main.tex
added skeleton latex source

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage[letterpaper,margin=0.65in]{geometry}
\usepackage[ansinew]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{color}
\usepackage{amssymb}
\usepackage[normalem]{ulem}
\usepackage{natbib}
\usepackage{url}
\usepackage{placeins}
\usepackage{times}

% By default the URLs are put in typewriter type in the body and the
% bibliography of the document when using the \url command.  If you are
% using many long URLs you may want to uncommennt the next line so they
% are typeset a little smaller.
\renewcommand{\UrlFont}{\small\tt}

\def\aap{{A\&A}}
\def\AaA{{A\&A}}
\def\AJ{{AJ}}
\def\aj{{AJ}}
\def\ApJ{{ApJ}}
\def\apj{{ApJ}}
\def\apjl{{ApJL}}
\def\ApJL{{ApJL}}
\def\ApJSupp{{ApJS}}
\def\MN{{MNRAS}}
\def\mnras{{MNRAS}}
\def\pasp{{PASP}}
\def\jcap{JCAP}
\def\pasj{{PASJ}}
\def\nat{Nature}
\def\ARAA{{ARA\&A}}
\def\apjs{{ApJS}}
\def\araa{{ARA\&A}}
\def\apss{{Ap\&SS}}
\def\cjaa{{ChJAA}}
\def\aaps{{A\&AS}}

\newcommand{\eg}{{e.g., }}
\newcommand{\ie}{{i.e., }}

\pdfminorversion=5

\title[Deep Learning]{Deep Learning for Source Classification}

\author[E. J. Kim \& R. J. Brunner]{
  Edward J.~Kim$^1$\thanks{jkim575@illinois.edu},
  Robert J.~Brunner$^{2,3,4}$ \\
$^1$Department of Physics, University of Illinois, Urbana, IL 61801 USA\\
$^2$Department of Astronomy, University of Illinois, Urbana, IL 61801 USA\\
$^3$Department of Statistics, University of Illinois, Champaign, IL 61820 USA\\
$^4$National Center for Supercomputing Applications, Urbana, IL 61801 USA}

\begin{document}

\date{\today}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}

\maketitle

\label{firstpage}
\begin{abstract}
Deep learning.
\end{abstract}

\begin{keywords}
methods: data analysis -- methods: statistical -- surveys -- stars: statistics
-- galaxies:statistics.
\end{keywords}

\section{Introduction}
  \label{section:introduction}

\section{Methods}
  \label{section:methods}

\section{Data}
  \label{section:data}

\section{Results and Discussion}
  \label{section:results_and_discussion}

\section{Conclusions}
  \label{section:conclusions}

\section*{Acknowledgements}

We thank XXXX.

Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
Participating Institutions, the National Science Foundation, and the U.S.
Department of Energy Office of Science. The SDSS-III web site is
http://www.sdss3.org/.

SDSS-III is managed by the Astrophysical Research Consortium for the
Participating Institutions of the SDSS-III Collaboration including the
University of Arizona, the Brazilian Participation Group, Brookhaven National
Laboratory, Carnegie Mellon University, University of Florida, the French
Participation Group, the German Participation Group, Harvard University, the
Instituto de Astrofisica de Canarias, the Michigan State/Notre Dame/JINA
Participation Group, Johns Hopkins University, Lawrence Berkeley National
Laboratory, Max Planck Institute for Astrophysics, Max Planck Institute for
Extraterrestrial Physics, New Mexico State University, New York University,
Ohio State University, Pennsylvania State University, University of Portsmouth,
Princeton University, the Spanish Participation Group, University of Tokyo,
University of Utah, Vanderbilt University, University of Virginia, University
of Washington, and Yale University.

This paper uses data from the 
VIMOS Public Extragalactic Redshift Survey (VIPERS).
VIPERS has been performed using the ESO Very Large Telescope, under the "Large
Programme" 182.A-0886. The participating institutions and funding agencies are
listed at http://vipers.inaf.it/.

This research uses data from the VIMOS VLT Deep Survey, obtained from the VVDS
database operated by Cesam, Laboratoire d'Astrophysique de Marseille, France.

\footnotesize{
\bibliographystyle{mn2e}
\bibliography{sg_paper}
}

\bsp

\label{lastpage}

\end{document}

### 2016-05-17 paper/main.tex
update draft paper

@@
-\documentclass[useAMS,usenatbib]{mn2e}
-\usepackage[letterpaper,margin=0.65in]{geometry}
+% Basic setup. Most papers should leave these options alone.
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
+
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+%\usepackage{newtxtext,newtxmath}
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+\usepackage{mathptmx}
+%\usepackage{txfonts}
+
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+
+% Only include extra packages if you really need them. Common packages are:
+\usepackage{savesym}
+\usepackage{amsmath}
+\savesymbol{iint}
+\usepackage{txfonts}
+\restoresymbol{TXF}{iint}
+
+\usepackage{graphicx}	% Including figure files
+%\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
 \usepackage[ansinew]{inputenc}
 \usepackage{amsfonts}
-\usepackage{amsmath}
 \usepackage{graphicx}
@@
 \usepackage{color}
-\usepackage{amssymb}
 \usepackage[normalem]{ulem}
@@
 \usepackage{placeins}
-\usepackage{times}
+\usepackage{caption}
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
 
@@
 
-\title[Deep Learning]{Deep Learning for Source Classification}
+\title[Star-galaxy Classification Using ConvNets]{Star-galaxy Classification Using Convolutional Neural Networks}
 
-\author[E. J. Kim \& R. J. Brunner]{
-  Edward J.~Kim$^1$\thanks{jkim575@illinois.edu},
-  Robert J.~Brunner$^{2,3,4}$ \\
+\author[E. J. Kim and R. J. Brunner]{
+  Edward J.~Kim$^1$\thanks{jkim575@illinois.edu} and Robert J.~Brunner$^{2}$ \\
 $^1$Department of Physics, University of Illinois, Urbana, IL 61801 USA\\
-$^2$Department of Astronomy, University of Illinois, Urbana, IL 61801 USA\\
-$^3$Department of Statistics, University of Illinois, Champaign, IL 61820 USA\\
-$^4$National Center for Supercomputing Applications, Urbana, IL 61801 USA}
+$^2$Department of Astronomy, University of Illinois, Urbana, IL 61801 USA}
 
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2015}
+
+% Don't change these lines
 \begin{document}
-
-\date{\today}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}
-
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \maketitle
 
-\label{firstpage}
 \begin{abstract}
-Deep learning.
+Most existing star-galaxy classifiers use the reduced summary information from catalogs,
+requiring careful feature extraction and selection.
+The latest advances in machine learning using deep convolutional neural networks
+allow a machine to automatically learn the features directly from data,
+minimizing need for input from human experts.
+We present a star-galaxy classification framework that uses
+a deep convolutional neural network (ConvNet) directly on the raw pixel values.
+Using data from the Sloan Digital Sky Survey (SDSS) and
+the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS),
+we demonstrate that ConvNet is able to produce accurate and well-calibrated
+probabilistic classifications that are competitive with
+conventional machine learning techniques.
+Future advances in deep learning may bring more success in currently ongoing and
+forthcoming photometric surveys, such as the Dark Energy Survey (DES) and
+the Large Synoptic Survey Telescope (LSST), because deep neural networks require
+very little feature engineering by hand.
 \end{abstract}
@@
 
-\section{Methods}
-  \label{section:methods}
+Currently ongoing and forthcoming large-scale photometric surveys,
+such as the Dark Energy Survey (DES) and the Large Synoptic Survey Telescope (LSST),
+aim to collect photometric data for hundreds of millions to billions of
+stars and galaxies.
+Due to the sheer volume of data, it is not possible for human experts to
+manually classify them,
+and the separation of photometric catalogs into stars and galaxies has to be automated.
+Furthermore, any classification approach must be probabilistic in nature.
+A fully probabilistic classifier enables a user to adopt probability cuts
+to obtain a pure sample for population studies,
+or to optimize the allocation of observing time by selecting objects for follow-up.
+However, ideally, the probability estimates themselves would be retained for all sources
+and used in subsequent analyses to improve or enhance a particular
+measurement~\citep{ross2011ameliorating,seo2012acoustic}.
+
+With machine learning, we can use algorithms to automatically create
+accurate source catalogs with well-calibrated posterior probabilities.
+Machine learning techniques have been a popular tool
+in many areas of astronomy~\citep{ball2007robust,ball2008robust,
+banerji2010galaxy,
+carrascokind2013tpz,carrascokind2014somz,carrascokind2014exhausting,
+ivezic2014statistics,
+kamdar2016machine1,kamdar2016machine2}.
+Artificial neural networks were first applied to the problem of star-galaxy
+classification in the work of \citet{odewahn1992automated},
+which has become a core part of the astronomical image processing software
+\texttt{SExtractor}~\citep{bertin1996sextractor}.
+Other successfully implemented examples of applying machine learning to
+the star-galaxy classification problem include decision 
+trees~\citep{weir1995automated,suchkov2005census,ball2006robust,sevilla2015effect}
+, Support Vector Machines~\citep{Fadely2012}, and
+classifier combination strategies~\citep{kim2015hybrid}.
+
+Almost all star-galaxy classifiers published in the literature use
+the reduced summary information available from astronomical catalogs.
+Constructing catalogs requires careful engineering and considerable domain expertise
+to transform the raw pixel values of an image to suitable features,
+such as magnitudes or shape information of an object.
+In a branch of machine learning called deep learning,
+features are not designed by human experts;
+they are learned from data by deep neural networks.
+Deep learning has been applied successfully to galaxy morphological
+classification in Sloan Digital Sky Survey~\citep[SDSS;][]{dieleman2015rotation}
+and Cosmic Assembly Near-infrared Deep Extragalactic Legacy
+Survey~\citep[CANDELS;][]{huertas2015catalog} and to photometric redshift
+estimation~\citep{hoyle2015measuring},
+but it has never been applied to the problem of source classification.
+
+In this paper, we present a star-galaxy classification framework
+that uses a convolutional neural network (ConvNet) model directly on the images
+from SDSS and Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS).
+We compare its performance with a standard machine learning technique
+that uses the reduced summary information from catalogs,
+and demonstrate that our ConvNet model is able to produce accurate and
+well-calibrated probabilistic classifications with very little feature
+engineering by hand.
+In Section~\ref{section:data}, we describe the data sets used in this paper
+and the pre-processing steps for preparing the image data sets.
+We provide a brief overview of deep learning and ConvNets
+in Section~\ref{section:deep_learning}, and
+discuss our strategy for preventing overfitting in Section~\ref{section:overfitting}.
+In Section~\ref{section:tpc}, we describe a state-of-the-art tree-based
+machine learning algorithm, to which the performance of our ConvNet model is
+compared.
+We present the main results of our ConvNet model in
+Section~\ref{section:results_and_discussion}, and
+we outline our conclusions in Section~\ref{section:conclusions}.
 
@@
 
+\subsection{Sloan Digital Sky Survey}
+  \label{section:sdss}
+
+The Sloan Digital Sky Survey~\citep[SDSS;][]{york2000sloan}
+phases I--III obtained photometric data in five bands:
+$u$, $g$, $r$, $i$, and $z$,
+covering 14,555 square degrees, more than one-third of the entire sky.
+The resulting catalog contains photometry of over 300 million stars galaxies
+with a limiting magnitude of $r \approx 22$,
+making the SDSS one of the largest sky surveys ever undertaken.
+The SDSS also conducted an expansive spectroscopic follow-up of
+more than three million stars and galaxies~\citep{eisenstein2011sdss}.
+In this paper, we use a subset of the photometric and spectroscopic data
+contained within the Data Release 12~\citep[DR12;][]{alam2015eleventh},
+which is publicly available through the online CasJobs
+server~\citep{li2008casjobs}~\footnote{http://skyserver.sdss.org/casjobs/}.
+
+Using the CasJobs server, we randomly select 65,000 stars and galaxies.
+We exclude some bad photometric observations as follows.
+We consider only objects whose $r$ band magnitude is less than 40;
+there are no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
+the half-light radius in the $r$ band is less than 30 arc seconds
+as measured by the exponential and de Vaucouleurs light profiles;
+the error on the spectroscopic redshift measurement is less than 0.1; and
+the spectroscopic redshift is less than 2.
+
+To create training images,
+we obtain the image FITS files for SDSS fields containing these objects
+in five photometric bands: $u$, $g$, $r$, $i$, and $z$.
+We use the astrometry information in the FITS headers
+in the \texttt{Montage}~\footnote{http://montage.ipac.caltech.edu/} software
+to align each image to the reference ($r$-band) image.
+We then use \texttt{SExtractor} to find the pixel positions of
+the 65,000 objects we have selected,
+and to center each object in the cutout image.
+We also convert the flux values to inverse hyperbolic sine magnitudes
+\citep[also known as luptitudes;][]{lupton1999modified}.
+Finally, in order to account for the effect of galactic dust,
+galactic extinction corrections in magnitudes are applied
+following \cite{schlegel1998maps}.
+In the end, we have cutout images of size $48\times48$ pixels
+with luptitude values in each pixel.
+We note that we have experimented with increasing the pixel dimensions to
+$60\times60$ and $72\times72$ pixels, but do not find noticeable
+improvement in the performance of our model.
+
+In the end, we have 17 344 stars and 47 656 galaxies available
+for the training and testing processes.
+We randomly split the objects into training, validation, and test sets
+of 40 000, 10 000, and 15 000, respectively.
+We note that we perform a blind test, and the test set is not used in any
+to train or calibrate the algorithms.
+
+\subsection{Canada-France-Hawaii Telescope Lensing Survey}
+
+We also use photometric data from
+the Canada-France-Hawaii Telescope Lensing Survey
+\cite[CFHTLenS\footnote{http://www.cfhtlens.org/};][]
+{heymans2012cfhtlens,erben2013cfhtlens,hildebrandt2012cfhtlens}.
+This catalog consists of more than twenty five million objects
+with a limiting magnitude of $i_{\text{AB}} \approx 25.5$. 
+It covers a total of 154 square degrees
+in the four fields (named W1, W2, W3, and W4)
+of CFHT Legacy Survey~\citep[CFHTLS;][]{gwyn2012canada}
+observed in the five photometric bands:
+$u$, $g$, $r$, $i$, and $z$.
+
+We have cross-matched reliable spectroscopic galaxies from
+the Deep Extragalactic Evolutionary Probe Phase 2~
+\citep[DEEP2;][]{davis2003science,newman2013deep2},
+the Sloan Digital Sky Survey Data Release 10~\citep[SDSS-DR10]{alam2015eleventh},
+the VIsible imaging Multi-Object Spectrograph (VIMOS)
+Very Large Telescope (VLT) Deep Survey~
+\citep[VVDS;][]{le2005vimos,garilli2008vimos}, and
+the VIMOS Public Extragalactic Redshift
+Survey~\citep[VIPERS;][]{garilli2014vimos}.
+We have selected only sources with very secure
+redshifts and no bad flags (quality flags -1, 3, and 4 for DEEP2;
+quality flag 0 for SDSS; quality flags 3, 4, 23, and 24 for VIPERS
+and VVDS).
+
+We obtain FITS images for each 1 square degree CFHTLenS pointing
+that contains objects with spectroscopic labels.
+We create cutout images of size $96\times96$ pixels by using a similar method
+to that described in Section~\ref{section:sdss}.
+Finally, images are downscaled to $48\times48$ pixels
+to reduce reduce computational cost.
+
+In the end, we have 8 545 stars and 57 843 galaxies available
+for the training and testing processes.
+We randomly split the objects into training, validation, and test sets of size
+40 000, 10 000, and 13 278, respectively.
+
+\section{Deep Learning}
+  \label{section:deep_learning}
+
+\subsection{Neural Networks}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[]{0.49\linewidth}
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/neuron.pdf}
+    \caption{}
+    \label{fig:neuron_a}
+  \end{subfigure}
+  \begin{subfigure}[]{0.49\linewidth}
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/network.pdf}
+    \caption{}
+    \label{fig:neuron_b}
+  \end{subfigure}
+  \caption{
+    (a) A mathematical model of a biological neuron.
+    (b) A schematic diagram of a neural network with one hidden layer
+    of two neurons and one output layer with two neurons.
+    }
+\end{figure*}
+
+A neuron in the human brain receives signals from other neurons through
+synaptic connections.
+If the combination of these signals exceeds a certain threshold,
+the neuron will fire and send a signal to other neurons.
+Intelligence is believed to be the collective effect of
+approximately $10^{11}$ neurons firing.
+An artificial neuron in most artificial neural networks is represented
+as a mathematical function that models a biological neural structure
+(Figure~\ref{fig:neuron_a}).
+Let $\mathbf{x}$ be a vector of inputs to a given neuron,
+$\mathbf{w}$ be a vector of weights, and
+$\mathbf{b}$ be the bias.
+Then, the output of the neuron is
+\begin{equation}
+  y = \sigma \left( \mathbf{w} \cdot \mathbf{x} + b \right),
+  \label{eq:neuron_output}
+\end{equation}
+where $\sigma$ is the activation function (or \textit{non-linearity}).
+
+The sigmoid function, $\sigma(x)=1/\left(1+e^{-x}\right)$,
+has frequently been used as activation function, but it has recently fallen out of favor,
+and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$ is almost always used instead.
+The most popular non-linearity at present, however, is the rectified linear unit
+\citep[ReLU;][]{nair2010rectified}, $\sigma(x)=\max(0, x)$,
+ReLUs generally allow much faster
+training of deep neural networks with many layers.
+However, ReLU units can sometimes result in dead neurons whose output is always zero.
+To mitigate this problem, we use leaky ReLUs that have a small negative slope
+in the negative region,
+\begin{equation}
+  \sigma(x) =
+    \begin{cases}
+      x & \mbox{if } x \geq 0 \\
+      0.01x & \mbox{if } x < 0.
+    \end{cases}
+\end{equation}
+
+Many deep learning models use feedforward neural network architectures with multiple layers,
+where each neuron in one layer is connected to the neurons of the subsequent layer.
+A schematic representation is shown in Figure~\ref{fig:neuron_b}.
+All layers except the input and output layers are conveniently called hidden layers.
+With multiple hidden layers, deep neural networks can model complex nonlinear
+relationships, and they have had great success in multimedia tasks where humans traditionally
+outperformed computers: speech recognition, language processing, and image classification.
+
+The goal of learning is to find a set of weights and biases such that
+the output from the network $\mathbf{y}=\left\{ y_1, y_2, \dots, y_n \right\}$
+approximates the desired output
+$\hat{\mathbf{y}}=\left\{\hat{y}_1, \hat{y}_2, \dots, \hat{y}_n \right\}$
+as closely as possible for all input $\mathbf{x}$.
+We can formulate this as the minimization of a loss function $L(\mathbf{x},\hat{\mathbf{y}})$
+over the training data.
+In this work, we use \textit{cross-entropy},
+\begin{equation}
+  L(y, \hat{y}) = -\hat{y} \log_2 y - (1 - \hat{y}) \log_2(1 - y),
+\end{equation}
+where $\hat{y}$ is the actual truth value (\eg 0 or 1)
+and $y$ is the probability prediction made by the model.
+We compute the loss function by taking the average of all cross-entropies in the sample.
+Given $N$ samples, the loss function becomes
+\begin{equation}
+  L(y, \hat{y}) = - \frac{1}{N} \sum_{i=1}^{N} \hat{y}_i  \log_2 y_i
+    + (1 - \hat{y}_i)  \log_2 (1 - \hat y_i).
+\end{equation}
+where $\hat{y}_i$ is the truth value and probability estimate of the $i$-th data,
+respectively.
+
+To find the weights $\mathbf{w}$ and biases $\mathbf{b}$ which minimize the loss,
+we use a technique called \textit{gradient descent},
+where we the following rules to update the parameters in each layer $j$:
+\begin{align}
+  \mathbf{w}_j &\rightarrow
+  \mathbf{w}^{\prime}
+  = \mathbf{w}_j - \eta \frac{\partial L}{\partial \mathbf{w}_j} \\
+  \mathbf{b}_j &\rightarrow
+  \mathbf{b}^{\prime}
+  = \mathbf{b}_j - \eta \frac{\partial L}{\partial \mathbf{b}_j},
+  \label{eq:gradeitn_descent}
+\end{align}
+where $\eta$ is a small, positive number known as the \textit{learning rate}.
+A common approach to speed up training is to split the training data
+into mini-batches and compute the gradients in
+Equation~\ref{eq:gradeitn_descent} for each mini-batch separately instead of
+the entire training data.
+This results in much faster convergence, as training examples are usually correlated
+and the gradient computed from a randomly chosen mini-batch is a good approximation
+of the overall gradient.
+We define an \textit{epoch} as a single, complete pass through the training data,
+and full training usually requires many epochs.
+At the end of each epoch, we evaluate the loss function on the validation set,
+and the model that minimizes the loss is chosen as the best model.
+
+\subsection{Convolutional Neural Networks}
+
+The Convolutional neural network~\citep[ConvNet;][]{fukushima1980neocognitron,lecun1998gradient}
+is a type of deep, feedforward neural network
+that has recently become the dominant approach in the computer vision community.
+In a typical ConvNet, the first few stages are composed of two types of layers: 
+convolutional layers and pooling layers.
+
+The input to a convolutional layer is an image with a certain number of color channels
+or \textit{feature maps}.
+To produce output feature maps, we convolve each feature map with a set of weights
+called \textit{filters},
+and apply a non-linearity such as ReLU to the weighted sum of these convolutions.
+Different feature maps use different sets of filters,
+but all neurons in a feature map share the same set of filters.
+Mathematically, we replace the dot product in Equation~\ref{eq:neuron_output}
+with a sum of convolutions. The $k$-th feature map is given by
+\begin{equation}
+\mathbf{y}^k = \sigma \left( \sum_{j} \mathbf{w}_j^k \ast \mathbf{x}_j + b^k \right),
+\end{equation}
+where we sum over the set of filters,
+$\ast$ is the convolution operator, and $\mathbf{w}_j^k$ represent the filters.
+
+A typical pooling layer computes the maximum of a local $2\times2$ patch in a feature map.
+Since the pooling layer aggregates the activations of neighboring units from the previous layer,
+it reduces the dimensionality of the feature maps and
+makes the model invariant to small shifts and distortions.
+Two or more layers of convolution and pooling are stacked,
+followed by more convolutional and fully-connected layers.
+
+\subsection{Neural Network Architecture}
+
+\begin{table*}
+  \centering
+  \caption{Summary of hyperparameters. Note that pooling layers have no learnable parameters.}
+  \label{table:hyperparamters}
+  \begin{tabular}{ccccccc}
+    \hline
+    type            & filters & filter size & padding & non-linearity & initial weights & initial biases \\
+    \hline
+    convolutional   & 32          & $5\times5$  & -       & leaky ReLU    & orthogonal      & 0.1            \\
+    convolutional   & 32          & $3\times3$  & 1       & leaky ReLU    & orthogonal      & 0.1            \\
+    pooling         & -           & $2\times2$  & -       & -             & -               & -              \\
+    convolutional   & 64          & $3\times3$  & 1       & leaky ReLU    & orthogonal      & 0.1            \\
+    convolutional   & 64          & $3\times3$  & 1       & leaky ReLU    & orthogonal      & 0.1            \\
+    convolutional   & 64          & $3\times3$  & 1       & leaky ReLU    & orthogonal      & 0.1            \\
+    pooling         & -           & $2\times2$  & -       & -             & -               & -              \\
+    convolutional   & 128         & $3\times3$  & 1       & leaky ReLU    & orthogonal      & 0.1            \\
+    convolutional   & 128         & $3\times3$  & 1       & leaky ReLU    & orthogonal      & 0.1            \\
+    convolutional   & 128         & $3\times3$  & 1       & leaky ReLU    & orthogonal      & 0.1            \\
+    pooling         & -           & $2\times2$  & -       & -             & -               & -              \\
+    fully-connected & 2048        & -           & -       & leaky ReLU    & orthogonal      & 0.01            \\
+    fully-connected & 2048        & -           & -       & leaky ReLU    & orthogonal      & 0.01            \\
+    fully-connected & 2           & -           & -       & softmax       & orthogonal      & 0.01            \\
+    \hline
+  \end{tabular}
+\end{table*}
+
+We present the overall architecture of our ConvNet model in Table~\ref{table:hyperparamters}.
+The network consists of eleven trainable layers.
+The first convolutional layer filters the $5\times44\times44$ input image
+(\ie $44\times44$ images in five bands $ugriz$) with 32 square filters of size $5\times5\times5$.
+The leaky ReLU non-linearity is applied to the output of the first convolutional layer
+(and all subsequent layers), and the second convolutional layer filters it
+with 32 filters of $32\times3\times3$.
+In the second convolutional layer (and all subsequent convolutional layers),
+we pad the input with zeros spatially on the border
+(\ie the zero-padding is 1 pixel for $3\times3$ convolutional layers)
+such that the spatial resolution is preserved after convolution.
+Max-pooling with filters of size $2\times2$ follows the second convolutional layer.
+A stack of six additional convolutional layers, all with filters of size $3\times3$,
+is followed by three fully-connected layers.
+The first two fully-connected layers have 2048 channels each,
+and the third performs binary classification.
+
+The output of the final fully-connected layer is fed to a softmax function.
+The softmax function is given by
+\begin{equation}
+  P (y_i \mid \mathbf{x}) = 
+    \frac{ e^{ \mathbf{x} \cdot \mathbf{w}_{y_i} } }
+    { \sum_{k} e^{ \mathbf{x} \cdot \mathbf{w}_k } },
+\end{equation}
+where we interpret its output as the posterior probability that an object is a galaxy
+(or a star).
+We note that we could also try to solve a regression problem, \eg
+by normalizing the output values that the network produces for each class.
+However, we find that solving a regression problem instead of using
+the softmax function results in significantly worse performance.
+
+In addition to hyperparamter optimization, we have explored more than 100 different architectures
+and have found that the architecture described in this section provides
+the best performance on the validation data.
+For example, the architecture of \cite{krizhevsky2012imagenet}
+uses relatively large receptive fields ($11\times11$) in the first convolutional layers.
+\citet{zeiler2014visualizing} and \cite{dieleman2015rotation}
+also use large receptive fields of $7\times7$ and $6\times6$
+in the first convolution layer, respectively.
+However, we find that using a receptive field larger than $5\times5$ in the first
+convolutional layer leads to worse performance.
+This result is in agreement with \citet{simonyan2014very},
+which features an extremely homogeneous architecture that only performs
+$3\times3$ convolutions.
+Using a large receptive field instead of a stack of multiple $3\times3$ convolutions
+leads to a shallower network, and it is often preferable to increase
+the depth by using smaller receptive fields.
+However, we find that replacing the first layer with
+a stack of two $3\times3$ convolutional layers increases the validation error,
+but we still follow \citet{simonyan2014very} and add many
+$3\times3$ convolutions (with zero-padding) in the remaining layers.
+
+\subsection{Training}
+
+The choice of momentum, learning rate, and initial weights is crucial
+for achieving high predictive performance and speeding up the learning
+process~\citep{sutskever2013importance}.
+To train our models, we use mini-batch gradient descent with a batch size of 128
+and Nesterov momentum~\citep{bengio2013advances} of 0.9.
+We initialize the learning rate $\eta$ at 0.003 for all layers and
+decrease it linearly with the number of epochs 
+from 0.003 to 0.0001 over 750 epochs.
+We also initialize the weights in each layer with random orthogonal initial 
+conditions~\citep{saxe2013exact}.
+We use a slightly positive value $b=0.1$ for all biases.
+We find initializing biases to a small constant value helps eliminate dead neurons
+by ensuring that all ReLU neurons fire in the beginning.
+We note that our network takes about 40 hours to train the networks on a NVIDIA Tesla K40 GPU.
+
+\section{Reducing Overfitting}
+  \label{section:overfitting}
+
+Our convolution neural network has $11\times10^6$ learnable parameters,
+while there are only $5\times10^4$ images in the training set.
+As a result, the model is very likely to \emph{overfit} without regularization.
+In this section, we describe the techniques used to combat overfitting.
+
+\subsection{Data Augmentation}
+  \label{sec:data_augmentation}
+
+One common method to combat overfitting is to artificially increase
+the number of training data by using label-preserving transformations.
+Each image is transformed as follows:
+\begin{itemize}
+\item{Rotation: 
+Rotating an image does not change whether the object is a star or a galaxy.
+We exploit this rotational symmetry and randomly rotate each image by a multiple of
+$90^{\circ}$. }
+
+\item{Reflection:
+We flip each image horizontally with a probability of 0.5 to exploit mirror symmetry. }
+\item{Translation:
+We also have translational symmetry in the images.
+Given an image of size $48\times48$ pixels, we extract a random contiguous crop
+of size $44\times44$.
+Each cropping is equivalent to randomly shifting a $44\times44$ image by up to 4 pixels
+vertically and horizontally. }
+\item{Gaussian noise:
+We introduce random Gaussian noise to each pixel values
+by using a similar method to \cite{krizhevsky2012imagenet}. }
+\end{itemize}
+These data augmentation schemes add almost no computational cost,
+as they are performed on the CPU while the GPU is training the ConvNets on images.
+
+\subsection{Dropout}
+
+We use a regularization technique called dropout~\citep{hinton2012improving}
+in the fully-connected layers.
+Dropout consists of randomly setting to zero
+the output of each hidden neuron of the previous layer with probability 0.5.
+The weights of the remaining neurons are multiplied by 0.5 to preserve
+the scale of input values to the next layer.
+Since a neuron can be removed at any time, it cannot rely on the presence of other neurons
+in the same layer and is forced to learn more robust features.
+
+\subsection{Model Combination}
+  \label{sec:bmc}
+
+To make final classifications,
+we use our ConvNet model to make 64 sets of predictions for
+64 transformations of the input images:
+4 rotations, 4 horizontal translations, and 4 vertical translations
+(with random horizontal reflections).
+Although we use an identical network architecture for all transformations,
+we consider each set of predictions as separate results from different models.
+Finally, we use a model combination technique known as
+Bayesian Model Combination~\citep[BMC;][]{Monteith2011}, which
+uses Bayesian principles to generate an ensemble combination of different models.
+Although the data augmentation step~\ref{sec:data_augmentation} should
+make our ConvNet model invariant to these types of transformations,
+we find that applying BMC still results in a significant decrease in validation error.
+
+The posterior probability that a source is a star is given by
+\begin{equation} \label{eq:p_star_bmc}
+  P \left(S | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right)
+  = \sum_{e \in \bmath{E}} P \left(S | \bmath{x}, \bmath{M}, e \right)
+  P \left(e | \bmath{D} \right),
+\end{equation}
+where $\bmath{D}$ is the data set,
+and $e$ is an element in the ensemble space $\bmath{E}$ of possible model combinations.
+By Bayes' Theorem, the posterior probability of $e$ given $\bmath{D}$ is given by
+\begin{equation} \label{eq:p_ensemble}
+  P \left(e | \bmath{D} \right)
+  = \frac{P \left(e \right)}{P \left(\bmath{D} \right)}
+  \prod_{d \in \bmath{D}} P \left( d | e \right)
+  \propto P \left(e\right) \prod_{d \in \bmath{D}} P \left(d | e \right).
+\end{equation}
+Here, $P\left(e \right)$ is the prior probability of $e$,
+which we assume to be uniform.
+The product of $P\left(d | e\right)$ is
+over all individual data $d$ in the training data $\bmath{D}$,
+and $P\left(\bmath{D}\right)$ is merely a normalization factor
+and not important.
+For probabilistic classifiers,
+we can directly use the probabilistic predictions
+and write Equation~\ref{eq:p_ensemble} as
+\begin{equation} \label{eq:p_ensemble_prob}
+  P \left( e | \bmath{D} \right) \propto 
+  P \left( e \right) \prod_{i=0}^{N-1}
+  \hat{y}_i y_i + 
+  \left(1 - \hat{y}_i\right) \left(1 - y_i\right).
+\end{equation}
+
+Although the space $\bmath{E}$ of potential model combinations
+is in principle infinite,
+we can produce a reasonable finite set
+of potential model combinations by using sampling techniques.
+In our implementation,
+the weights of each combination of the base classifiers
+is obtained by sampling from a Dirichlet distribution.
+We first set all alpha values of a Dirichlet distribution to unity.
+We then sample this distribution $q$ times
+to obtain $q$ sets of weights.
+For each combination,
+we assume a uniform prior and
+calculate $P\left(e|\bmath{D}\right)$ using
+Equation~\ref{eq:p_ensemble_prob}.
+We select the combination with the highest $P\left(e|\bmath{D}\right)$,
+and update the alpha values by
+adding the weights of the most probable combination
+to the current alpha values.
+The next $q$ sets of weights are drawn
+using the updated alpha values.
+
+We continue the sampling process until
+we reach a predefined number of combinations,
+and finally use Equation~\ref{eq:p_star_bmc} to compute
+the posterior probability that a source is a star (or a galaxy).
+In this paper, we use a $q$ value of three,
+and 1,000 model combinations are considered.
+
+\section{Trees for Probabilistic Classifications}
+  \label{section:tpc}
+
+To compare the performance of ConvNets with
+machine learning algorithms that use standard photometric features,
+we use a machine learning framework called
+Trees for Probabilistic Classifications (TPC).
+Although a complete description of TPC is beyond the scope of this paper,
+we provide a brief description in this section.
+For more details, we refer the reader to
+\cite{carrascokind2013tpz} and \cite{kim2015hybrid}.
+
+TPC is a parallel, supervised machine learning algorithm
+that uses prediction trees and random forest 
+techniques~\citep{breiman1984classification, breiman2001random}
+to produce a star-galaxy classification.
+TPC is a part of a publicly available software package called
+\textsc{MLZ}\footnote{http://lcdm.astro.illinois.edu/code/mlz.html}
+(Machine Learning for Photo-$z$).
+
+TPC uses classification trees,
+a type of prediction trees that are designed to
+provide a classification or predict a discrete category.
+Prediction trees are built by asking a sequence of questions
+that recursively split the data into branches
+until a terminal leaf is created
+that meets a stopping criterion
+(\eg a minimum leaf size).
+The optimal split dimension is decided by
+choosing the attribute that maximizes
+the \textit{Information Gain} ($I_G$), which is defined as
+
+\begin{equation} \label{eq:information_gain}
+  I_G \left(D_{\rmn{node}}, X\right)
+  = I_d \left( D_{\rmn{node}} \right)
+  - \sum_{x \in \rmn{values}(X)}
+  \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|}
+  I_d \left( D_{\rmn{node}, x} \right),
+\end{equation}
+
+\noindent
+where $D_{\rmn{node}}$ is the training data in a given node,
+$X$ is one of the possible dimensions (\eg magnitudes or colors)
+along which the node is split, and
+$x$ are the possible values of a specific dimension $X$.
+$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data
+and the number of objects in a given subset $x$ within the current node,
+respectively.
+$I_d$ is the impurity degree index,
+and TPC can calculate $I_d$
+from any of the three standard different impurity indices:
+\textit{information entropy}, \textit{Gini impurity},
+and \textit{classification error}.
+In this work, we use the information entropy,
+which is defined similarly to the thermodynamic entropy:
+
+\begin{equation}
+  I_d \left( D \right)
+  = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right),
+\end{equation}
+
+\noindent
+where $f_g$ is the fraction of galaxies in the training data.
+At each node in our tree,
+we scan all dimensions to identify the split point that
+maximizes the information gain as defined by Equation~\ref{eq:information_gain},
+and select the attribute that maximizes the impurity index overall.
+
+In a technique called random forest,
+we create bootstrap samples
+(\ie $N$ randomly selected objects with replacement)
+from the input training data
+by sampling repeatedly from the magnitudes and colors
+using their measurement errors.
+We use these bootstrap samples to construct
+multiple, uncorrelated prediction trees
+whose individual predictions are aggregated to produce
+a star-galaxy classification for each source.
+
+We train two TPC models on the SDSS data set using different sets of
+attributes.
+The first model, which we denote $\rmn{TPC}_{\rmn{phot}}$, is trained with
+only nine photometric attributes:
+the extinction-corrected model magnitudes in five bands
+($u$, $g$, $r$, $i$, $z$) and their corresponding colors
+($u-g$, $g-r$, $r-i$, $i-z$).
+The second model, which we denote $\rmn{TPC}_{\rmn{morph}}$, is trained with
+the concentration parameter in each band in addition to the magnitudes and
+colors, for a total of fifteen dimensions.
+The concentration is defined as the difference between the cmodel
+and PSF magnitude,
+\ie $\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
+The SDSS pipeline uses a parametric method based on the concentration,
+\ie an object is classified as a galaxy if $\rmn{concentration}>0.145$.
+We find that the concentration is an excellent morphological feature
+for star-galaxy separation, and including more morphological features
+does not show noticeable improvement in performance.
+The concentration is a good example of carefully handcrafted feature extraction,
+and we show in Section~\ref{section:results_and_discussion}
+that ConvNets do not require such feature engineering.
+
+We also train two models on the CFHTLenS data set.
+$\rmn{TPC}_{\rmn{phot}}$ is trained with 
+the five magnitudes and their corresponding colors,
+$u$, $g$, $r$, $i$, $z$, $u-g$, $g-r$, $r-i$, and $i-z$.
+Since the CFHTLenS catalog does not provide the concentration parameter,
+$\rmn{TPC}_{\rmn{morph}}$ uses
+\texttt{SExtractor}'s \texttt{FLUX\_RADIUS} (the half-light radius),
+\texttt{A\_WORLD} (the semi-major axis), \texttt{B\_WORLD} (the semi-minor axis)
+for morphological features, in addition to
+the five magnitudes and their corresponding colors,
+for a total of twelve dimensions.
+
 \section{Results and Discussion}
   \label{section:results_and_discussion}
+
+In this section, we present the classification performance of
+our ConvNet model and compare it with the performance of TPC.
+
+\subsection{Classification Metrics}
+
+Probabilistic classification models can be considered as
+functions that output a probability estimate of each source
+to be in one of the classes (\eg a star or a galaxy).
+The simplest way to way to use the probability output is to
+convert it into a class label by using a threshold (a probability cut).
+Although many studies often choose the threshold by setting it to a fixed value,
+\eg $p_\rmn{cut} = 0.5$ \citep[\eg][]{henrion2011bayesian, Fadely2012},
+choosing $0.5$ as a threshold is not the best choice
+for an unbalanced data set, where galaxies outnumber stars.
+Furthermore, setting a fixed threshold ignores the operating condition 
+(\eg science requirements, stellar distribution, misclassification costs)
+where the model will be applied.
+
+\subsubsection{Receiver Operating Characteristic Curve}
+
+When we have no information about the operating condition
+when evaluating the performance of classifiers,
+there are effective tools such as
+the Receiver Operating Characteristic (ROC) curve
+\citep*{swets2000better}.
+An ROC curve is a graphical plot that illustrates the true positive rate
+versus the false positive rate of a binary classifier
+as its classification threshold is varied.
+The Area Under the Curve (AUC) summarizes the curve information
+in a single number,
+and can be used as an assessment of the overall performance.
+
+\subsubsection{Completeness and Purity}
+
+In astronomical applications,
+the operating condition usually translates to
+the completeness and purity requirements of the star or galaxy sample.
+We define the galaxy \textit{completeness}
+$c_g$ (also known as recall or sensitivity) as
+the fraction of the number of true galaxies classified as galaxies
+out of the total number of true galaxies,
+\begin{equation}
+c_g = \frac{N_g}{N_g + M_g},
+\end{equation}
+
+\noindent
+where $N_g$ is the number of true galaxies classified as galaxies,
+and $M_g$ is the number of true galaxies classified as stars.
+We define the galaxy \textit{purity} $p_g$ (also known as precision
+or positive predictive value)
+as the fraction of the number of true galaxies classified as galaxies
+out of the total number of objects classified as galaxies, 
+\begin{equation}
+p_g = \frac{N_g}{N_g + M_s},
+\end{equation}
+
+\noindent
+where $M_s$ is the number of true stars classified as galaxies.
+Star completeness and purity are defined in a similar manner.
+
+One of the advantages of a probabilistic classification is
+that the threshold can be adjusted to produce
+a more complete but less pure sample,
+or a less complete but more pure one.
+We can compare the performance of different classification techniques
+by assuming an arbitrary operating condition.
+For example, weak lensing science measurements
+of the DES require $c_g > 0.960$ and $p_g > 0.778$
+to control both the statistical and systematic errors
+on the cosmological parameters,
+and $c_s > 0.250$ and $p_s > 0.970$
+for stellar Point Spread Function (PSF) calibration
+\citep{soumagnac2013star}.
+Although these values will likely be different
+for the science cases of the CFHTLenS data,
+we adopt these values to compare the classification performance
+at a reasonable operating condition.
+Thus, we compute $p_{g}$ at $c_g=0.960$
+and $c_{s}$ at $p_s=0.250$.
+
+\subsubsection{Mean Squared Error}
+
+We also use the mean squared error
+(MSE; also known as Brier score~\citep{brier1950verification})
+as a performance metric. We define MSE as
+\begin{equation} \label{eq:mse}
+  \rmn{MSE} = \frac{1}{N} \sum^{N}_{i=1}
+  \left( y_i - \hat{y}_i \right)^2,
+\end{equation}
+The MSE can be considered as both a score function that quantifies
+how well a set of probabilistic predictions are calibrated,
+or a loss function.
+
+\subsubsection{Calibration Error}
+
+A fully probabilistic classifier predicts not only the class label,
+but also its confidence level on the prediction.
+In a well-calibrated classifier, the posterior class probability estimates
+should coincide with the proportion of objects that truly belong to a certain class.
+Probability \textit{calibration curves}~\citep[or reliability curves;][]{degroot1983comparison}
+are often used to display this relationship,
+where we bin the probability estimates and plot the
+fraction of positive examples versus the predicted probability in each bin
+(see Figures~\ref{fig:clens_calibration_conv} and fig:\textcolor{red}{xxx}).
+
+The problem with binning approach is either too few or too many bins
+can distort the evaluation of calibration performance.
+Thus, we adopt a calibration measure based on
+overlapping binning~\citep{caruana2004data}.
+We order the predicted values $P_\rmn{class}$ and
+put the first 1000 elements in the first bin.
+We calculate the true probability $P_\rmn{gal}$ by counting the true galaxies
+in this bin.
+The calibration error for this bin is $\mid P_\rmn{gal} - P_\rmn{class} \mid$.
+We then repeat this for the second bin (2 to 1001),
+the third bin (3 to 1002), and so on, and average the binned calibration errors.
+Thus, the overall calibration error is given by
+\begin{equation}
+\rmn{CAL} = \frac{1}{N-s} \sum_{b=1}^{N-s} \sum_{i=b}^{b+s-1}
+\bigg| P_{\rmn{class},i} - \frac{\sum_{i=b}^{b+s-1} P_{\rmn{gal},i}}{s} \bigg|
+\end{equation}
+where $s=1000$ is the bin length.
+
+\begin{table}
+  \caption{The definition of the classification performance metrics.}
+  \centering
+  \begin{tabular}{c l}
+  \hline
+  Metric & Meaning \\
+  \hline
+  AUC & Area under the Receiver Operating Curve \\
+  MSE & Mean squared error \\
+  $c_g$ & Galaxy completeness \\
+  $p_g$ & Galaxy purity \\
+  $c_s$ & Star completeness \\
+  $p_s$ & Star purity \\
+  $p_g(c_g=x)$ & Galaxy purity at $x$ galaxy completeness \\
+  $p_s(c_s=x)$ & Star purity at $x$ star completeness \\
+  $CAL$ & Calibration error with overlapping binning \\
+  $\mid\Delta N_g\mid / N_g$ & Absolute error in number of galaxies\\
+  \hline
+  \end{tabular}
+  \label{table:metrics}
+\end{table}
+
+\subsubsection{Number of galaxies}
+
+Ideally, the probabilistic output of a classifier would be used in subsequent
+scientific analyses.
+For example, one can weight each object by the probability that it is a galaxy
+when measuring auto-correlation functions of luminous
+galaxies~\citep{ross2011ameliorating}.
+In other words, given a well-calibrated classifier,
+instead of counting each galaxy equally, a galaxy could be
+counted as $P_{\rmn{class}}$, the probability estimate.
+This should, in principle, remove the contamination effect of stars.
+For a perfect classifier, we can count the number of galaxies by summing
+the values of $P_{\rmn{class}}$.
+Thus, we measure the reliability of the classifier output by the absolute error
+in the estimation of number of galaxies,
+\begin{equation}
+  \frac{\mid \Delta N_g \mid}{N_g} =
+  \frac{\big| N_g - \sum_{i=1}^{N} P_{\rmn{class}} \big|}{N_g}
+\end{equation}
+
+\subsection{CFHTLenS}
+  \label{sec:results_cfht}
+
+\begin{table*}
+  \caption{
+    A summary of the classification performance metrics
+    as applied to the CFHTLenS data.
+    The definition of the metrics is summarized in Table~\ref{table:metrics}.
+    The bold entries highlight the best performance values within each column.
+  }
+  \centering
+  \begin{tabular}{l c c c c c c}
+    \hline
+    classifier & AUC & MSE & $p_{g}(c_g=0.96)$ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ \\
+    \hline
+    ConvNet                       & \textbf{0.9948} & 0.0112          & \textbf{0.9972} & 0.8971          & \textbf{0.0197}  & \textbf{0.0029} \\
+    TPC${}_{\rmn{morph}}$         & 0.9924          & \textbf{0.0109} & 0.9963          & \textbf{0.9268} & 0.0245           & 0.0056 \\
+    TPC${}_{\rmn{phot}}$          & 0.9876          & 0.0189          & 0.9927          & 0.8044          & 0.0266           & 0.0101 \\
+    \hline
+  \end{tabular}
+  \label{table:clens_metrics}
+\end{table*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/clens_mag.pdf}
+  \caption{Galaxy completeness and star purity values as a function
+           of the $i$-band magnitude
+           as estimated by the kernel density estimation (KDE) method
+           for the differential counts.
+           The top panel shows the histogram with a bin size of 0.1 mag
+           and the KDE for objects in the test set.
+           The second panel shows the fraction of stars estimated by KDE
+           as a function of magnitude.
+           The bottom two panels compare the galaxy purity and star completeness
+           values for ConvNet (red solid line),
+           $\rmn{TPC}_{\rmn{morph}}$ (blue dashed line),
+           and $\rmn{TPC}_{\rmn{phot}}$ (yellow dashed line)
+           as functions of magnitude.
+           The $1 \sigma$ confidence bands are estimated by
+           bootstrap sampling.}
+  \label{fig:clens_mag}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/clens_integrated.pdf}
+  \caption{
+    Galaxy purity and star completeness as functions of the $i$-band
+    magnitude for the integrated counts. The upper panel compres the galaxy
+    purity values for ConvNet (red solid line), $\rmn{TPC}_{\rmn{morph}}$
+    (blue dashed line), and $\rmn{TPC}_{\rmn{phot}}$ (yellow dashed line).
+    The lower panel compares the star completeness.
+    The $1 \sigma$ error bars are computed following the method
+    of \citet{paterno2004calculating} to avoid the unphysical
+    errors of binomial or Poisson statistics.
+    }
+  \label{fig:clens_integrated}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/clens_g_r.pdf}
+  \caption{Similar to Figure~\ref{fig:clens_mag}
+           but as a function of $g-r$ color.
+           The bin size of histogram in the top panel is 0.05.}
+  \label{fig:clens_g_r}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figures/clens_calibration_conv.pdf}
+  \caption{
+    Calibration curve for ConvNet as applied to the CFHTLenS data set.
+    $p_{\rmn{gal}}$ is the fraction of objects that are galaxies.
+    $p_{\rmn{conv}}$ is the probabilistic output generated by ConvNet.
+    The dashed line displays the relationship
+    $p_{\rmn{gal}} = p_{\rmn{conv}}$.
+    The $1 \sigma$ error bars are computed following the method
+    of \citet{paterno2004calculating}.
+    }
+  \label{fig:clens_calibration_conv}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figures/clens_calibration_tpc.pdf}
+  \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
+  \label{fig:clens_calibration_tpc}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/galaxy_original.pdf}
+    \caption{Input (5 bands$\times44\times44$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/galaxy_conv11.pdf}
+    \caption{Layer 1 (32 maps$\times40\times40$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/galaxy_conv21.pdf}
+    \caption{Layer 3 (64 maps$\times20\times20$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/galaxy_conv31.pdf}
+    \caption{Layer 6 (128 maps$\times10\times10$)}
+  \end{subfigure}
+  \caption{
+    (a) A sample $44\times44$ RGB image of a CFHTLenS galaxy.
+    The RGB image is created by mapping R $\rightarrow g$ band magnitude,
+    G $\rightarrow r$ band magnitude, and B $\rightarrow i$ band magnitude.
+    (b) Activations on the first convolutional layer when a $5\times44\times44$
+    image is fed into the network.
+    (c) Activations on the third convolutional layer.
+    (d) Activations on the sixth convolutional layer.
+    Each image in (a), (b), and (c) is a feature map corresponding to the
+    output for one of the learned features.
+    }
+  \label{fig:galaxy_activations}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/star_original.pdf}
+    \caption{Input (5 bands$\times44\times44$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/star_conv11.pdf}
+    \caption{Layer 1 (32 maps$\times40\times40$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/star_conv21.pdf}
+    \caption{Layer 3 (64 maps$\times20\times20$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/star_conv31.pdf}
+    \caption{Layer 6 (128 maps$\times10\times10$)}
+  \end{subfigure}
+  \caption{
+    Same as Figure~\ref{fig:galaxy_activations} but for a CFHTLenS star.
+    }
+  \label{fig:star_activations}
+\end{figure*}
+
+We present in Table~\ref{table:clens_metrics} a summary of the results obtained
+by applying ConvNet and TPC on the CFHTLenS data set.
+The bold entries highlight the best technique for any particular metric.
+ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ in four metrics (AUC, $p_g$, CAL,
+and $|\Delta N_g|/N_g$), while $\rmn{TPC}_{\rmn{morph}}$ performs better in
+two metrics (MSE and $c_g$).
+It is not surprising that $\rmn{TPC}_{\rmn{phot}}$ performs significantly worse
+than both ConvNet and $\rmn{TPC}_{\rmn{phot}}$,
+as morphology is critical in separating stars from galaxies.
+This suggests that ConvNet is able to learn the morphological features
+automatically from the images.
+
+In Figure~\ref{fig:clens_mag}, we compare the galaxy completeness
+and star purity values for ConvNet and TPC as functions of $i$-band magnitude
+for the differential counts.
+We use the kernel density estimation~\citep[KDE][]{silverman1986density}
+with the Gaussian kernel.
+As the first panel shows, KDE is able to smooth the fluctutions in the distribution
+without binning.
+While ConvNet shows a slightly better performance than $\rmn{TPC}_{\rmn{morph}}$
+in galaxy purity, the star completeness plots for ConvNet and TPC
+are nearly identical.
+Again, $\rmn{TPC}_{\rmn{phot}}$ performs significantly worse than both
+ConvNet and TPC, and this suggests that ConvNets are able to learn
+the shape information automatically from the images.
+We note that, at these operating conditions ($c_g=0.96$, $p_s=0.97$),
+both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ outperform the
+star-galaxy classification provided by
+the CFHTLenS pipeline~\cite{hildebrandt2012cfhtlens} across all magnitudes.
+We do not show the CFHTLenS classifications to avoid cluttering the plots.
+
+In Figure~\ref{fig:clens_integrated}, we show the overall galaxy purity
+and star completeness values as functions of magnitude for the integrated
+counts.
+ConvNet is able to mantain a galaxy purity of 0.9972 up to $i\sim24.5$,
+while the galaxy purity of $\rmn{TPC}_{\rmn{morph}}$ drops to 0.9963.
+However, $\rmn{TPC}_{\rmn{morph}}$ performs better than ConvNet
+in terms of star completeness, maintaining a purity of 0.9252 up to
+$i\sim24.5$, while ConvNet drops to 0.8966.
+
+We also show the galaxy purity and star completeness values as functions of
+$g-r$ color in Figure~\ref{fig:clens_g_r}.
+$\rmn{TPC}_{\rmn{morph}}$ provides slightly better
+completeness and purity than ConvNet between $0.8 \la g-r \la 1.6$ while
+ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ or is similar to
+$\rmn{TPC}_{\rmn{morph}}$ in the remaining regions.
+
+Figure~\ref{fig:clens_calibration_conv} shows the calibration curve
+that compares $P_{\rmn{gal}}$,
+the fraction of objects that are galaxies (as determined from their spectra)
+to $P_{\rmn{conv}}$ the probabilistic output that our ConvNet model produces.
+The calibration curve is nearly diagonal, which implies that ConvNet
+is well-calibrated and we can treat $P_{\rmn{conv}}$ as the probability
+that an object is a galaxy.
+Figure~\ref{fig:clens_calibration_tpc} shows the calibration curve
+for the probabilistic output of TPC,
+which is apparently not as well-calibrated as ConvNet.
+These calibration curves visually confirm the results in
+Table~\ref{table:clens_metrics} that the calibration error
+of ConvNet is about 20\% lower than that of TPC.
+While probabilistic predictions can be further calibrated by using,
+\eg isotonic calibration~\citep{zadrozny2001obtaining},
+we do not consider additional probability calibration in this work.
+
+It is informative to visualize how an input image activates the neurons
+in the convolutional layers.
+Figures~\ref{fig:galaxy_activations} and \ref{fig:star_activations}
+show the activations of the network when images of a galaxy and a star
+are fed into the network.
+The size of feature maps decreases with depth, and layers near the
+input layer have fewer filters while the later layers have more.
+The low-level features
+
+When highly optimized features (\eg the $\rmn{concentration}$ of SDSS)
+are not readily available from the catalog, a ConvNet model becomes more
+attractive.
+
+\subsection{SDSS}
+  \label{sec:results_sdss}
+
+\begin{table*}
+  \caption{
+    A summary of the classification performance metrics
+    as applied to the SDSS data.
+  }
+  \centering
+  \begin{tabular}{l c c c c c c}
+    \hline
+    classifier & AUC & MSE & $p_{g}(c_g=0.96) $ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ \\
+    \hline
+    ConvNet               & 0.9952          & 0.0182          & 0.9915          & 0.9500          & \textbf{0.0243} & 0.0157          \\
+    TPC${}_{\rmn{morph}}$ & \textbf{0.9967} & \textbf{0.0099} & \textbf{0.9977} & \textbf{0.9810} & 0.0254          & \textbf{0.0044} \\
+    TPC${}_{\rmn{phot}}$  & 0.9886          & 0.0283          & 0.9819          & 0.8879          & 0.0316          & 0.0160 \\
+    \hline
+  \end{tabular}
+  \label{table:sdss_metrics}
+\end{table*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/sdss_mag.pdf}
+  \caption{Completeness and purity in the SDSS
+           as a function of the $r$-band magnitude for
+           the differential counts.}
+  \label{fig:sdss_mag}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/sdss_integrated.pdf}
+  \caption{Completeness and purity in the SDSS
+           as a function of the $r$-band magnitude
+           for the integrated counts.}
+  \label{fig:sdss_integrated}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/sdss_g_r.pdf}
+  \caption{Similar to Figure~\ref{fig:sdss_mag}
+           but as a function of $g-r$ color.
+           The bin size of histogram in the top panel is 0.05.}
+  \label{fig:sdss_g_r}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/sdss_calibration_conv.pdf}
+  \caption{Calibration curve for ConvNet as applied to the SDSS data set.}
+  \label{fig:sdss_calibration_conv}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/sdss_calibration_tpc.pdf}
+  \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
+  \label{fig:sdss_calibration_tpc}
+\end{figure}
+
+We have also trained and tested our ConvNet model on the SDSS data set, and
+we present in Table~\ref{table:sdss_metrics} the same six metrics for ConvNet,
+$\rmn{TPC}_{\rmn{morph}}$, and $\rmn{TPC}_{\rmn{phot}}$.
+The bold entries highlight the best technique for any particular metrics.
+In contrast with the CFHTLenS data set in the previous section,
+it is apparent that $\rmn{TPC}_{\rmn{morph}}$ outperforms ConvNet
+in all metrics except the $\rmn{CAL}$.
+Both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ still outperforms
+$\rmn{TPC}_{\rmn{phot}}$ in all six metrics by a significant amount.
+
+In Figure~\ref{fig:sdss_mag}, we compare the galaxy completeness
+and star purity values for ConvNet and TPC as functions of $i$-band magnitude
+for the differential counts.
+We note that $\rmn{TPC}_{\rmn{morph}}$ outperforms the star-galaxy
+classifier used by the SDSS pipeline (\ie an object is classifed as a galaxy
+if the concentration parameter is greater than 0.145) across all magnitudes.
+We do not show the SDSS classifications to avoid cluttering the plots.
+While ConvNet shows a similar but slighly worse performance than
+$\rmn{TPC}_{\rmn{morph}}$,
+the galaxy purity and star completeness values of ConvNet begin to
+drop at faint magnitudes $i \la 21$.
+Again, $\rmn{TPC}_{\rmn{phot}}$ performs significantly worse than both
+ConvNet and TPC at bright magnitudes.
+One reason that ConvNet fails to outperform $\rmn{TPC}_{\rmn{phot}}$,
+especially at faint magnitudes,
+might be its over-reliance on morphological features.
+Near a survey's limit, the measurement uncertainties generally increase,
+and morphology is not a reliable metric for star-galaxy classification.
+
+In Figure~\ref{fig:sdss_integrated}, we show the overall galaxy purity
+and star completeness values as functions of magnitude for the integrated
+counts.
+ConvNet is able to mantain a galaxy purity of 0.9915 up to $i\sim22.5$,
+while $\rmn{TPC}_{\rmn{morph}}$ provides a glaxay purity of 0.9977.
+$\rmn{TPC}_{\rmn{morph}}$ also outperforms ConvNet
+in terms of star completeness, maintaining a purity of 0.9810 up to
+$i\sim22.5$, while the star completeness of ConvNet drops to 0.9500.
+
+We also show the galaxy purity and star completeness values as functions of
+$g-r$ color in Figure~\ref{fig:sdss_g_r}.
+$\rmn{TPC}_{\rmn{morph}}$ provides slightly better
+completeness and purity than ConvNet between $0.8 \la g-r \la 1.6$ while
+ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ or is similar to
+$\rmn{TPC}_{\rmn{morph}}$ in the remaining regions.
+
+Figure~\ref{fig:sdss_calibration_conv} shows the calibration curve
+that compares $P_{\rmn{gal}}$,
+the fraction of objects that are galaxies (as determined from their spectra)
+to $P_{\rmn{conv}}$ the probabilistic output that our ConvNet model produces.
+The calibration curve is nearly diagonal, which implies that ConvNet
+is well-calibrated and we can treat $P_{\rmn{conv}}$ as the probability
+that an object is a galaxy.
+Figure~\ref{fig:sdss_calibration_tpc} shows the calibration curve
+for the probabilistic output of TPC,
+which is apparently not as well-calibrated as ConvNet.
+These calibration curves visually confirm the results in
+Table~\ref{table:sdss_metrics} that the calibration error
+of ConvNet is about 20\% lower than that of TPC.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+We have presented a convolutional neural network for classifying stars and
+galaxies in the SDSS and CFHTLenS photometric images.
+In the interest of scientific reproducibility, we make all our code available at
+\url{https://github.com/EdwardJKim/dl4astro}.  
+For the CFHTLenS data set, the network is able to provide a classification that
+is as accurate as a random forest algorithm (TPC), while the probability estimates of
+our ConvNet model appear to be better calibrated.
+When the same network architecture is applied to the SDSS data set,
+the network fails to outperform TPC,
+but the probabilities are still slightly better calibrated.
+The major advatange of ConvNets is that useful features are learned
+automatically from raw pixel values, while traditional machine learning
+algorithms require feature engineering as a separate process
+to provide produce accurate classifications.
+
+ConvNets have recently achieved record-breaking results in many image
+classification tasks~\citep{lecun2015deep} and have been quickly and widely
+adopted by the computer vision community.
+One of the main reasons for the success is that ConvNets are general-purpose
+algorithms that are applicable to a variety of problems without the need for
+designing a feature extractor.
+The lack of requirement for feature extraction is a huge advantage \eg
+when the task is to classify 1 000 classes in the ImageNet data
+set~\citep{russakovsky2015imagenet},
+as a good feature extractor for identifying images of cats would of little use
+for classifying sailboats, and it is impractical to design a feature extractor
+for each class.
+However, if there already exists a good feature extractor for the problem
+at hand, \eg the concentration parameter or the \texttt{SExtractor} software,
+conventional machine learning algorithms that are proven to be effective,
+such as TPC~\citep{carrascokind2013tpz, kim2015hybrid}, remain a viable option.
+As the "no free lunch" theorem~\citep{wolpert1996lack} states,
+there is no one model that works for every problem.
+For the CFHTLenS data set, our ConvNet model outperforms TPC trained on the
+output of \texttt{SExtractor}.
+Since the SDSS catalog provides the concentration paramter that is highly
+optmized for star-galaxy classification, TPC works better for SDSS.
+
+Although we used various techniques to combat overfitting,
+it is possible that our ConvNet model has overfit the data.
+Overfitting could explain why our ConvNet model with maximal information
+fails to significantly outperform a standard machine learning algorithm
+that uses the reduced summary information from catalogs.
+The most effective way to prevent overfitting would be to simply collect more training images
+with spectroscopic follow-up, as the performance of ConvNets apparently
+improves with more training data.
+However, spectroscopic observations are expensive and time-consuming,
+and it is unclear if sufficient training data will be available
+in future photometric surveys.
+If enough training data become available in DES or LSST, ConvNets
+become an attractive option because it can be applied immediately on raw images
+to produce well-calibrated posterior probabilities.
+
+Deep learning is a rapidly developing field and recent developments include
+improved network architectures.
+For future work, we plan to train more ConvNet variants, such as the
+Inception Module~\citep{szegedy2015going} and Residual network~\citep{he2015deep}.
+To improve the predictive performance,
+we have combined the predictions of different models across multiple
+transformations of the input images (Section~\ref{sec:bmc}).
+To further improve the performance, we could also train several networks
+with different architectures and combine the models.
+The winning solution of \cite{dieleman2015rotation}
+for the Galaxy Zoo challenge was based on a ConvNet model,
+and it required averaging many sets of predictions from models with different
+neural network architectures.
+It is likely that the performance will be improved by,
+not only training multiple network architectures,
+but also combining with different star-galaxy classifiers.
+In \citet{kim2015hybrid}, we combined a purely morphological classifier,
+a supervised machine learning method (TPC),
+an unsupervised machine learning method based on self-organizing maps,
+and a hierarchical Bayesian template fitting method, and
+demonstrated that our combination technique improves the overall
+performance over any individual classification method.
+ConvNets could be included as a different machine learning paradigm in this
+classifier combination framework to produce further improvements in
+predictive performance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Acknowledgements}
 
-We thank XXXX.
+We acknowledge support from the 
+National Science Foundation Grant No.\ AST-1313415.
+RJB acknowledges support as an Associate
+within the Center for Advanced Study at the University of Illinois.
+
+This work used the Extreme Science and Engineering Discovery Environment
+(XSEDE), which is supported by National Science Foundation grant number
+ACI-1053575.
+
+This work is based on observations obtained with MegaPrime/MegaCam, a
+joint project of CFHT and CEA/DAPNIA, at the Canada-France-Hawaii
+Telescope (CFHT) which is operated by the National Research Council
+(NRC) of Canada, the Institut National des Sciences de l'Univers of
+the Centre National de la Recherche Scientifique (CNRS) of France, and
+the University of Hawaii. This research used the facilities of the
+Canadian Astronomy Data Centre operated by the National Research
+Council of Canada with the support of the Canadian Space Agency.
+CFHTLenS data processing was made possible thanks to significant
+computing support from the NSERC Research Tools and Instruments grant
+program.
 
@@
 
-This paper uses data from the 
-VIMOS Public Extragalactic Redshift Survey (VIPERS).
-VIPERS has been performed using the ESO Very Large Telescope, under the "Large
-Programme" 182.A-0886. The participating institutions and funding agencies are
-listed at http://vipers.inaf.it/.
-
-This research uses data from the VIMOS VLT Deep Survey, obtained from the VVDS
-database operated by Cesam, Laboratoire d'Astrophysique de Marseille, France.
-
 \footnotesize{
-\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 \bibliography{sg_paper}
@@
 
-\bsp
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
+\end{document}
 
-\label{lastpage}
-
-\end{document}
+% End of mnras_template.tex

### 2016-05-17 paper/main.tex
add spread model reference

@@
 for each class.
-However, if there already exists a good feature extractor for the problem
-at hand, \eg the concentration parameter or the \texttt{SExtractor} software,
+However, when there already exists a good feature extractor for the problem
+at hand, \eg the concentration parameter, the weight-averaged
+\texttt{spread\_model} parameter from the Dark Energy
+Survey~\citep{desai2012blanco,crocce2016galaxy},
+or even the \texttt{SExtractor} software,
 conventional machine learning algorithms that are proven to be effective,

### 2016-05-17 paper/main.tex
put calibration curves side by side

@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figures/clens_calibration_conv.pdf}
+\begin{figure*}
+  \centering
+  \begin{minipage}[c]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figures/clens_calibration_conv.pdf}
     \caption{
@@
     \label{fig:clens_calibration_conv}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figures/clens_calibration_tpc.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[c]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{figures/clens_calibration_tpc.pdf}
     \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
     \label{fig:clens_calibration_tpc}
-\end{figure}
+  \end{minipage}
+\end{figure*}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{figures/sdss_calibration_conv.pdf}
+\begin{figure*}
+  \centering
+  \begin{minipage}[c]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figures/sdss_calibration_conv.pdf}
     \caption{Calibration curve for ConvNet as applied to the SDSS data set.}
     \label{fig:sdss_calibration_conv}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{figures/sdss_calibration_tpc.pdf}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[c]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figures/sdss_calibration_tpc.pdf}
     \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
     \label{fig:sdss_calibration_tpc}
-\end{figure}
+  \end{minipage}
+\end{figure*}
 

### 2016-05-17 paper/main.tex
update paper

@@
 \end{equation}
-where $\hat{y}_i$ is the truth value and probability estimate of the $i$-th data,
-respectively.
+where $\hat{y}_i$ and $y_i$ are the truth value and probability estimate of
+the $i$-th data, respectively.
 
@@
 we use a technique called \textit{gradient descent},
-where we the following rules to update the parameters in each layer $j$:
+where we use the following rules to update the parameters in each layer $j$:
 \begin{align}
@@
 At the end of each epoch, we evaluate the loss function on the validation set,
-and the model that minimizes the loss is chosen as the best model.
+and the model that minimizes the validation loss is chosen as the best model.
 
@@
 Thus, we compute $p_{g}$ at $c_g=0.960$
-and $c_{s}$ at $p_s=0.250$.
+and $c_{s}$ at $p_s=0.970$.
 
@@
 fraction of positive examples versus the predicted probability in each bin
-(see Figures~\ref{fig:clens_calibration_conv} and fig:\textcolor{red}{xxx}).
+(see Figures~\ref{fig:clens_calibration_conv} and \ref{fig:clens_calibration_tpc}).
 
@@
   \frac{\mid \Delta N_g \mid}{N_g} =
-  \frac{\big| N_g - \sum_{i=1}^{N} P_{\rmn{class}} \big|}{N_g}
+  \frac{\big| N_g - \sum_{i=1}^{N} P_{\rmn{class}} \big|}{N_g}.
 \end{equation}
@@
     \includegraphics[width=\textwidth]{figures/clens_calibration_tpc.pdf}
-    \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
+    \caption{Calibration curve for $\rmn{TPC}_{\rmn{morph}}$
+      as applied to the CFHTLenS data set.}
     \label{fig:clens_calibration_tpc}
@@
 star-galaxy classification provided by
-the CFHTLenS pipeline~\cite{hildebrandt2012cfhtlens} across all magnitudes.
-We do not show the CFHTLenS classifications to avoid cluttering the plots.
+the CFHTLenS pipeline~\citep{hildebrandt2012cfhtlens} over all magnitudes.
 
@@
 completeness and purity than ConvNet between $0.8 \la g-r \la 1.6$ while
-ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ or is similar to
-$\rmn{TPC}_{\rmn{morph}}$ in the remaining regions.
+ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ in the remaining regions.
 
@@
 that compares $P_{\rmn{gal}}$,
-the fraction of objects that are galaxies (as determined from their spectra)
-to $P_{\rmn{conv}}$ the probabilistic output that our ConvNet model produces.
+the fraction of objects that are galaxies (as determined from their spectra),
+to $P_{\rmn{conv}}$, the probabilistic output that our ConvNet model produces.
 The calibration curve is nearly diagonal, which implies that ConvNet
@@
 Figure~\ref{fig:clens_calibration_tpc} shows the calibration curve
-for the probabilistic output of TPC,
+for the probabilistic output of $\rmn{TPC}_{\rmn{morph}}$,
 which is apparently not as well-calibrated as ConvNet.
@@
 Table~\ref{table:clens_metrics} that the calibration error
-of ConvNet is about 20\% lower than that of TPC.
+of ConvNet is about 20\% lower than that of $\rmn{TPC}_{\rmn{morph}}$.
 While probabilistic predictions can be further calibrated by using,
@@
 The low-level features
-
-When highly optimized features (\eg the $\rmn{concentration}$ of SDSS)
-are not readily available from the catalog, a ConvNet model becomes more
-attractive.
 
@@
     \includegraphics[width=\textwidth]{figures/sdss_calibration_tpc.pdf}
-    \caption{Calibration curve for TPC as applied to the CFHTLenS data set.}
+    \caption{Calibration curve for $\rmn{TPC}_{\rmn{morph}}$
+      as applied to the SDSS data set.}
     \label{fig:sdss_calibration_tpc}
@@
 classifier used by the SDSS pipeline (\ie an object is classifed as a galaxy
-if the concentration parameter is greater than 0.145) across all magnitudes.
+if the concentration parameter is greater than 0.145) over all magnitudes.
 We do not show the SDSS classifications to avoid cluttering the plots.
@@
 $g-r$ color in Figure~\ref{fig:sdss_g_r}.
-$\rmn{TPC}_{\rmn{morph}}$ provides slightly better
-completeness and purity than ConvNet between $0.8 \la g-r \la 1.6$ while
-ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ or is similar to
-$\rmn{TPC}_{\rmn{morph}}$ in the remaining regions.
-
-Figure~\ref{fig:sdss_calibration_conv} shows the calibration curve
-that compares $P_{\rmn{gal}}$,
-the fraction of objects that are galaxies (as determined from their spectra)
-to $P_{\rmn{conv}}$ the probabilistic output that our ConvNet model produces.
-The calibration curve is nearly diagonal, which implies that ConvNet
-is well-calibrated and we can treat $P_{\rmn{conv}}$ as the probability
-that an object is a galaxy.
-Figure~\ref{fig:sdss_calibration_tpc} shows the calibration curve
-for the probabilistic output of TPC,
-which is apparently not as well-calibrated as ConvNet.
-These calibration curves visually confirm the results in
-Table~\ref{table:sdss_metrics} that the calibration error
-of ConvNet is about 20\% lower than that of TPC.
+ConvNet performs slightly better than $\rmn{TPC}_{\rmn{morph}}$ in both
+galaxy completeness and star purity between $0.7 \la g-r \la 2.0$
+where the stellar fraction is relatively low.
+Both $\rmn{TPC}_{\rmn{morph}}$ and $\rmn{TPC}_{\rmn{phot}}$ outperform
+ConvNet in the region $g-r \la 0.8$ where the stellar fraction is higher.
+
+Figure~\ref{fig:sdss_calibration_conv} and \ref{fig:sdss_calibratoin_tpc}
+show the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$,
+respectively.
+Compared to Figure~\ref{fig:clens_calibration_conv}, our ConvNet as applied to
+the SDSS data set is not as well-calibrated as when it is applied to the
+CFHTLenS data set.
 

### 2016-05-31 paper/main.tex
update paper

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
 \usepackage{natbib}
-\usepackage{url}
+%\usepackage{url}
+\usepackage{hyperref}
 \usepackage{placeins}
@@
 % are typeset a little smaller.
-\renewcommand{\UrlFont}{\small\tt}
+%\renewcommand{\UrlFont}{\small\tt}
 
@@
 
-\title[Star-galaxy Classification Using ConvNets]{Star-galaxy Classification Using Convolutional Neural Networks}
+\title[Star-galaxy Classification Using ConvNets]{Star-galaxy Classification Using Deep Convolutional Neural Networks}
 
@@
 \begin{keywords}
-methods: data analysis -- methods: statistical -- surveys -- stars: statistics
--- galaxies:statistics.
+methods: data analysis -- techniques: image processing -- methods: statistical
+-- surveys -- stars: statistics -- galaxies:statistics.
 \end{keywords}
@@
 \section{Introduction}
-  \label{section:introduction}
+  \label{sec:introduction}
 
@@
 engineering by hand.
-In Section~\ref{section:data}, we describe the data sets used in this paper
+In Section~\ref{sec:data}, we describe the data sets used in this paper
 and the pre-processing steps for preparing the image data sets.
 We provide a brief overview of deep learning and ConvNets
-in Section~\ref{section:deep_learning}, and
-discuss our strategy for preventing overfitting in Section~\ref{section:overfitting}.
-In Section~\ref{section:tpc}, we describe a state-of-the-art tree-based
+in Section~\ref{sec:deep_learning}, and
+discuss our strategy for preventing overfitting in Section~\ref{sec:overfitting}.
+In Section~\ref{sec:tpc}, we describe a state-of-the-art tree-based
 machine learning algorithm, to which the performance of our ConvNet model is
@@
 We present the main results of our ConvNet model in
-Section~\ref{section:results_and_discussion}, and
-we outline our conclusions in Section~\ref{section:conclusions}.
+Section~\ref{sec:results_and_discussion}, and
+we outline our conclusions in Section~\ref{sec:conclusions}.
 
 \section{Data}
-  \label{section:data}
+  \label{sec:data}
 
 \subsection{Sloan Digital Sky Survey}
-  \label{section:sdss}
+  \label{sec:sdss}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/sdss_color_color.pdf}
+  \caption{
+    The color-color space distribution of stars and galaxies in the SDSS data
+    set. It is easy to see that there is significant overlap between stars
+    and galaxies in the color-color space. 
+  }
+  \label{fig:sdss_color_color}
+\end{figure}
 
@@
 for the training and testing processes.
-We randomly split the objects into training, validation, and test sets
+The apparent magnitudes range from $10.7 < r < 23.1$,
+and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
+The $ugriz$ color-color space of the sample is plotted in
+Figure~\ref{fig:sdss_color_color}.
+We randomly split the objects into training, hold-out validation,
+and blind test sets
 of 40 000, 10 000, and 15 000, respectively.
-We note that we perform a blind test, and the test set is not used in any
+We note that cross-validation is often avoided in deep learning
+in favor of hold-out validation,
+since cross-validation is computationally expensive.
+We also note that we perform a blind test, and the test set is not used in any
 to train or calibrate the algorithms.
@@
 \subsection{Canada-France-Hawaii Telescope Lensing Survey}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/clens_color_color.pdf}
+  \caption{
+    The color-color space distribution of stars and galaxies in the CFHTLenS data
+    set.
+  }
+  \label{fig:clens_color_color}
+\end{figure}
 
@@
 We create cutout images of size $96\times96$ pixels by using a similar method
-to that described in Section~\ref{section:sdss}.
+to that described in Section~\ref{sec:sdss}.
 Finally, images are downscaled to $48\times48$ pixels
@@
 for the training and testing processes.
+The apparent magnitudes range from $13.9 < r < 25.6$,
+and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
+The $ugriz$ color-color space of the sample is plotted in
+Figure~\ref{fig:clens_color_color}.
 We randomly split the objects into training, validation, and test sets of size
@@
 \section{Deep Learning}
-  \label{section:deep_learning}
+  \label{sec:deep_learning}
 
@@
 (Figure~\ref{fig:neuron_a}).
-Let $\mathbf{x}$ be a vector of inputs to a given neuron,
-$\mathbf{w}$ be a vector of weights, and
-$\mathbf{b}$ be the bias.
+Let $\bmath{x}=\left(x_1,x_2,\dots,x_n\right)$ be a vector of inputs to a given neuron,
+$\bmath{w}=\left(w_1,w_2,\dots,w_n\right)$ be a vector of weights, and
+$\bmath{b}$ be the bias.
 Then, the output of the neuron is
 \begin{equation}
-  y = \sigma \left( \mathbf{w} \cdot \mathbf{x} + b \right),
+  y = \sigma \left( \bmath{w} \cdot \bmath{x} + b \right),
   \label{eq:neuron_output}
@@
 has frequently been used as activation function, but it has recently fallen out of favor,
-and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$ is almost always used instead.
+and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$, is almost always used instead.
 The most popular non-linearity at present, however, is the rectified linear unit
-\citep[ReLU;][]{nair2010rectified}, $\sigma(x)=\max(0, x)$,
+\citep[ReLU;][]{nair2010rectified}, $\sigma(x)=\max(0, x)$.
 ReLUs generally allow much faster
@@
 However, ReLU units can sometimes result in dead neurons whose output is always zero.
-To mitigate this problem, we use leaky ReLUs that have a small negative slope
+To mitigate this problem, we use leaky ReLUs that have a small, non-zero slope
 in the negative region,
@@
 
-The goal of learning is to find a set of weights and biases such that
-the output from the network $\mathbf{y}=\left\{ y_1, y_2, \dots, y_n \right\}$
+The goal of learning is to find a set of weights and biases such that,
+given $N$ samples, the output from the network
+$\bmath{y}=\left(y_1, y_2, \dots, y_N \right)$
 approximates the desired output
-$\hat{\mathbf{y}}=\left\{\hat{y}_1, \hat{y}_2, \dots, \hat{y}_n \right\}$
-as closely as possible for all input $\mathbf{x}$.
-We can formulate this as the minimization of a loss function $L(\mathbf{x},\hat{\mathbf{y}})$
+$\hat{\bmath{y}}=\left(\hat{y}_1, \hat{y}_2, \dots, \hat{y}_N \right)$
+as closely as possible for all input
+$\bmath{X}=\left(\bmath{x}_1,\bmath{x}_2,\dots,\bmath{x}_N\right)$.
+We can formulate this as the minimization of a loss function
+$L(\bmath{y},\hat{\bmath{y}})$
 over the training data.
@@
 \begin{equation}
-  L(y, \hat{y}) = -\hat{y} \log_2 y - (1 - \hat{y}) \log_2(1 - y),
-\end{equation}
-where $\hat{y}$ is the actual truth value (\eg 0 or 1)
-and $y$ is the probability prediction made by the model.
+  L(y_j, \hat{y}_j) = -\hat{y}_j \log_2 y_j - (1 - \hat{y}_j) \log_2(1 - y_j),
+  \label{eq:cross_entropy}
+\end{equation}
+where $\hat{y}_j$ is the actual truth value (\eg 0 or 1) of the $j$-th data and
+$y_j$ is the probability prediction made by the model.
 We compute the loss function by taking the average of all cross-entropies in the sample.
-Given $N$ samples, the loss function becomes
+Thus, the loss function becomes
 \begin{equation}
-  L(y, \hat{y}) = - \frac{1}{N} \sum_{i=1}^{N} \hat{y}_i  \log_2 y_i
-    + (1 - \hat{y}_i)  \log_2 (1 - \hat y_i).
-\end{equation}
-where $\hat{y}_i$ and $y_i$ are the truth value and probability estimate of
-the $i$-th data, respectively.
-
-To find the weights $\mathbf{w}$ and biases $\mathbf{b}$ which minimize the loss,
+  L(y_j, \hat{y}_j) = - \frac{1}{N} \sum_{j=1}^{N} \hat{y}_j  \log_2 y_j
+    + (1 - \hat{y}_j)  \log_2 (1 - \hat y_j).
+  \label{eq:cross_entropy_all}
+\end{equation}
+
+To find the weights $\bmath{w}$ and biases $\bmath{b}$ which minimize the loss,
 we use a technique called \textit{gradient descent},
-where we use the following rules to update the parameters in each layer $j$:
+where we use the following rules to update the parameters in each layer $l$:
 \begin{align}
-  \mathbf{w}_j &\rightarrow
-  \mathbf{w}^{\prime}
-  = \mathbf{w}_j - \eta \frac{\partial L}{\partial \mathbf{w}_j} \\
-  \mathbf{b}_j &\rightarrow
-  \mathbf{b}^{\prime}
-  = \mathbf{b}_j - \eta \frac{\partial L}{\partial \mathbf{b}_j},
-  \label{eq:gradeitn_descent}
+  \bmath{w}_l &\rightarrow
+  \bmath{w}_l^{\prime}
+  = \bmath{w}_l - \eta \frac{\partial L}{\partial \bmath{w}_l} \nonumber \\
+  \bmath{b}_l &\rightarrow
+  \bmath{b}_l^{\prime}
+  = \bmath{b}_l - \eta \frac{\partial L}{\partial \bmath{b}_l},
+  \label{eq:gradient_descent}
 \end{align}
@@
 into mini-batches and compute the gradients in
-Equation~\ref{eq:gradeitn_descent} for each mini-batch separately instead of
+Equation~\ref{eq:gradient_descent} for each mini-batch separately instead of
 the entire training data.
@@
 
+The gradients in \ref{eq:gradient_descent} can be computed using the
+\textit{backpropagation} procedure, which is nothing more than an application of
+the chain rule for derivatives.
+The derivative of the loss function with respect to the input of a unit can be
+computed by working backwards from the gradient with respect to the output of
+the unit.
+At the output layer, the derivative of the loss function with respect to the
+output is given by
+\begin{align}
+  \frac{ \partial L }{ \partial y_i } &= y_i - \hat{y}_i \\
+  \frac{ \partial L }{ \partial x_i } &=
+    \frac{ \partial L }{ \partial y_i }
+    \frac{ \partial y_i }{ \partial x_i }.
+\end{align}
+At each hidden layer, the derivative of the loss function with respect to the
+output of each unit is a weighted sum of the derivatives with respect to the
+inputs of the subsequent layer,
+\begin{align}
+  \frac{ \partial L }{ \partial y_j } &=
+    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}   \\
+  \frac{ \partial L }{ \partial x_i } &=
+    \frac{ \partial L }{ \partial y_i }
+    \frac{ \partial y_i }{ \partial x_i }.
+\end{align}
+Finally, once the gradients $\partial L / \partial x_i$ have been
+computed, it is straightforward to compute the gradients for the weight,
+\begin{equation}
+\frac{\partial L}{\partial w_{ji}} = y_j \frac{\partial L}{\partial x_i}.
+\end{equation}
+
 \subsection{Convolutional Neural Networks}
+  \label{sec:convnet}
 
@@
 Mathematically, we replace the dot product in Equation~\ref{eq:neuron_output}
-with a sum of convolutions. The $k$-th feature map is given by
+with a sum of convolutions. Thus, the $k$-th feature map is given by
 \begin{equation}
-\mathbf{y}^k = \sigma \left( \sum_{j} \mathbf{w}_j^k \ast \mathbf{x}_j + b^k \right),
-\end{equation}
-where we sum over the set of filters,
-$\ast$ is the convolution operator, and $\mathbf{w}_j^k$ represent the filters.
+  y^k = \sigma \left( \sum_{m} \bmath{w}_m^k \ast \bmath{x}_m + b^k \right),
+\end{equation}
+where we sum over the set of input feature maps,
+$\ast$ is the convolution operator, and $\bmath{w}_m^k$ represent the filters.
 
@@
 (\ie $44\times44$ images in five bands $ugriz$) with 32 square filters of size $5\times5\times5$.
+We have also experimented with using only three bands $gri$ (for three channels of RGB) and 
+four bands $ugri$ and $griz$ (corresponding to RGBA),
+and using only colors, \eg $u-g$, $g-r$, $r-i$, and/or $i-z$,
+but we find that using magnitudes in all five bands $ugriz$ yields the best performance.
 The leaky ReLU non-linearity is applied to the output of the first convolutional layer
@@
 
-The output of the final fully-connected layer is fed to a softmax function.
+The output of the final fully-connected layer is fed to a \textit{softmax} function.
 The softmax function is given by
 \begin{equation}
-  P (y_i \mid \mathbf{x}) = 
-    \frac{ e^{ \mathbf{x} \cdot \mathbf{w}_{y_i} } }
-    { \sum_{k} e^{ \mathbf{x} \cdot \mathbf{w}_k } },
-\end{equation}
-where we interpret its output as the posterior probability that an object is a galaxy
+  P (G \mid \bmath{x}) = 
+    \frac{ e^{ \bmath{x} \cdot \bmath{w}_G } }
+    { \sum_{i} e^{ \bmath{x} \cdot \bmath{w}_i } },
+\end{equation}
+where we sum over the different possible values of the class label (\ie star or galaxy),
+and interpret its output as the posterior probability that an object is a galaxy
 (or a star).
@@
 
-In addition to hyperparamter optimization, we have explored more than 100 different architectures
-and have found that the architecture described in this section provides
-the best performance on the validation data.
+We have performed a manual search to explore more than 200 combinations of different architectures
+and hyperparameters to find an architecture that minimizes the loss function
+(Equation~\ref{eq:cross_entropy_all}) on the validation set.
+The architecture described in this section provides the best performance on the validation data.
 For example, the architecture of \cite{krizhevsky2012imagenet}
@@
 
-\subsection{Training}
-
 The choice of momentum, learning rate, and initial weights is crucial
@@
 \section{Reducing Overfitting}
-  \label{section:overfitting}
+  \label{sec:overfitting}
 
 Our convolution neural network has $11\times10^6$ learnable parameters,
-while there are only $5\times10^4$ images in the training set.
+while there are only $4\times10^4$ images in the training set.
 As a result, the model is very likely to \emph{overfit} without regularization.
@@
 One common method to combat overfitting is to artificially increase
-the number of training data by using label-preserving transformations.
+the number of training data by using label-preserving
+transformations~\citep{krizhevsky2012imagenet,dieleman2015rotation,dieleman2016exploiting}.
 Each image is transformed as follows:
@@
 uses Bayesian principles to generate an ensemble combination of different models.
-Although the data augmentation step~\ref{sec:data_augmentation} should
+Although the data augmentation step in Section~\ref{sec:data_augmentation} should
 make our ConvNet model invariant to these types of transformations,
-we find that applying BMC still results in a significant decrease in validation error.
-
-The posterior probability that a source is a star is given by
-\begin{equation} \label{eq:p_star_bmc}
-  P \left(S | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right)
-  = \sum_{e \in \bmath{E}} P \left(S | \bmath{x}, \bmath{M}, e \right)
+we find that applying BMC still results in a significant increase in performance.
+
+The posterior probability that a source is a galaxy is given by
+\begin{equation} \label{eq:posterior_bmc}
+  P \left(G | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right)
+  = \sum_{e \in \bmath{E}} P \left(G | \bmath{x}, \bmath{M}, e \right)
   P \left(e | \bmath{D} \right),
 \end{equation}
-where $\bmath{D}$ is the data set,
+where $\bmath{x}$ is the input, $\bmath{D}$ is the data set,
+$\bmath{M}$ is the set of models (\ie different transformations of input images),
 and $e$ is an element in the ensemble space $\bmath{E}$ of possible model combinations.
@@
   P \left( e | \bmath{D} \right) \propto 
-  P \left( e \right) \prod_{i=0}^{N-1}
+  P \left( e \right) \prod_{i=1}^{N}
   \hat{y}_i y_i + 
@@
 we reach a predefined number of combinations,
-and finally use Equation~\ref{eq:p_star_bmc} to compute
+and finally use Equation~\ref{eq:posterior_bmc} to compute
 the posterior probability that a source is a star (or a galaxy).
@@
 \section{Trees for Probabilistic Classifications}
-  \label{section:tpc}
+  \label{sec:tpc}
 
@@
 TPC is a part of a publicly available software package called
-\textsc{MLZ}\footnote{http://lcdm.astro.illinois.edu/code/mlz.html}
+\textsc{MLZ}\footnote{http://pythonhosted.org/MLZ/}
 (Machine Learning for Photo-$z$).
@@
 the extinction-corrected model magnitudes in five bands
-($u$, $g$, $r$, $i$, $z$) and their corresponding colors
+($u$, $g$, $r$, $i$, $z$)
+and their corresponding colors
 ($u-g$, $g-r$, $r-i$, $i-z$).
@@
 The concentration is a good example of carefully handcrafted feature extraction,
-and we show in Section~\ref{section:results_and_discussion}
+and we show in Section~\ref{sec:results_and_discussion}
 that ConvNets do not require such feature engineering.
@@
 
+We note that TPC is able to utilize parallelization, and parallelized on 64
+cores of Xeon E5 processors, it takes 23 minutes to train 500 trees,
+for a total of 25 CPU hours.
+
 \section{Results and Discussion}
-  \label{section:results_and_discussion}
-
-In this section, we present the classification performance of
-our ConvNet model and compare it with the performance of TPC.
+  \label{sec:results_and_discussion}
+
+In this section, we first describe the performance metrics we use to evaluate
+the models. We then present the classification performance of our ConvNet model
+on CFHTLenS and SDSS data sets and compare it with the performance of TPC.
 
@@
 Although many studies often choose the threshold by setting it to a fixed value,
-\eg $p_\rmn{cut} = 0.5$ \citep[\eg][]{henrion2011bayesian, Fadely2012},
+\eg $P_{\rmn{cut}} = 0.5$ \citep[\eg][]{henrion2011bayesian, Fadely2012},
 choosing $0.5$ as a threshold is not the best choice
@@
   \rmn{CAL} = \frac{1}{N-s} \sum_{b=1}^{N-s} \sum_{i=b}^{b+s-1}
-\bigg| P_{\rmn{class},i} - \frac{\sum_{i=b}^{b+s-1} P_{\rmn{gal},i}}{s} \bigg|
+  \bigg| P_{\rmn{class},i} - \frac{\sum_{i=b}^{b+s-1} P_{\rmn{gal},i}}{s} \bigg|,
 \end{equation}
@@
 
+After we use the training set to train our ConvNet model descrbied in
+Section~\ref{sec:convnet} and the validation set to optimize the
+hyperparameters, we evaluate the model's performance on the blind test set.
+We also use the same training and validation sets to train 
+$\rmn{TPC}_{\rmn{morph}}$ and $\rmn{TPC}_{\rmn{phot}}$, and
+perform classifications on the same test set to compare their performance
+with that of ConvNet.
+
 We present in Table~\ref{table:clens_metrics} a summary of the results obtained
-by applying ConvNet and TPC on the CFHTLenS data set.
+by applying ConvNet, $\rmn{TPC}_{\rmn{morph}}$, and $\rmn{TPC}_{\rmn{phot}}$
+on the test set of the CFHTLenS data.
 The bold entries highlight the best technique for any particular metric.
@@
 It is not surprising that $\rmn{TPC}_{\rmn{phot}}$ performs significantly worse
-than both ConvNet and $\rmn{TPC}_{\rmn{phot}}$,
-as morphology is critical in separating stars from galaxies.
-This suggests that ConvNet is able to learn the morphological features
-automatically from the images.
+than both ConvNet and $\rmn{TPC}_{\rmn{phot}}$.
+As Figure~\ref{fig:clens_color_color} shows, there is significant overlap
+between stars and galaxies in color-color space.
+Thus, magnitudes and colors alone are not be sufficient to separate stars from
+galaxies,
+and morphology is critical in separating stars from galaxies.
+ConvNet is able to learn the morphological features automatically from
+the raw images, and ConvNet is comparable to $\rmn{TPC}_{\rmn{morph}}$,
+which is trained on both morphological and photometric attributes.
 
@@
 for the differential counts.
-We use the kernel density estimation~\citep[KDE][]{silverman1986density}
+We use the kernel density estimation~\citep[KDE;][]{silverman1986density}
 with the Gaussian kernel.
@@
 input layer have fewer filters while the later layers have more.
-The low-level features
+The low-level features, \eg edges or blobs, of the input images are still
+recognizable in the first convolutional layers.
+Subsequent layers use these low-level features to detect higher-level features,
+and the final layer is a classifier that uses these high-level features.
+Thus, by performing hierarchical abstraction from low-level to high-level
+features, ConvNets are able to utilize shape information in the classification
+process.
 
@@
 We note that $\rmn{TPC}_{\rmn{morph}}$ outperforms the star-galaxy
-classifier used by the SDSS pipeline (\ie an object is classifed as a galaxy
+classifier used by the SDSS pipeline (\ie an object is classified as a galaxy
 if the concentration parameter is greater than 0.145) over all magnitudes.
 We do not show the SDSS classifications to avoid cluttering the plots.
-While ConvNet shows a similar but slighly worse performance than
+While ConvNet shows a similar but slightly worse performance than
 $\rmn{TPC}_{\rmn{morph}}$,
@@
 counts.
-ConvNet is able to mantain a galaxy purity of 0.9915 up to $i\sim22.5$,
-while $\rmn{TPC}_{\rmn{morph}}$ provides a glaxay purity of 0.9977.
+ConvNet is able to maintain a galaxy purity of 0.9915 up to $i\sim22.5$,
+while $\rmn{TPC}_{\rmn{morph}}$ provides a galaxy purity of 0.9977.
 $\rmn{TPC}_{\rmn{morph}}$ also outperforms ConvNet
@@
 
-Figure~\ref{fig:sdss_calibration_conv} and \ref{fig:sdss_calibratoin_tpc}
+Figure~\ref{fig:sdss_calibration_conv} and \ref{fig:sdss_calibration_tpc}
 show the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$,
@@
 \section{Conclusions}
-  \label{section:conclusions}
+  \label{sec:conclusions}
 
@@
 In the interest of scientific reproducibility, we make all our code available at
-\url{https://github.com/EdwardJKim/dl4astro}.  
+\href{https://github.com/EdwardJKim/dl4astro}{https://github.com/EdwardJKim/dl4astro}.  
 For the CFHTLenS data set, the network is able to provide a classification that
@@
 but the probabilities are still slightly better calibrated.
-The major advatange of ConvNets is that useful features are learned
+The major advantage of ConvNets is that useful features are learned
 automatically from raw pixel values, while traditional machine learning
@@
 such as TPC~\citep{carrascokind2013tpz, kim2015hybrid}, remain a viable option.
-As the "no free lunch" theorem~\citep{wolpert1996lack} states,
+As the ``no free lunch'' theorem~\citep{wolpert1996lack} states,
 there is no one model that works for every problem.
@@
 Since the SDSS catalog provides the concentration paramter that is highly
-optmized for star-galaxy classification, TPC works better for SDSS.
+optimized for star-galaxy classification, TPC works better for SDSS.
 
@@
 The most effective way to prevent overfitting would be to simply collect more training images
-with spectroscopic follow-up, as the performance of ConvNets apparently
+with spectroscopic follow-up, as the performance of ConvNets generally
 improves with more training data.
@@
 to produce well-calibrated posterior probabilities.
+We also note that using more training images will require the use of multi-GPU,
+which is beyond the scope of the present work.
 

### 2016-05-31 paper/main.tex
some minor fixes

@@
 which is publicly available through the online CasJobs
-server~\citep{li2008casjobs}~\footnote{http://skyserver.sdss.org/casjobs/}.
-
-Using the CasJobs server, we randomly select 65,000 stars and galaxies.
+server~\footnote{http://skyserver.sdss.org/casjobs/}~\citep{li2008casjobs}.
+
+Using the CasJobs server, we randomly select $65\,000$ stars and galaxies.
 We exclude some bad photometric observations as follows.
@@
 We then use \texttt{SExtractor} to find the pixel positions of
-the 65,000 objects we have selected,
+the $65\,000$ objects we have selected,
 and to center each object in the cutout image.
@@
 
-In the end, we have 17 344 stars and 47 656 galaxies available
+In the end, we have $17\,344$ stars and $47\,656$ galaxies available
 for the training and testing processes.
@@
 We randomly split the objects into training, hold-out validation,
-and blind test sets
-of 40 000, 10 000, and 15 000, respectively.
+and blind test sets of size $40\,000$, $10\,000$, and $15\,000$, respectively.
 We note that cross-validation is often avoided in deep learning
@@
 We also note that we perform a blind test, and the test set is not used in any
-to train or calibrate the algorithms.
+way to train or calibrate the algorithms.
 
@@
 
-In the end, we have 8 545 stars and 57 843 galaxies available
+In the end, we have $8\,545$ stars and $57\,843$ galaxies available
 for the training and testing processes.
@@
 Figure~\ref{fig:clens_color_color}.
-We randomly split the objects into training, validation, and test sets of size
-40 000, 10 000, and 13 278, respectively.
+We randomly split the objects into training, hold-out validation, and
+blind test sets of size $40\,000$, $10\,000$, and $13\,278$, respectively.
 
@@
     (a) A mathematical model of a biological neuron.
-    (b) A schematic diagram of a neural network with one hidden layer
-    of two neurons and one output layer with two neurons.
+    (b) A schematic diagram of a neural network with one hidden layer.
     }
@@
   \centering
-  \caption{Summary of hyperparameters. Note that pooling layers have no learnable parameters.}
+  \caption{Summary of ConvNet architecture and hyperparameters. Note that pooling layers have no learnable parameters.}
   \label{table:hyperparamters}
@@
 and hyperparameters to find an architecture that minimizes the loss function
-(Equation~\ref{eq:cross_entropy_all}) on the validation set.
-The architecture described in this section provides the best performance on the validation data.
-For example, the architecture of \cite{krizhevsky2012imagenet}
+(Equation~\ref{eq:cross_entropy_all}) on the validation set of the SDSS data.
+The architecture described in this section provides the best performance on
+the SDSS validation set.
+To test how this model performs across different, related problems,
+we use the same architecture on the CFHTLenS data set.
+
+The architecture of \cite{krizhevsky2012imagenet}
 uses relatively large receptive fields ($11\times11$) in the first convolutional layers.
@@
 by ensuring that all ReLU neurons fire in the beginning.
+
 We note that our network takes about 40 hours to train the networks on a NVIDIA Tesla K40 GPU.
@@
 In this paper, we use a $q$ value of three,
-and 1,000 model combinations are considered.
+and $1\,000$ model combinations are considered.
 
@@
 $\rmn{TPC}_{\rmn{phot}}$ is trained with 
-the five magnitudes and their corresponding colors,
+the five magnitudes and their corresponding colors:
 $u$, $g$, $r$, $i$, $z$, $u-g$, $g-r$, $r-i$, and $i-z$.
@@
 \texttt{SExtractor}'s \texttt{FLUX\_RADIUS} (the half-light radius),
-\texttt{A\_WORLD} (the semi-major axis), \texttt{B\_WORLD} (the semi-minor axis)
-for morphological features, in addition to
+\texttt{A\_WORLD} (the semi-major axis), and \texttt{B\_WORLD}
+(the semi-minor axis) for morphological features, in addition to
 the five magnitudes and their corresponding colors,
@@
 We note that TPC is able to utilize parallelization, and parallelized on 64
-cores of Xeon E5 processors, it takes 23 minutes to train 500 trees,
+cores of Xeon E5 2.7 GHz processors, it takes 23 minutes to train 500 trees,
 for a total of 25 CPU hours.
@@
 the models. We then present the classification performance of our ConvNet model
-on CFHTLenS and SDSS data sets and compare it with the performance of TPC.
+on CFHTLenS and SDSS data sets, and compare it with the performance of TPC.
 
 \subsection{Classification Metrics}
+
+\begin{table}
+  \caption{The definition of the classification performance metrics.}
+  \centering
+  \begin{tabular}{c l}
+  \hline
+  Metric & Meaning \\
+  \hline
+  AUC & Area under the Receiver Operating Curve \\
+  MSE & Mean squared error \\
+  $c_g$ & Galaxy completeness \\
+  $p_g$ & Galaxy purity \\
+  $c_s$ & Star completeness \\
+  $p_s$ & Star purity \\
+  $p_g(c_g=x)$ & Galaxy purity at $x$ galaxy completeness \\
+  $p_s(c_s=x)$ & Star purity at $x$ star completeness \\
+  $CAL$ & Calibration error with overlapping binning \\
+  $\mid\Delta N_g\mid / N_g$ & Absolute error in number of galaxies\\
+  \hline
+  \end{tabular}
+  \label{table:metrics}
+\end{table}
 
@@
 \begin{equation} \label{eq:mse}
-  \rmn{MSE} = \frac{1}{N} \sum^{N}_{i=1}
-  \left( y_i - \hat{y}_i \right)^2,
+  \rmn{MSE} = \frac{1}{N} \sum^{N}_{j=1}
+  \left( y_j - \hat{y}_j \right)^2,
 \end{equation}
@@
 We order the predicted values $P_\rmn{class}$ and
-put the first 1000 elements in the first bin.
+put the first $1\,000$ elements in the first bin.
 We calculate the true probability $P_\rmn{gal}$ by counting the true galaxies
@@
 The calibration error for this bin is $\mid P_\rmn{gal} - P_\rmn{class} \mid$.
-We then repeat this for the second bin (2 to 1001),
-the third bin (3 to 1002), and so on, and average the binned calibration errors.
+We then repeat this for the second bin (2 to $1\,001$),
+the third bin (3 to $1\,002$), and so on, and average the binned calibration errors.
 Thus, the overall calibration error is given by
 \begin{equation}
-  \rmn{CAL} = \frac{1}{N-s} \sum_{b=1}^{N-s} \sum_{i=b}^{b+s-1}
-  \bigg| P_{\rmn{class},i} - \frac{\sum_{i=b}^{b+s-1} P_{\rmn{gal},i}}{s} \bigg|,
-\end{equation}
-where $s=1000$ is the bin length.
-
-\begin{table}
-  \caption{The definition of the classification performance metrics.}
-  \centering
-  \begin{tabular}{c l}
-  \hline
-  Metric & Meaning \\
-  \hline
-  AUC & Area under the Receiver Operating Curve \\
-  MSE & Mean squared error \\
-  $c_g$ & Galaxy completeness \\
-  $p_g$ & Galaxy purity \\
-  $c_s$ & Star completeness \\
-  $p_s$ & Star purity \\
-  $p_g(c_g=x)$ & Galaxy purity at $x$ galaxy completeness \\
-  $p_s(c_s=x)$ & Star purity at $x$ star completeness \\
-  $CAL$ & Calibration error with overlapping binning \\
-  $\mid\Delta N_g\mid / N_g$ & Absolute error in number of galaxies\\
-  \hline
-  \end{tabular}
-  \label{table:metrics}
-\end{table}
+  \rmn{CAL} = \frac{1}{N-s} \sum_{b=1}^{N-s} \sum_{j=b}^{b+s-1}
+  \bigg| P_{\rmn{class},j} - \frac{\sum_{j=b}^{b+s-1} P_{\rmn{gal},j}}{s} \bigg|,
+\end{equation}
+where $s=1\,000$ is the bin length.
 
@@
 instead of counting each galaxy equally, a galaxy could be
-counted as $P_{\rmn{class}}$, the probability estimate.
-This should, in principle, remove the contamination effect of stars.
-For a perfect classifier, we can count the number of galaxies by summing
-the values of $P_{\rmn{class}}$.
-Thus, we measure the reliability of the classifier output by the absolute error
+counted as $P_{\rmn{class}}$ the probability estimate.
+This should in principle remove the contamination effect of stars.
+For a perfect classifier, we can count the total number of galaxies in the sample
+by summing the values of $P_{\rmn{class}}$.
+Thus, we measure the reliability of classifier output by the absolute error
 in the estimation of number of galaxies,
@@
   \frac{\mid \Delta N_g \mid}{N_g} =
-  \frac{\big| N_g - \sum_{i=1}^{N} P_{\rmn{class}} \big|}{N_g}.
+  \frac{\big| N_g - \sum_{j=1}^{N} P_{\rmn{class},j} \big|}{N_g}.
 \end{equation}
@@
   \includegraphics[width=\columnwidth]{figures/clens_mag.pdf}
-  \caption{Galaxy completeness and star purity values as a function
+  \caption{Galaxy completeness and star purity values as functions
            of the $i$-band magnitude
            as estimated by the kernel density estimation (KDE) method
-           for the differential counts.
+           for the differential counts in the CFHTLenS data set.
            The top panel shows the histogram with a bin size of 0.1 mag
@@
     Galaxy purity and star completeness as functions of the $i$-band
-    magnitude for the integrated counts. The upper panel compres the galaxy
+    magnitude for the integrated counts in the CFHTLenS data set.
+    The upper panel compares the galaxy
     purity values for ConvNet (red solid line), $\rmn{TPC}_{\rmn{morph}}$
@@
       Calibration curve for ConvNet as applied to the CFHTLenS data set.
-      $p_{\rmn{gal}}$ is the fraction of objects that are galaxies.
-      $p_{\rmn{conv}}$ is the probabilistic output generated by ConvNet.
+      $P_{\rmn{gal}}$ is the fraction of objects that are galaxies.
+      $P_{\rmn{conv}}$ is the probabilistic output generated by ConvNet.
       The dashed line displays the relationship
-      $p_{\rmn{gal}} = p_{\rmn{conv}}$.
+      $P_{\rmn{gal}} = P_{\rmn{conv}}$.
       The $1 \sigma$ error bars are computed following the method
@@
     \includegraphics[width=\textwidth]{figures/clens_calibration_tpc.pdf}
-    \caption{Calibration curve for $\rmn{TPC}_{\rmn{morph}}$
-      as applied to the CFHTLenS data set.}
+    \caption{Similar to Figure~\ref{fig:clens_calibration_conv} but for
+      $\rmn{TPC}_{\rmn{morph}}$.
+      $P_{\rmn{tpc}}$ is the probabilistic output generated by ConvNet.}
     \label{fig:clens_calibration_tpc}
@@
   \caption{
-    (a) A sample $44\times44$ RGB image of a CFHTLenS galaxy.
+    (a) A sample $44\times44$ RGB image of a galaxy in the CFHTLenS data set.
     The RGB image is created by mapping R $\rightarrow g$ band magnitude,
@@
   \caption{
-    Same as Figure~\ref{fig:galaxy_activations} but for a CFHTLenS star.
+    Similar to Figure~\ref{fig:galaxy_activations} but for a star in the
+    CFHTLenS data set.
     }
@@
 
-After we use the training set to train our ConvNet model descrbied in
-Section~\ref{sec:convnet} and the validation set to optimize the
-hyperparameters, we evaluate the model's performance on the blind test set.
+As descrbied in Section~\ref{sec:convnet},
+we train our ConvNet model by monitoring its performance on the validatoin set.
+Once we have finished training our model,
+we evaluate its performance on the blind test set.
 We also use the same training and validation sets to train 
@@
 two metrics (MSE and $c_g$).
-It is not surprising that $\rmn{TPC}_{\rmn{phot}}$ performs significantly worse
-than both ConvNet and $\rmn{TPC}_{\rmn{phot}}$.
+It is not surprising that $\rmn{TPC}_{\rmn{phot}}$, which is trained on only
+magnitudes and colors, performs significantly worse than both ConvNet and
+$\rmn{TPC}_{\rmn{phot}}$.
 As Figure~\ref{fig:clens_color_color} shows, there is significant overlap
 between stars and galaxies in color-color space.
-Thus, magnitudes and colors alone are not be sufficient to separate stars from
+Thus, magnitudes and colors alone are not sufficient to separate stars from
 galaxies,
@@
 ConvNet is able to learn the morphological features automatically from
-the raw images, and ConvNet is comparable to $\rmn{TPC}_{\rmn{morph}}$,
+the raw images, and the performance of ConvNet is therefore comparable to
+that of $\rmn{TPC}_{\rmn{morph}}$,
 which is trained on both morphological and photometric attributes.
@@
 the shape information automatically from the images.
-We note that, at these operating conditions ($c_g=0.96$, $p_s=0.97$),
+We note that, at these operating conditions ($c_g=0.96$ or $p_s=0.97$),
 both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ outperform the
@@
 In Figure~\ref{fig:clens_integrated}, we show the overall galaxy purity
-and star completeness values as functions of magnitude for the integrated
-counts.
+and star completeness values as functions of $i$-band magnitude for the
+integrated counts.
 ConvNet is able to mantain a galaxy purity of 0.9972 up to $i\sim24.5$,
@@
 The low-level features, \eg edges or blobs, of the input images are still
-recognizable in the first convolutional layers.
+recognizable in the first convolutional layer.
 Subsequent layers use these low-level features to detect higher-level features,
@@
   \includegraphics[width=\columnwidth]{figures/sdss_mag.pdf}
-  \caption{Completeness and purity in the SDSS
-           as a function of the $r$-band magnitude for
-           the differential counts.}
+  \caption{Galaxy ompleteness and star purity as function of the $r$-band
+    magnitude for the differential counts in the SDSS data set.}
   \label{fig:sdss_mag}
@@
   \includegraphics[width=\columnwidth]{figures/sdss_integrated.pdf}
-  \caption{Completeness and purity in the SDSS
-           as a function of the $r$-band magnitude
-           for the integrated counts.}
+  \caption{Galaxy completeness and star purity as functions of the $r$-band
+    magnitude for the integrated counts in the SDSS data set.}
   \label{fig:sdss_integrated}
@@
   \includegraphics[width=\columnwidth]{figures/sdss_g_r.pdf}
-  \caption{Similar to Figure~\ref{fig:sdss_mag}
-           but as a function of $g-r$ color.
-           The bin size of histogram in the top panel is 0.05.}
+  \caption{Similar to Figure~\ref{fig:sdss_mag} but as a function of
+    $g-r$ color. The bin size of histogram in the top panel is 0.05.}
   \label{fig:sdss_g_r}
@@
 The bold entries highlight the best technique for any particular metrics.
-In contrast with the CFHTLenS data set in the previous section,
+In contrast with the CFHTLenS data set in Section~\ref{sec:results_cfht},
 it is apparent that $\rmn{TPC}_{\rmn{morph}}$ outperforms ConvNet
-in all metrics except the $\rmn{CAL}$.
+in all metrics except $\rmn{CAL}$.
 Both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ still outperforms
-$\rmn{TPC}_{\rmn{phot}}$ in all six metrics by a significant amount.
+$\rmn{TPC}_{\rmn{phot}}$ in all six metrics by a significant amount, as
+magnitudes and colors alone are not sufficient to separate stars from galaxies.
+Alhtough ConvNet performs worse than $\rmn{TPC}_{\rmn{morph}}$ on the SDSS
+data, its performance is much closer to $\rmn{TPC}_{\rmn{morph}}$, as ConvNet
+is able to learn the shape information automatically from the raw images.
 
 In Figure~\ref{fig:sdss_mag}, we compare the galaxy completeness
-and star purity values for ConvNet and TPC as functions of $i$-band magnitude
-for the differential counts.
+and star purity values for ConvNet and $\rmn{TPC}_{\rmn{morph}}$ as
+functions of $i$-band magnitude for the differential counts in the SDSS data.
 We note that $\rmn{TPC}_{\rmn{morph}}$ outperforms the star-galaxy
@@
 ConvNet performs slightly better than $\rmn{TPC}_{\rmn{morph}}$ in both
-galaxy completeness and star purity between $0.7 \la g-r \la 2.0$
+galaxy completeness and star purity between $0.7 \la g-r \la 2.0$,
 where the stellar fraction is relatively low.
@@
 respectively.
-Compared to Figure~\ref{fig:clens_calibration_conv}, our ConvNet as applied to
-the SDSS data set is not as well-calibrated as when it is applied to the
+Compared to Figure~\ref{fig:clens_calibration_conv},
+when our ConvNet is applied to the SDSS data set,
+its calibration curve is not as well-calibrated as when it is applied to the
 CFHTLenS data set. 
+Although it is not straightforward to compare the two calibration curves by
+visual inspection, Table~\ref{table:sdss_metrics} shows that the CAL metrics of
+ConvNet is lower than that of TPC.
 
@@
 The lack of requirement for feature extraction is a huge advantage \eg
-when the task is to classify 1 000 classes in the ImageNet data
+when the task is to classify $1\,000$ classes in the ImageNet data
 set~\citep{russakovsky2015imagenet},
@@
 We also note that using more training images will require the use of multi-GPU,
-which is beyond the scope of the present work.
+which was beyond the scope of the present work.
 
@@
 For future work, we plan to train more ConvNet variants, such as the
-Inception Module~\citep{szegedy2015going} and Residual network~\citep{he2015deep}.
+Inception Module~\citep{szegedy2015going} and Residual Network~\citep{he2015deep}.
 To improve the predictive performance,
@@
 neural network architectures.
-It is likely that the performance will be improved by,
+
+It is also likely that the performance will be improved by,
 not only training multiple network architectures,

### 2016-06-02 notebooks/utils/bootstrap.py
add helper scripts

@@ -1,0 +1,92 @@
+from __future__ import (
+    division, print_function, unicode_literals, absolute_import
+    )
+import numpy as np
+from sklearn.neighbors import KernelDensity
+from .metrics import threshold_at_completeness_of, threshold_at_purity_of
+
+def get_log_density(x, bins):
+
+    x_kde = bins[:, np.newaxis]
+    bandwidth = 1.06 * np.std(x) * np.power(len(x), -0.2)
+    kde = KernelDensity(kernel='gaussian', bandwidth=bandwidth).fit(x[:, np.newaxis])
+    log_density = kde.score_samples(x_kde)
+
+    return log_density
+
+def kde_completeness(y_true, y_pred, mag, threshold=0.5, bins=None):
+    
+    if bins is None:
+        bins = np.linspace(mag.min(), mag.max(), 100)
+
+    true_class = mag[y_true == 1]
+    log_dens_true = get_log_density(true_class, bins)
+
+    tp = mag[(y_pred >= threshold) & (y_true == 1)]
+    log_dens_tp = get_log_density(tp, bins)
+
+    completeness = (
+        len(tp) * np.exp(log_dens_tp) / np.exp(log_dens_tp).sum()
+        / (len(true_class) * np.exp(log_dens_true) / np.exp(log_dens_true).sum())
+        )
+
+    return completeness
+
+def kde_purity(y_true, y_pred, mag, threshold=0.5, bins=None):
+    
+    if bins is None:
+        bins = np.linspace(mag.min(), mag.max(), 100)
+
+    true_class = mag[y_pred >= threshold]
+    log_dens_true = get_log_density(true_class, bins)
+
+    tp = mag[(y_pred >= threshold) & (y_true == 1)]
+    log_dens_tp = get_log_density(tp, bins)
+
+    purity = (
+        len(tp) * np.exp(log_dens_tp) / np.exp(log_dens_tp).sum()
+        / (len(true_class) * np.exp(log_dens_true) / np.exp(log_dens_true).sum())
+        )
+
+    return purity
+
+def get_stellar_fraction(y_true, y_pred, mag, bins=None):
+
+    if bins is None:
+        bins = np.linspace(mag.min(), mag.max(), 100)
+
+    log_dens_mag = get_log_density(mag, bins)
+
+    sx = mag[y_true == 1]
+    log_dens_sx = get_log_density(sx, bins)
+
+    stellar_fraction = (
[…]

### 2016-06-02 notebooks/utils/metrics.py

@@ -1,0 +1,232 @@
+from __future__ import (
+    division, print_function, unicode_literals, absolute_import
+    )
+import numpy as np
+from scipy.special import gammaln
+from scipy.integrate import quad
+import pandas as pd
+
+def get_purity(y_true, y_pred, threshold):
+
+    num = ((y_true == 1) & (y_pred >= threshold)).sum()
+    denom = (y_pred >= threshold).sum()
+
+    if denom:
+        purity = num / denom
+    else:
+        purity = np.nan
+
+    return purity
+
+def get_completeness(y_true, y_pred, threshold):
+
+    num = ((y_true == 1) & (y_pred >= threshold)).sum()
+    denom = (y_true == 1).sum()
+
+    if denom:
+        completeness = num / denom
+    else:
+        completeness = np.nan
+
+    return completeness
+
+def threshold_at_purity_of(y_true, y_pred, threshold):
+    
+    thresholds = np.sort(y_pred)
+    purity = np.zeros_like(thresholds)
+    
+    for i, t in enumerate(thresholds):
+        purity[i] = get_purity(y_true, y_pred, t)
+
+    purity = purity[~np.isnan(purity)] 
+
+    idx = np.argmin(np.abs(purity - threshold))
+    
+    return thresholds[idx], purity[idx]
+
+def threshold_at_completeness_of(y_true, y_pred, threshold):
+    
+    thresholds = np.sort(y_pred)
+    completeness = np.zeros_like(thresholds)
+    
+    for i, t in enumerate(thresholds):
+        completeness[i] = get_completeness(y_true, y_pred, t)
+ 
+    completeness = completeness[~np.isnan(completeness)]
+    
+    idx = np.argmin(np.abs(completeness - threshold))
+
+    return thresholds[idx], completeness[idx]
+
+
+def bayes_conf(N, k, conf=0.683, tol=1.0e-3, step=1.0e-3, a0=None, dx0=None, output=True):
+    """
+    http://inspirehep.net/record/669498/files/fermilab-tm-2286.PDF
+    """
+    
+    epsilon = k / N
+    
+    if a0 is None:
+        a0 = epsilon
+        
+    if dx0 is None:
+        dx0 = step
+    
+    bins = np.arange(0, 1 + step, step)
+    
+    def get_log_p(N, k):
+        p = gammaln(N + 2) - gammaln(k + 1) - gammaln(N - k + 1) + k * np.log(bins) + (N - k) * np.log(1 - bins)
+        return p
+    
[…]

### 2016-06-02 scripts/bmc.py
added convnet training scripts

@@ -1,0 +1,86 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+from __future__ import unicode_literals
+
+import numpy as np
+
+
+class BMC(object):
+    '''
+    Bayesian Model Combination (Monteith et al. 2011).
+    A Hybrid Ensemble Approach to Star-galaxy Classification (Kim, Brunner & Carrasco Kind 2015).
+    '''
+    def __init__(self, q=4, ncomb=1000, nburn=200, ntop=10, icore=0):
+        '''
+        Constructor.
+        
+        Parameters
+        ----------
+        q: The number of combinations drawn each time from Dirichlet distribution.
+        ncomb: The total number of ensembles.
+        nburn: The number of iterations in the burn-in step.
+        ntop: The side length of a rectangular SOM.
+        icore: The number of cores (0 unless parallelized).
+        '''
+        self.q = q
+        self.ncomb = ncomb
+        self.nburn = nburn
+        self.pfloor = 1e-300
+
+    def get_log_likelihood(self, label, array, weight):
+
+        y = label
+        x = np.sum(array * weight, axis=1)
+        error = np.abs(y - x)
+        
+        # Cromwell's rule:
+        # I beseech you, in the bowels of Christ,
+        # think it possible that you may be mistaken.
+        # and also the fact that log of 0 diverges.
+        error[error == 0] = self.pfloor
+        error[error == 1] = 1 - self.pfloor
+        lnlike = np.log(1 - error).sum()
+
+        return lnlike
+
+    def fit(self, X, y, create_cells=True):
+
+        nxrows, nxcols = X.shape
+        self.m = nxcols
+
+        post_all = np.zeros(nxrows)
+
+        # create folders
+        weight_all = np.zeros(((self.ncomb - self.nburn) * self.q, self.m))
+        
+        alpha = np.ones(self.m)
+        log_p_comb = np.zeros(self.q)
+
+        for i in range(self.ncomb):
+            weight = np.random.dirichlet(alpha, self.q)
+
+            for j in range(self.q):
+                w = self.get_log_likelihood(y, X, weight[j])
+                log_p_comb[j] = w
+                        
+                if i >= self.nburn:
+                    weight_all[(i - self.nburn) * self.q + j] = weight[j]
+
+            best_weight = weight[log_p_comb.argmax()]
+            alpha += best_weight
+
+        a = np.dot(X, weight_all.T)
+
[…]

### 2016-06-02 scripts/train_cnn.py

@@ -1,0 +1,349 @@
+'''
+If you are using a GPU, write the following in ~/.theanorc.
+
+[global]
+device=gpu
+floatX=float32
+
+[blas]
+ldflags=-lopenblas
+
+[cuda]
+root=/opt/apps/cuda/7.0
+
+[nvcc]
+fastmath=True
+'''
+
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+from __future__ import unicode_literals
+
+import os
+import sys
+import time
+import cPickle as pickle
+
+import numpy as np
+
+import theano
+import theano.tensor as T
+
+import lasagne
+from lasagne import layers
+from lasagne.updates import nesterov_momentum
+from lasagne.objectives import categorical_crossentropy
+from lasagne.nonlinearities import leaky_rectify
+from lasagne.init import Orthogonal, Constant
+from nolearn.lasagne import NeuralNet
+from nolearn.lasagne import BatchIterator
+from lasagne.nonlinearities import softmax
+from sklearn.utils import shuffle
+
+import bmc
+
+X = np.load("sdss_training_images.npy")
+print("X.shape = {}, X.min = {}, X.max = {}".format(X.shape, X.min(), X.max()))
+
+y = np.load("sdss_training_labels.npy")
+print("y.shape = {}, y.min = {}, y.max = {}".format(y.shape, y.min(), y.max()))
+
+X, y = shuffle(X, y)
+
+def renormalize(array):
+    return (array - array.min()) / (array.max() - array.min())
+
+for i in range(5):
+    X[:, i, :, :] = renormalize(X[:, i, :, :])
+    
+y = renormalize(y).astype(np.int32)
+print("X.shape = {}, X.min = {}, X.max = {}".format(X.shape, X.min(), X.max()))
+print("y.shape = {}, y.min = {}, y.max = {}".format(y.shape, y.min(), y.max()))
+
+def compute_PCA(array):
+
+    nimages0, nchannels0, height0, width0 = array.shape
+    rolled = np.transpose(array, (0, 2, 3, 1))
+    # transpose from N x channels x height x width  to  N x height x width x channels
+    nimages1, height1, width1, nchannels1 = rolled.shape
+    # check shapes
+    assert nimages0 == nimages1
+    assert nchannels0 == nchannels1
+    assert height0 == height1
+    assert width0 == width1
+    # flatten
[…]

### 2016-06-02 scripts/fetch_sdss.py
update fetch_sdss

@@ -1,4 +1,4 @@
-#!/usr/bin/env python
+#!/usr/bin/env python2
 
 # This script
 # 
@@ -27,7 +27,7 @@ from time import sleep
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
-from mpi4py import MPI
+#from mpi4py import MPI
 
 import montage_wrapper as mw
 from astropy.io import fits
@@ -393,9 +393,9 @@ def save_cutout(df, size=48, image_dir="temp", save_dir="result"):
             save_path = os.path.join(save_dir, "{0}.{1}x{1}.{2}.npy".format(row["class"], size, row["objID"]))
             np.save(save_path, array)
 
-def run_online_mode():
+def run_online_mode(filename="DR12_spec_phot_sample.csv", chunk_size=100):
 
-    df = pd.read_csv("../data/DR12_spec_phot_sample.csv", dtype={"objID": "object"})
+    df = pd.read_csv(filename, dtype={"objID": "object"})
 
     if os.path.exists("result"):
         done = os.listdir("result")
@@ -471,4 +471,4 @@ def run_parallel(filename, dest=None):
 
 if __name__ == "__main__":
 
-    run_parallel("chunk.csv")
+    run_online_mode("DR12_spec_phot_sample.csv")

### 2016-06-02 scripts/fetch_sdss.py
added some instructions in sdss_fetch.py

@@ -1,14 +1,31 @@
 #!/usr/bin/env python2
 
-# This script
-# 
-# - makes an SQL query to the SDSS DR12 database (using its [API](http://skyserver.sdss.org/dr12/en/help/docs/api.aspx)) to create a catalog, 
-# - downloads the FITS files,
-# - uses [Montage](http://montage.ipac.caltech.edu/) (and [montage wrapper](http://www.astropy.org/montage-wrapper/) to align each image to the image in the $r$-band, and
-# - uses [Sextractor](http://www.astromatic.net/software/sextractor) to find the pixel position of objects, and
-# - converts the fluxes in FITS files to [luptitudes](http://www.sdss.org/dr12/algorithms/magnitudes/#asinh).
-# 
-# This [Docker image](https://github.com/EdwardJKim/deeplearning4astro/tree/master/docker) has all packages necessary to run this notebook.
+'''
+Author: Edward J Kim <edward.junhyung.kim@gmail.com>
+
+This script
+ 
+- Makes an SQL query to the SDSS DR12 database (using its API at
+  http://skyserver.sdss.org/dr12/en/help/docs/api.aspx) to create a catalog, 
+
+- Downloads the FITS files,
+
+- Uses Montage (http://montage.ipac.caltech.edu/) and
+  montage wrapper (http://www.astropy.org/montage-wrapper/) to align each image
+  to the image in the r-band, and
+
+- Uses Sextractor (http://www.astromatic.net/software/sextractor) to find the
+  pixel position of objects, and
+
+- Converts the fluxes in FITS files to luptitudes
+  (http://www.sdss.org/dr12/algorithms/magnitudes/#asinh).
+ 
+See Dockerfile at https://github.com/EdwardJKim/deeplearning4astro/tree/master/docker.
+It has all packages necessary to run this notebook.
+
+To use this script with CasJobs, see
+https://github.com/EdwardJKim/dl4astro/blob/master/scripts/README.md.
+'''
 
 from __future__ import absolute_import
 from __future__ import division

### 2016-06-02 scripts/fetch_sdss.py
update fetch_sdss script

@@ -366,7 +366,7 @@ def nanomaggie_to_luptitude(array, band):
     
     return luptitude
 
-def save_cutout(df, size=48, image_dir="temp", save_dir="result"):
+def save_cutout(df, cat, size=48, image_dir="temp", save_dir="result"):
 
     if not os.path.exists(save_dir):
         os.makedirs(save_dir)
@@ -386,16 +386,20 @@ def save_cutout(df, size=48, image_dir="temp", save_dir="result"):
             l = r + cut_size
         return r, l
 
-    for i, row in df.iterrows():
+    for i, row in cat.iterrows():
 
         array = np.zeros((5, size, size))
+        
+        y0, x0, y1, x1 = row[["xmin", "ymin", "xmax", "ymax"]].values
+        matched = df[df["objID"] == row.astype("object")["objID"]]
+        assert len(matched) == 1
 
         for j, b in enumerate("ugriz"):
 
             fpath = os.path.join(image_dir, row["file"])
             image_data = fits.getdata(fpath.replace("-r-", "-{}-".format(b)))
             
-            y0, x0, y1, x1 = row[["xmin", "ymin", "xmax", "ymax"]].values
+            extinction = matched["extinction_{}".format(b)].values[0]
 
             right, left = find_position(x0, x1, size, image_data.shape[0])
             down, up = find_position(y0, y1, size, image_data.shape[1])
@@ -403,7 +407,7 @@ def save_cutout(df, size=48, image_dir="temp", save_dir="result"):
             cut_out = image_data[right: left, down: up]
         
             if cut_out.shape[0] == size and cut_out.shape[1] == size:
-                cut_out = nanomaggie_to_luptitude(cut_out, b)
+                cut_out = nanomaggie_to_luptitude(cut_out, b) - extinction
                 array[j, :, :] = cut_out
                 
         if np.isnan(array).sum() == 0 and array.sum() > 0:
@@ -433,7 +437,7 @@ def run_online_mode(filename="DR12_spec_phot_sample.csv", chunk_size=100):
         convert_catalog_to_pixels(chunk)
         cat = run_sex(chunk)
         try:
-            saved = save_cutout(cat, size=48)
+            saved = save_cutout(chunk, cat, size=48)
         except:
             pass
         shutil.rmtree("temp")

### 2016-06-03 scripts/fetch_cfhtlens.py
update fetch_cfhtlens script

@@ -334,7 +334,9 @@ def save_cutout(df, size=96, image_dir="temp", save_dir="result"):
             right, left = find_position(x0, x1, size, image_data.shape[0])
             down, up = find_position(y0, y1, size, image_data.shape[1])
 
-            cut_out = image_data[right: left, down: up]
+            extinction = df[df["id"] == row["id"]]["EXTINCTION_{}".format(b)].values[0]
+
+            cut_out = image_data[right: left, down: up] - extinction
             
             cut_out[cut_out <= 0] = 1.0e-20
 

### 2016-06-03 scripts/train_cnn.py
update train_cnn.py

@@ -172,8 +172,8 @@ class TrainSplit(object):
 
     def __call__(self, X, y, net):
         if self.eval_size:
-            X_train, y_train = X[:-eval_size], y[:-eval_size]
-            X_valid, y_valid = X[-eval_size:], y[-eval_size:]
+            X_train, y_train = X[:-self.eval_size], y[:-self.eval_size]
+            X_valid, y_valid = X[-self.eval_size:], y[-self.eval_size:]
         else:
             X_train, y_train = X, y
             X_valid, y_valid = _sldict(X, slice(len(y), None)), y[len(y):]

### 2016-06-03 scripts/train_cnn.py
update train_cnn script

@@ -39,17 +39,14 @@ from lasagne.init import Orthogonal, Constant
 from nolearn.lasagne import NeuralNet
 from nolearn.lasagne import BatchIterator
 from lasagne.nonlinearities import softmax
-from sklearn.utils import shuffle
 
 import bmc
 
-X = np.load("sdss_training_images.npy")
+X = np.load("../data/sdss_training_images.npy")
 print("X.shape = {}, X.min = {}, X.max = {}".format(X.shape, X.min(), X.max()))
 
-y = np.load("sdss_training_labels.npy")
+y = np.load("../data/sdss_training_labels.npy")
 print("y.shape = {}, y.min = {}, y.max = {}".format(y.shape, y.min(), y.max()))
-
-X, y = shuffle(X, y)
 
 def renormalize(array):
     return (array - array.min()) / (array.max() - array.min())
@@ -274,17 +271,17 @@ net = NeuralNet(
     ],
 
     verbose=2,
-    train_split=TrainSplit(eval_size=10000)
+    train_split=TrainSplit(eval_size=15000)
     )
 
 
 net.fit(X, y)
             
-best_valid_loss = min([row['valid_loss'] for row in net50k.train_history_])
+best_valid_loss = min([row['valid_loss'] for row in net.train_history_])
 print("Best valid loss: {}".format(best_valid_loss))
 
-X_valid = np.load("sdss_valid_images.npy")
-y_valid = np.load("sdss_valid_labels.npy")
+X_valid = X[-15000:]
+y_valid = y[-15000:]
 
 for i in range(5):
     X_valid[:, i, :, :] = renormalize(X_valid[:, i, :, :])
@@ -292,6 +289,68 @@ for i in range(5):
 y_valid = renormalize(y_valid).astype(np.int32)
 
 y_pred_valid = np.zeros((len(y_valid), 64))
+
+class AugmentedBatchIterator(BatchIterator):
+
+    def __init__(self, batch_size, crop_size=8, validation=False, testing=False, startx=None, starty=None, rotate=None):
+        super(AugmentedBatchIterator, self).__init__(batch_size)
+        self.crop_size = crop_size
+        self.validation = validation
+        self.testing = testing
+        self.startx, self.starty = startx, starty
+        self.rotate = rotate
+
+    def transform(self, Xb, yb):
+
+        Xb, yb = super(AugmentedBatchIterator, self).transform(Xb, yb)
+        batch_size, nchannels, width, height = Xb.shape
[…]

### 2016-06-11 paper/main.tex
add backprop citation
minor fixes and updates

@@
 We present a star-galaxy classification framework that uses
-a deep convolutional neural network (ConvNet) directly on the raw pixel values.
+deep convolutional neural networks (ConvNets) directly on the raw pixel values.
 Using data from the Sloan Digital Sky Survey (SDSS) and
 the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS),
-we demonstrate that ConvNet is able to produce accurate and well-calibrated
+we demonstrate that ConvNets are able to produce accurate and well-calibrated
 probabilistic classifications that are competitive with
@@
 ivezic2014statistics,
-kamdar2016machine1,kamdar2016machine2}.
-Artificial neural networks were first applied to the problem of star-galaxy
+kamdar2016machine1,kamdar2016machine2}, and
+artificial neural networks were first applied to the problem of star-galaxy
 classification in the work of \citet{odewahn1992automated},
@@
 such as magnitudes or shape information of an object.
-In a branch of machine learning called deep learning,
+In a branch of machine learning called \textit{deep learning},
 features are not designed by human experts;
-they are learned from data by deep neural networks.
+they are learned directly from data by deep neural networks.
 Deep learning has been applied successfully to galaxy morphological
@@
   \caption{
-    The color-color space distribution of stars and galaxies in the SDSS data
-    set. It is easy to see that there is significant overlap between stars
+    Hexbin plots showing the color-color space distribution of stars and
+    galaxies in the SDSS data set.
+    It is easy to see that there is significant overlap between stars
     and galaxies in the color-color space. 
@@
 The Sloan Digital Sky Survey~\citep[SDSS;][]{york2000sloan}
-phases I--III obtained photometric data in five bands:
+phases I--III obtained photometric data in five bands,
 $u$, $g$, $r$, $i$, and $z$,
@@
 which is publicly available through the online CasJobs
-server~\footnote{http://skyserver.sdss.org/casjobs/}~\citep{li2008casjobs}.
+server\footnote{http://skyserver.sdss.org/casjobs/}~\citep{li2008casjobs}.
 
@@
 We exclude some bad photometric observations as follows.
-We consider only objects whose $r$ band magnitude is less than 40;
+We consider only objects whose $r$-band magnitude is less than 40;
 there are no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
@@
 We use the astrometry information in the FITS headers
-in the \texttt{Montage}~\footnote{http://montage.ipac.caltech.edu/} software
+in the \texttt{Montage}\footnote{http://montage.ipac.caltech.edu/} software
 to align each image to the reference ($r$-band) image.
@@
 Figure~\ref{fig:sdss_color_color}.
-We randomly split the objects into training, hold-out validation,
+We randomly split the objects into training, held-out validation,
 and blind test sets of size $40\,000$, $10\,000$, and $15\,000$, respectively.
@@
   \caption{
-    The color-color space distribution of stars and galaxies in the CFHTLenS data
-    set.
+    Hexbin plots showing the color-color space distribution of stars and
+    galaxies in the CFHTLenS data set.
   }
@@
 Finally, images are downscaled to $48\times48$ pixels
-to reduce reduce computational cost.
+to reduce computational cost.
 
@@
 Figure~\ref{fig:clens_color_color}.
-We randomly split the objects into training, hold-out validation, and
+We randomly split the objects into training, held-out validation, and
 blind test sets of size $40\,000$, $10\,000$, and $13\,278$, respectively.
@@
 $\bmath{w}=\left(w_1,w_2,\dots,w_n\right)$ be a vector of weights, and
-$\bmath{b}$ be the bias.
+$b$ be the bias.
 Then, the output of the neuron is
@@
 \end{equation}
-where $\hat{y}_j$ is the actual truth value (\eg 0 or 1) of the $j$-th data and
+where $\hat{y}_j$ is the actual truth value (\eg 0 or 1) of the $j$-th data, and
 $y_j$ is the probability prediction made by the model.
@@
 The gradients in \ref{eq:gradient_descent} can be computed using the
-\textit{backpropagation} procedure, which is nothing more than an application of
-the chain rule for derivatives.
+\textit{backpropagation} procedure~\citep{rumelhart1988learning},
+which is nothing more than an application of the chain rule for derivatives.
 The derivative of the loss function with respect to the input of a unit can be
@@
     \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}   \\
-  \frac{ \partial L }{ \partial x_i } &=
-    \frac{ \partial L }{ \partial y_i }
-    \frac{ \partial y_i }{ \partial x_i }.
+  \frac{ \partial L }{ \partial x_j } &=
+    \frac{ \partial L }{ \partial y_j }
+    \frac{ \partial y_j }{ \partial x_j }.
 \end{align}
-Finally, once the gradients $\partial L / \partial x_i$ have been
+Finally, once the gradients $\partial L / \partial x_j$ have been
 computed, it is straightforward to compute the gradients for the weight,
 \begin{equation}
-\frac{\partial L}{\partial w_{ji}} = y_j \frac{\partial L}{\partial x_i}.
+\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
 \end{equation}
@@
 
-The Convolutional neural network~\citep[ConvNet;][]{fukushima1980neocognitron,lecun1998gradient}
+The convolutional neural network~\citep[ConvNet;][]{fukushima1980neocognitron,lecun1998gradient}
 is a type of deep, feedforward neural network
@@
 but we find that using magnitudes in all five bands $ugriz$ yields the best performance.
+
 The leaky ReLU non-linearity is applied to the output of the first convolutional layer
@@
 conditions~\citep{saxe2013exact}.
-We use a slightly positive value $b=0.1$ for all biases.
+We use slightly positive values ($b=0.01$ or $0.1$) for all biases.
 We find initializing biases to a small constant value helps eliminate dead neurons
@@
 
-We note that our network takes about 40 hours to train the networks on a NVIDIA Tesla K40 GPU.
+We note that training our network takes about 40 hours on a NVIDIA Tesla K40 GPU.
 
@@
 Each cropping is equivalent to randomly shifting a $44\times44$ image by up to 4 pixels
-vertically and horizontally. }
+vertically and/or horizontally. }
 \item{Gaussian noise:
@@
 
-In this section, we first describe the performance metrics we use to evaluate
-the models. We then present the classification performance of our ConvNet model
-on CFHTLenS and SDSS data sets, and compare it with the performance of TPC.
+In this section, we first describe the performance metrics that were used for
+evaluating the models.
+We then present the classification performance of our ConvNet model
+on the CFHTLenS and SDSS data sets, and compare it with the performance of TPC.
 
@@
   $p_g(c_g=x)$ & Galaxy purity at $x$ galaxy completeness \\
-  $p_s(c_s=x)$ & Star purity at $x$ star completeness \\
+  $c_s(p_s=x)$ & Star completeness at $x$ star purity \\
   $CAL$ & Calibration error with overlapping binning \\
@@
 The MSE can be considered as both a score function that quantifies
-how well a set of probabilistic predictions are calibrated,
+how well a set of probabilistic predictions is calibrated,
 or a loss function.
@@
   \includegraphics[width=\columnwidth]{figures/clens_mag.pdf}
-  \caption{Galaxy completeness and star purity values as functions
+  \caption{Galaxy purity and star completeness values as functions
            of the $i$-band magnitude
@@
     (blue dashed line), and $\rmn{TPC}_{\rmn{phot}}$ (yellow dashed line).
-    The lower panel compares the star completeness.
+    The lower panel compares the star completeness values.
     The $1 \sigma$ error bars are computed following the method
@@
       $\rmn{TPC}_{\rmn{morph}}$.
-      $P_{\rmn{tpc}}$ is the probabilistic output generated by ConvNet.}
+      $P_{\rmn{tpc}}$ is the probabilistic output generated by $\rmn{TPC}_{\rmn{morph}}$.}
     \label{fig:clens_calibration_tpc}
@@
 
-As descrbied in Section~\ref{sec:convnet},
-we train our ConvNet model by monitoring its performance on the validatoin set.
-Once we have finished training our model,
+As described in Section~\ref{sec:convnet},
+we train our ConvNet model by monitoring its performance on the validation set.
+Once we have finished training the model,
 we evaluate its performance on the blind test set.
@@
 
-In Figure~\ref{fig:clens_mag}, we compare the galaxy completeness
-and star purity values for ConvNet and TPC as functions of $i$-band magnitude
+In Figure~\ref{fig:clens_mag}, we compare the galaxy purity
+and star completeness values for ConvNet, $\rmn{TPC}_{\rmn{morph}}$, and
+$\rmn{TPC}_{\rmn{phot}}$, as functions of $i$-band magnitude
 for the differential counts.
@@
 with the Gaussian kernel.
-As the first panel shows, KDE is able to smooth the fluctutions in the distribution
+As the first panel shows, KDE is able to smooth the fluctuations in the distribution
 without binning.
 While ConvNet shows a slightly better performance than $\rmn{TPC}_{\rmn{morph}}$
-in galaxy purity, the star completeness plots for ConvNet and TPC
-are nearly identical.
+in galaxy purity,
+ConvNet performs slightly worse than $\rmn{TPC}_{\rmn{morph}}$ in star completeness.
 Again, $\rmn{TPC}_{\rmn{phot}}$ performs significantly worse than both
-ConvNet and TPC, and this suggests that ConvNets are able to learn
+ConvNet and $\rmn{TPC}_{\rmn{morph}}$, and this suggests that ConvNets are able to learn
 the shape information automatically from the images.
@@
 integrated counts.
-ConvNet is able to mantain a galaxy purity of 0.9972 up to $i\sim24.5$,
+ConvNet is able to maintain a galaxy purity of 0.9972 up to $i\sim24.5$,
 while the galaxy purity of $\rmn{TPC}_{\rmn{morph}}$ drops to 0.9963.
@@
   \includegraphics[width=\columnwidth]{figures/sdss_mag.pdf}
-  \caption{Galaxy ompleteness and star purity as function of the $r$-band
+  \caption{Galaxy purity and star completeness as function of the $r$-band
     magnitude for the differential counts in the SDSS data set.}
@@
   \includegraphics[width=\columnwidth]{figures/sdss_integrated.pdf}
-  \caption{Galaxy completeness and star purity as functions of the $r$-band
+  \caption{Galaxy purity and star completeness as functions of the $r$-band
     magnitude for the integrated counts in the SDSS data set.}
@@
 in all metrics except $\rmn{CAL}$.
-Both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ still outperforms
+Both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ still outperform
 $\rmn{TPC}_{\rmn{phot}}$ in all six metrics by a significant amount, as
 magnitudes and colors alone are not sufficient to separate stars from galaxies.
-Alhtough ConvNet performs worse than $\rmn{TPC}_{\rmn{morph}}$ on the SDSS
+Although ConvNet performs worse than $\rmn{TPC}_{\rmn{morph}}$ on the SDSS
 data, its performance is much closer to $\rmn{TPC}_{\rmn{morph}}$, as ConvNet
@@
 
-In Figure~\ref{fig:sdss_mag}, we compare the galaxy completeness
-and star purity values for ConvNet and $\rmn{TPC}_{\rmn{morph}}$ as
-functions of $i$-band magnitude for the differential counts in the SDSS data.
+In Figure~\ref{fig:sdss_mag}, we compare the galaxy purity
+and star completeness values for ConvNet, $\rmn{TPC}_{\rmn{morph}}$, and
+$\rmn{TPC}_{\rmn{phot}}$ as
+functions of $r$-band magnitude for the differential counts in the SDSS data.
 We note that $\rmn{TPC}_{\rmn{morph}}$ outperforms the star-galaxy
 classifier used by the SDSS pipeline (\ie an object is classified as a galaxy
-if the concentration parameter is greater than 0.145) over all magnitudes.
+if $\rmn{concentration} > 0.145$) over all magnitudes.
 We do not show the SDSS classifications to avoid cluttering the plots.
@@
 
-Figure~\ref{fig:sdss_calibration_conv} and \ref{fig:sdss_calibration_tpc}
+Figures~\ref{fig:sdss_calibration_conv} and \ref{fig:sdss_calibration_tpc}
 show the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$,
 respectively.
-Compared to Figure~\ref{fig:clens_calibration_conv},
-when our ConvNet is applied to the SDSS data set,
-its calibration curve is not as well-calibrated as when it is applied to the
-CFHTLenS data set. 
+The calibration curve of ConvNet in Figure~\ref{fig:sdss_calibration_conv}
+is not as well-calibrated as the calibration curve in
+Figure~\ref{fig:clens_calibration_conv},
+where the same ConvNet model was applied to the CFHTLenS data set.
+However, ConvNet may still be better calibrated than $\rmn{TPC}_{\rmn{morph}}$,
+even when it is applied to the SDSS data set.
 Although it is not straightforward to compare the two calibration curves by
-visual inspection, Table~\ref{table:sdss_metrics} shows that the CAL metrics of
-ConvNet is lower than that of TPC.
+visual inspection, Table~\ref{table:sdss_metrics} shows that the CAL metric of
+ConvNet is lower than that of $\rmn{TPC}_{\rmn{morph}}$.
 
@@
 designing a feature extractor.
-The lack of requirement for feature extraction is a huge advantage \eg
+The lack of requirement for feature extraction is a huge advantage, \eg
 when the task is to classify $1\,000$ classes in the ImageNet data
@@
 as a good feature extractor for identifying images of cats would of little use
-for classifying sailboats, and it is impractical to design a feature extractor
-for each class.
+for classifying sailboats, and it is impractical to design a separate
+feature extractor for each class.
 However, when there already exists a good feature extractor for the problem
@@
 or even the \texttt{SExtractor} software,
-conventional machine learning algorithms that are proven to be effective,
+conventional machine learning algorithms that have been shown to be effective,
 such as TPC~\citep{carrascokind2013tpz, kim2015hybrid}, remain a viable option.
@@
 there is no one model that works for every problem.
-For the CFHTLenS data set, our ConvNet model outperforms TPC trained on the
-output of \texttt{SExtractor}.
-Since the SDSS catalog provides the concentration paramter that is highly
+For the CFHTLenS data set, our ConvNet model outperforms TPC.
+Since the SDSS catalog provides the concentration parameter that is highly
 optimized for star-galaxy classification, TPC works better for SDSS.
@@
 with different architectures and combine the models.
-The winning solution of \cite{dieleman2015rotation}
+For example, the winning solution of \cite{dieleman2015rotation}
 for the Galaxy Zoo challenge was based on a ConvNet model,

### 2016-06-18 paper/main.tex
added robert's comments

@@
 
+\newcommand{\RC}[1]{{\color{red}\textbf{Robert Comment: #1\ }}}
+
 \pdfminorversion=5
@@
 requiring careful feature extraction and selection.
-The latest advances in machine learning using deep convolutional neural networks
+The latest advances in machine learning that use deep convolutional neural networks
 allow a machine to automatically learn the features directly from data,
-minimizing need for input from human experts.
+minimizing the need for input from human experts.
 We present a star-galaxy classification framework that uses
-deep convolutional neural networks (ConvNets) directly on the raw pixel values.
+deep convolutional neural networks (ConvNets) directly on the reduced, calibrated pixel values.
 Using data from the Sloan Digital Sky Survey (SDSS) and
@@
 conventional machine learning techniques.
-Future advances in deep learning may bring more success in currently ongoing and
+Future advances in deep learning may bring more success with current and
 forthcoming photometric surveys, such as the Dark Energy Survey (DES) and
 the Large Synoptic Survey Telescope (LSST), because deep neural networks require
-very little feature engineering by hand.
+very little, manual feature engineering.
 \end{abstract}
@@
 or to optimize the allocation of observing time by selecting objects for follow-up.
-However, ideally, the probability estimates themselves would be retained for all sources
+Ideally, however, the probability estimates themselves would be retained for all sources
 and used in subsequent analyses to improve or enhance a particular
@@
 ivezic2014statistics,
-kamdar2016machine1,kamdar2016machine2}, and
-artificial neural networks were first applied to the problem of star-galaxy
+kamdar2016machine1,kamdar2016machine2}. 
+Artificial neural networks were first applied to the problem of star-galaxy
 classification in the work of \citet{odewahn1992automated},
-which has become a core part of the astronomical image processing software
+and they have become a core part of the astronomical image processing software
 \texttt{SExtractor}~\citep{bertin1996sextractor}.
@@
 the star-galaxy classification problem include decision 
-trees~\citep{weir1995automated,suchkov2005census,ball2006robust,sevilla2015effect}
-, Support Vector Machines~\citep{Fadely2012}, and
+trees~\citep{weir1995automated,suchkov2005census,ball2006robust,sevilla2015effect}, 
+Support Vector Machines~\citep{Fadely2012}, and
 classifier combination strategies~\citep{kim2015hybrid}.
@@
 Constructing catalogs requires careful engineering and considerable domain expertise
-to transform the raw pixel values of an image to suitable features,
+to transform the reduced, calibrated pixel values that comprise an image into suitable features,
 such as magnitudes or shape information of an object.
@@
 estimation~\citep{hoyle2015measuring},
-but it has never been applied to the problem of source classification.
+but it has not yet been applied to the problem of source classification.
+
+\RC{FYI, a raw pixel value is observed directly from the telescope and is generally worthless.
+It must be reduced (correcting for the optics of the telescope and observational imprints) and calibrated (so that photon counts mean a physical value) before being useful in any sense.}
 
@@
 that uses a convolutional neural network (ConvNet) model directly on the images
-from SDSS and Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS).
+from the SDSS and the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS).
 We compare its performance with a standard machine learning technique
 that uses the reduced summary information from catalogs,
-and demonstrate that our ConvNet model is able to produce accurate and
+and we demonstrate that our ConvNet model is able to produce accurate and
 well-calibrated probabilistic classifications with very little feature
@@
   \caption{
-    Hexbin plots showing the color-color space distribution of stars and
-    galaxies in the SDSS data set.
+    Hexbin plots showing the color-color space distribution of galaxies (blue, top row) and stars (green, bottom row)
+    in the SDSS data set used in this analysis.
     It is easy to see that there is significant overlap between stars
-    and galaxies in the color-color space. 
+    and galaxies in these color-color spaces. 
   }
@@
 \end{figure}
+
+\RC{It might be helpful to have a colorbar with these plots to show relative densities.
+I also wonder if the extra whitespace might be reduced somehow.
+Finally, I actually think a ratio plot might be best her, where the hexbin shows the ratio of the normalized counts.}
 
@@
 covering 14,555 square degrees, more than one-third of the entire sky.
-The resulting catalog contains photometry of over 300 million stars galaxies
+The resulting catalog contains photometry of over 300 million stars and galaxies
 with a limiting magnitude of $r \approx 22$,
@@
 
-Using the CasJobs server, we randomly select $65\,000$ stars and galaxies.
+Using the CasJobs server, we randomly select a total of 65,000 sources, which are either stars or galaxies.
 We exclude some bad photometric observations as follows.
@@
 \citep[also known as luptitudes;][]{lupton1999modified}.
-Finally, in order to account for the effect of galactic dust,
-galactic extinction corrections in magnitudes are applied
+Finally, in order to account for the effect of Galactic dust,
+extinction corrections in magnitudes are applied
 following \cite{schlegel1998maps}.
@@
 
-In the end, we have $17\,344$ stars and $47\,656$ galaxies available
+In the end, we have 17,344 stars and 47,656 galaxies available
 for the training and testing processes.
@@
 We randomly split the objects into training, held-out validation,
-and blind test sets of size $40\,000$, $10\,000$, and $15\,000$, respectively.
+and blind test sets of size 40,000, 10,000, and 15,000, respectively.
 We note that cross-validation is often avoided in deep learning
@@
 
+\RC{Be useful to state what the ratio of Stars to galaxies are in these three data sets (train, validate, test). Also, a referee will likely ask how they are distributed in magnitude and color.}
+
 \subsection{Canada-France-Hawaii Telescope Lensing Survey}
@@
     Hexbin plots showing the color-color space distribution of stars and
-    galaxies in the CFHTLenS data set.
+    galaxies in the CFHTLenS data set used in this analysis.
   }
@@
 in the four fields (named W1, W2, W3, and W4)
-of CFHT Legacy Survey~\citep[CFHTLS;][]{gwyn2012canada}
+of the CFHT Legacy Survey~\citep[CFHTLS;][]{gwyn2012canada}
 observed in the five photometric bands:
@@
 Finally, images are downscaled to $48\times48$ pixels
-to reduce computational cost.
-
-In the end, we have $8\,545$ stars and $57\,843$ galaxies available
+to reduce the computational cost.
+
+In the end, we have 8,545 stars and 57,843 galaxies available
 for the training and testing processes.
@@
 
+\RC{ Again the S:G ratio in the data sets and mag and color distributions. Referee will likely ask, so you can put something in here to simplify review process.}
 \section{Deep Learning}
@@
 The sigmoid function, $\sigma(x)=1/\left(1+e^{-x}\right)$,
-has frequently been used as activation function, but it has recently fallen out of favor,
-and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$, is almost always used instead.
+has frequently been used as an activation function, but it has recently fallen out of favor,
+and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$, is generally used instead.
 The most popular non-linearity at present, however, is the rectified linear unit
@@
 relationships, and they have had great success in multimedia tasks where humans traditionally
-outperformed computers: speech recognition, language processing, and image classification.
+outperformed computers, such as speech recognition, language processing, and image classification.
 
@@
 
+\RC{You do not talk anywhere on the software you actually use to do this work.
+You should introduce Python, Lasagna, Theano, and any other relevant software.
+You also should cite them.
+Finally, what hardware was used for these tests?}
+
 \subsection{Neural Network Architecture}
@@
   \centering
-  \caption{Summary of ConvNet architecture and hyperparameters. Note that pooling layers have no learnable parameters.}
+  \caption{Summary of ConvNet architecture and hyperparameters.
+Note that pooling layers have no learnable parameters.
+\RC{ This might be much easier to understand if it is a flowchart, like we did in INFO490 with Keras.
+Is that possible?
+I say this as it would better  match your toy ANN in  a previous figure.}}
   \label{table:hyperparamters}
@@
 
+\RC{ I wonder why? Is this somehow relevant?}
+
 We have performed a manual search to explore more than 200 combinations of different architectures
@@
 the SDSS validation set.
-To test how this model performs across different, related problems,
+To test how this model performs across different, related data,
 we use the same architecture on the CFHTLenS data set.
@@
 
-We note that training our network takes about 40 hours on a NVIDIA Tesla K40 GPU.
+We note that training our network takes about forty hours on an NVIDIA Tesla K40 GPU.
 
@@
 As a result, the model is very likely to \emph{overfit} without regularization.
-In this section, we describe the techniques used to combat overfitting.
+In this section, we describe the techniques we used to minimize overfitting.
 
@@
 we reach a predefined number of combinations,
-and finally use Equation~\ref{eq:posterior_bmc} to compute
+and we finally use Equation~\ref{eq:posterior_bmc} to compute
 the posterior probability that a source is a star (or a galaxy).
 In this paper, we use a $q$ value of three,
-and $1\,000$ model combinations are considered.
+and we consider a total of $1\,000$ model combinations.
 
@@
 TPC uses classification trees,
-a type of prediction trees that are designed to
+a type of prediction tree that is designed to
 provide a classification or predict a discrete category.
@@
 maximizes the information gain as defined by Equation~\ref{eq:information_gain},
-and select the attribute that maximizes the impurity index overall.
+and select the attribute that maximizes the overall impurity index.
 
@@
 
-We train two TPC models on the SDSS data set using different sets of
+We train two TPC models on the SDSS data set by using different sets of
 attributes.
@@
 The concentration is defined as the difference between the cmodel
-and PSF magnitude,
-\ie $\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
+and PSF magnitude: $\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
 The SDSS pipeline uses a parametric method based on the concentration,
-\ie an object is classified as a galaxy if $\rmn{concentration}>0.145$.
+an object is classified as a galaxy if $\rmn{concentration}>0.145$.
 We find that the concentration is an excellent morphological feature
@@
 does not show noticeable improvement in performance.
-The concentration is a good example of carefully handcrafted feature extraction,
-and we show in Section~\ref{sec:results_and_discussion}
+The concentration is a good example of carefully handcrafted feature extraction;
+we show in Section~\ref{sec:results_and_discussion}
 that ConvNets do not require such feature engineering.
@@
 to be in one of the classes (\eg a star or a galaxy).
-The simplest way to way to use the probability output is to
+The simplest way to use the probability output is to
 convert it into a class label by using a threshold (a probability cut).
 Although many studies often choose the threshold by setting it to a fixed value,
-\eg $P_{\rmn{cut}} = 0.5$ \citep[\eg][]{henrion2011bayesian, Fadely2012},
+such as $P_{\rmn{cut}} = 0.5$ \citep[\eg][]{henrion2011bayesian, Fadely2012},
 choosing $0.5$ as a threshold is not the best choice
@@
 We also use the mean squared error
-(MSE; also known as Brier score~\citep{brier1950verification})
+(MSE; also known as the Brier score~\citep{brier1950verification})
 as a performance metric. We define MSE as
@@
 
-The problem with binning approach is either too few or too many bins
+\RC{Why 1000 here?}
+
+The problem with a binning approach is either too few or too many bins
 can distort the evaluation of calibration performance.
@@
 We order the predicted values $P_\rmn{class}$ and
-put the first $1\,000$ elements in the first bin.
+put the first 1,000 elements in the first bin.
 We calculate the true probability $P_\rmn{gal}$ by counting the true galaxies
@@
 The calibration error for this bin is $\mid P_\rmn{gal} - P_\rmn{class} \mid$.
-We then repeat this for the second bin (2 to $1\,001$),
-the third bin (3 to $1\,002$), and so on, and average the binned calibration errors.
+We then repeat this for the second bin (2 to 1,001),
+the third bin (3 to 1,002), and so on, and average the binned calibration errors.
 Thus, the overall calibration error is given by
@@
 instead of counting each galaxy equally, a galaxy could be
-counted as $P_{\rmn{class}}$ the probability estimate.
+counted as $P_{\rmn{class}}$, the probability estimate.
 This should in principle remove the contamination effect of stars.
@@
   \caption{Galaxy purity and star completeness values as functions
-           of the $i$-band magnitude
-           as estimated by the kernel density estimation (KDE) method
-           for the differential counts in the CFHTLenS data set.
+           of the $i$-band magnitude (differential counts)
+           as estimated by kernel density estimation (KDE)
+           in the CFHTLenS data set.
            The top panel shows the histogram with a bin size of 0.1 mag
@@
     Galaxy purity and star completeness as functions of the $i$-band
-    magnitude for the integrated counts in the CFHTLenS data set.
+    magnitude (integrated counts) in the CFHTLenS data set.
     The upper panel compares the galaxy
@@
     \caption{
-      Calibration curve for ConvNet as applied to the CFHTLenS data set.
-      $P_{\rmn{gal}}$ is the fraction of objects that are galaxies.
+      The calibration curve for ConvNet as applied to the CFHTLenS data set.
+      $P_{\rmn{gal}}$ is the fraction of objects that are galaxies, and
       $P_{\rmn{conv}}$ is the probabilistic output generated by ConvNet.
@@
     output for one of the learned features.
+    \RC{Note that usually R = Red (i-band), G = Green (r-band), and B = Blue (g-band)}
     }
@@
 and star completeness values for ConvNet, $\rmn{TPC}_{\rmn{morph}}$, and
-$\rmn{TPC}_{\rmn{phot}}$, as functions of $i$-band magnitude
+$\rmn{TPC}_{\rmn{phot}}$, as a function of  $i$-band magnitude
 for the differential counts.
-We use the kernel density estimation~\citep[KDE;][]{silverman1986density}
-with the Gaussian kernel.
+We use  kernel density estimation~\citep[KDE;][]{silverman1986density}
+with a Gaussian kernel.
 As the first panel shows, KDE is able to smooth the fluctuations in the distribution
@@
 In Figure~\ref{fig:clens_integrated}, we show the overall galaxy purity
-and star completeness values as functions of $i$-band magnitude for the
+and star completeness values as a function of $i$-band magnitude for the
 integrated counts.
@@
 and star completeness values for ConvNet, $\rmn{TPC}_{\rmn{morph}}$, and
-$\rmn{TPC}_{\rmn{phot}}$ as
-functions of $r$-band magnitude for the differential counts in the SDSS data.
+$\rmn{TPC}_{\rmn{phot}}$ as a
+function of $r$-band magnitude for the differential counts in the SDSS data.
 We note that $\rmn{TPC}_{\rmn{morph}}$ outperforms the star-galaxy
@@
 
+\RC{I wonder if augmentation hurts us here, since we are populating our training data with more faint, and confusing objects? Mag distribution of stars and galaxies might help clarify this point.}
+
 In Figure~\ref{fig:sdss_integrated}, we show the overall galaxy purity
-and star completeness values as functions of magnitude for the integrated
+and star completeness values as a function of magnitude for the integrated
 counts.
@@
 
-We also show the galaxy purity and star completeness values as functions of
+We also show the galaxy purity and star completeness values as a function of
 $g-r$ color in Figure~\ref{fig:sdss_g_r}.
@@
 where the stellar fraction is relatively low.
-Both $\rmn{TPC}_{\rmn{morph}}$ and $\rmn{TPC}_{\rmn{phot}}$ outperform
+On the other hand, both $\rmn{TPC}_{\rmn{morph}}$ and $\rmn{TPC}_{\rmn{phot}}$ outperform
 ConvNet in the region $g-r \la 0.8$ where the stellar fraction is higher.
@@
 algorithms require feature engineering as a separate process
-to provide produce accurate classifications.
+to produce accurate classifications.
 
@@
 The lack of requirement for feature extraction is a huge advantage, \eg
-when the task is to classify $1\,000$ classes in the ImageNet data
+when the task is to classify 1,000 classes in the ImageNet data
 set~\citep{russakovsky2015imagenet},
-as a good feature extractor for identifying images of cats would of little use
+as a good feature extractor for identifying images of cats would be of little use
 for classifying sailboats, and it is impractical to design a separate
@@
 If enough training data become available in DES or LSST, ConvNets
-become an attractive option because it can be applied immediately on raw images
+become an attractive option because it can be applied immediately on reduced, calibrated images
 to produce well-calibrated posterior probabilities.
-We also note that using more training images will require the use of multi-GPU,
+We also note that using more training images will require the use of multi-GPU systems,
 which was beyond the scope of the present work.
 
-Deep learning is a rapidly developing field and recent developments include
+Deep learning is a rapidly developing field, and recent developments include
 improved network architectures.
@@
 
-It is also likely that the performance will be improved by,
-not only training multiple network architectures,
-but also combining with different star-galaxy classifiers.
+It is also likely that the performance will be improved
+not only by training multiple network architectures,
+but also by combining them with different star-galaxy classifiers.
 In \citet{kim2015hybrid}, we combined a purely morphological classifier,

### 2016-06-18 paper/main.tex
update paper

@@
 
-\RC{FYI, a raw pixel value is observed directly from the telescope and is generally worthless.
-It must be reduced (correcting for the optics of the telescope and observational imprints) and calibrated (so that photon counts mean a physical value) before being useful in any sense.}
-
 In this paper, we present a star-galaxy classification framework
@@
 way to train or calibrate the algorithms.
-
 \RC{Be useful to state what the ratio of Stars to galaxies are in these three data sets (train, validate, test). Also, a referee will likely ask how they are distributed in magnitude and color.}
+\textcolor{cyan}{
+The first two panels of Figure~\ref{fig:sdss_mag} show the number of objects
+and the fraction of stars in the test set as functions of $r$-band magnitude.
+Similarly, Figure~\ref{fig:sdss_g_r} shows the number of objects and the
+fraction of stars in the test set as functions of $g-r$ color.
+The normalized kernel density estimate distributions for the training set
+and validation sets are almost identical to those of the test set,
+and they are nearly indistinguishable when overlapped.
+We do not show the distributions for the training and validation sets in
+Figures~\ref{fig:sdss_mag} and \ref{fig:sdss_g_r} to avoid cluttering the
+plots.
+}
 
@@
 blind test sets of size $40\,000$, $10\,000$, and $13\,278$, respectively.
-
 \RC{ Again the S:G ratio in the data sets and mag and color distributions. Referee will likely ask, so you can put something in here to simplify review process.}
+\textcolor{cyan}{
+Figures~\ref{fig:clens_mag} and \ref{fig:clens_g_r} show the distribution
+of objects in the test set as functions of $r$-band magnitude and $g-r$ color.
+We do not show the distributions for the training and validation sets,
+since the normalized kernel density estimate distributions for the training set
+and validation sets are almost identical to those of the test set.
+}
+
 \section{Deep Learning}
@@
 We note that training our network takes about forty hours on an NVIDIA Tesla K40 GPU.
+\textcolor{cyan}{
+To implement our model, we use Python and the Lasagne
+library~\citep{dieleman2015lasagne}, which is built on top of
+Theano~\citep{theano2016theano}.
+In the interest of scientific reproducibility, we make all our code available at
+\href{https://github.com/EdwardJKim/dl4astro}{https://github.com/EdwardJKim/dl4astro}.  
+}
 
@@
 We order the predicted values $P_\rmn{class}$ and
-put the first 1,000 elements in the first bin.
+put the first $1\,000$ elements in the first bin.
 We calculate the true probability $P_\rmn{gal}$ by counting the true galaxies
@@
 The calibration error for this bin is $\mid P_\rmn{gal} - P_\rmn{class} \mid$.
-We then repeat this for the second bin (2 to 1,001),
-the third bin (3 to 1,002), and so on, and average the binned calibration errors.
+We then repeat this for the second bin (2 to $1\,001$),
+the third bin (3 to $1\,002$), and so on, and average the binned calibration errors.
 Thus, the overall calibration error is given by
@@
     (a) A sample $44\times44$ RGB image of a galaxy in the CFHTLenS data set.
-    The RGB image is created by mapping R $\rightarrow g$ band magnitude,
-    G $\rightarrow r$ band magnitude, and B $\rightarrow i$ band magnitude.
+    \textcolor{cyan}{
+    The RGB image is created by mapping R $\rightarrow i$ band magnitude,
+    G $\rightarrow r$ band magnitude, and B $\rightarrow g$ band magnitude.
+    }
     (b) Activations on the first convolutional layer when a $5\times44\times44$
@@
 galaxies in the SDSS and CFHTLenS photometric images.
-In the interest of scientific reproducibility, we make all our code available at
-\href{https://github.com/EdwardJKim/dl4astro}{https://github.com/EdwardJKim/dl4astro}.  
 For the CFHTLenS data set, the network is able to provide a classification that

### 2016-06-20 paper/main.tex
added colorbars to color-color diagrams

@@
 Finally, I actually think a ratio plot might be best her, where the hexbin shows the ratio of the normalized counts.}
+\textcolor{magenta}
+{
+I added colorbars.
+I don't see how I can reduce the whitespace further.
+I tried creating a ratio plot (see \url{https://github.com/EdwardJKim/dl4astro/blob/master/paper/figures/sdss_color_color.test.pdf}) but I think I prefer separate color-color diagrams for stars and galaxies.
+If you think the ratio plot is better, I can polish the linked ratio plot and replace the color-color diagrams with ratio plots.
+}
 
@@
 We then use \texttt{SExtractor} to find the pixel positions of
-the $65\,000$ objects we have selected,
+the 65,000 objects we have selected,
 and to center each object in the cutout image.
@@
   \caption{
-    Hexbin plots showing the color-color space distribution of stars and
-    galaxies in the CFHTLenS data set used in this analysis.
+    Hexbin plots showing the color-color space distribution of
+    galaxies (blue, top row) and stars (green, bottom row)
+    in the CFHTLenS data set used in this analysis.
   }
@@
 We randomly split the objects into training, held-out validation, and
-blind test sets of size $40\,000$, $10\,000$, and $13\,278$, respectively.
+blind test sets of size 40,000, 10,000, and 13,278, respectively.
 \RC{ Again the S:G ratio in the data sets and mag and color distributions. Referee will likely ask, so you can put something in here to simplify review process.}
@@
 
-\RC{You do not talk anywhere on the software you actually use to do this work.
-You should introduce Python, Lasagna, Theano, and any other relevant software.
-You also should cite them.
-Finally, what hardware was used for these tests?}
-
 \subsection{Neural Network Architecture}
@@
 \RC{ I wonder why? Is this somehow relevant?}
+\textcolor{magenta}{ I don't know.
+I treated regression vs classification problem as just another hyperparamter I have to choose.
+Using classification mode + softmax was simply a better hyperparamter for the problem.
+}
 
@@
 
-We note that training our network takes about forty hours on an NVIDIA Tesla K40 GPU.
+\RC{You do not talk anywhere on the software you actually use to do this work.
+You should introduce Python, Lasagna, Theano, and any other relevant software.
+You also should cite them.
+Finally, what hardware was used for these tests?}
 \textcolor{cyan}{
@@
 }
+We note that training our network takes about forty hours on an NVIDIA Tesla K40 GPU.
 
@@
 In this paper, we use a $q$ value of three,
-and we consider a total of $1\,000$ model combinations.
+and we consider a total of 1,000 model combinations.
 
@@
 \RC{Why 1000 here?}
+\textcolor{magenta}{It's somewhat arbitrary.
+Number of ojbects in the test set / Number of bins in the calibration curve = 15000 / 10 = 1500.
+So about 1000, rounded down.
+But I could have chosen 100 or 10000 or any other number.
+Do you think I need a reason here?}
 
@@
 \end{equation}
-where $s=1\,000$ is the bin length.
+where $s=1000$ is the bin length.
 
@@
     \RC{Note that usually R = Red (i-band), G = Green (r-band), and B = Blue (g-band)}
+    \textcolor{magenta}{Fixed}
     }
@@
 ConvNet is able to learn the morphological features automatically from
-the raw images, and the performance of ConvNet is therefore comparable to
+the images, and the performance of ConvNet is therefore comparable to
 that of $\rmn{TPC}_{\rmn{morph}}$,
@@
 data, its performance is much closer to $\rmn{TPC}_{\rmn{morph}}$, as ConvNet
-is able to learn the shape information automatically from the raw images.
+is able to learn the shape information automatically from the images.
 
@@
 The major advantage of ConvNets is that useful features are learned
-automatically from raw pixel values, while traditional machine learning
+automatically from images, while traditional machine learning
 algorithms require feature engineering as a separate process

### 2016-06-20 paper/main.tex
added a flowchart

@@
 Is that possible?
-I say this as it would better  match your toy ANN in  a previous figure.}}
+I say this as it would better  match your toy ANN in  a previous figure.}
+\textcolor{magenta}{
+Please see \url{https://github.com/EdwardJKim/dl4astro/blob/master/paper/figures/layers.png}.
+I can make this one look better and include it, but I would rather not include it if you are OK with it, because I don't think it adds any further information.
+It seems to me the flowchart is basically each row in the below table connected with arrows.
+}
+  }
   \label{table:hyperparamters}
@@
 Theano~\citep{theano2016theano}.
-In the interest of scientific reproducibility, we make all our code available at
-\href{https://github.com/EdwardJKim/dl4astro}{https://github.com/EdwardJKim/dl4astro}.  
-}
-We note that training our network takes about forty hours on an NVIDIA Tesla K40 GPU.
+The Theano library simplifies the use of GPU for computation, and using the GPU
+allows about an order of magnitude faster training than using just the CPU.
+}
+We note that training our network takes about forty hours on an NVIDIA Tesla
+K40 GPU.
+In the interest of scientific reproducibility, we make all our code available
+at \href{https://github.com/EdwardJKim/dl4astro}{https://github.com/EdwardJKim/dl4astro}.
 

### 2016-06-21 paper/main.tex
added response to comments

@@
 I don't see how I can reduce the whitespace further.
-I tried creating a ratio plot (see \url{https://github.com/EdwardJKim/dl4astro/blob/master/paper/figures/sdss_color_color.test.pdf}) but I think I prefer separate color-color diagrams for stars and galaxies.
-If you think the ratio plot is better, I can polish the linked ratio plot and replace the color-color diagrams with ratio plots.
+I tried creating a ratio plot (see \url{https://github.com/EdwardJKim/dl4astro/blob/master/paper/figures/sdss_color_color.test.pdf}) but I think I prefer separate color-color diagrams for stars and galaxies, because the only reason I included these color-color diagrams is the referee will be an astronomer, and I think a ratio plot will be less familiar to the referee than the conventional plots with number counts.
+If you think a ratio plot is better, I can polish the linked ratio plot and replace the color-color diagrams with ratio plots.
 }
@@
 fraction of stars in the test set as functions of $g-r$ color.
-The normalized kernel density estimate distributions for the training set
+The normalized kernel density estimate distributions for the training
 and validation sets are almost identical to those of the test set,
@@
 Figures~\ref{fig:clens_mag} and \ref{fig:clens_g_r} show the distribution
-of objects in the test set as functions of $r$-band magnitude and $g-r$ color.
+of objects in the test set as functions of $i$-band magnitude and $g-r$ color.
 We do not show the distributions for the training and validation sets,
-since the normalized kernel density estimate distributions for the training set
+since the normalized kernel density estimate distributions for the training
 and validation sets are almost identical to those of the test set.
@@
 Please see \url{https://github.com/EdwardJKim/dl4astro/blob/master/paper/figures/layers.png}.
-I can make this one look better and include it, but I would rather not include it if you are OK with it, because I don't think it adds any further information.
+I can make this one look better and include it, but I would rather not include it if you are OK with it, because I don't think it adds any useful information.
 It seems to me the flowchart is basically each row in the below table connected with arrows.
@@
 But I could have chosen 100 or 10000 or any other number.
-Do you think I need a reason here?}
+Do you think I need a justification here?}
 
@@
 \RC{I wonder if augmentation hurts us here, since we are populating our training data with more faint, and confusing objects? Mag distribution of stars and galaxies might help clarify this point.}
+\textcolor{magenta}{
+Even if we are populating our training data with fainter objects, augmentation still improves the overall performance on the validation set, so I don't think augmentation hurts us.
+}
 

### 2016-06-24 paper/main.tex
remove comments

@@
 
-\newcommand{\RC}[1]{{\color{red}\textbf{Robert Comment: #1\ }}}
-
 \pdfminorversion=5
@@
 
-\RC{It might be helpful to have a colorbar with these plots to show relative densities.
-I also wonder if the extra whitespace might be reduced somehow.
-Finally, I actually think a ratio plot might be best her, where the hexbin shows the ratio of the normalized counts.}
-\textcolor{magenta}
-{
-I added colorbars.
-I don't see how I can reduce the whitespace further.
-I tried creating a ratio plot (see \url{https://github.com/EdwardJKim/dl4astro/blob/master/paper/figures/sdss_color_color.test.pdf}) but I think I prefer separate color-color diagrams for stars and galaxies, because the only reason I included these color-color diagrams is the referee will be an astronomer, and I think a ratio plot will be less familiar to the referee than the conventional plots with number counts.
-If you think a ratio plot is better, I can polish the linked ratio plot and replace the color-color diagrams with ratio plots.
-}
-
 The Sloan Digital Sky Survey~\citep[SDSS;][]{york2000sloan}
@@
 way to train or calibrate the algorithms.
-\RC{Be useful to state what the ratio of Stars to galaxies are in these three data sets (train, validate, test). Also, a referee will likely ask how they are distributed in magnitude and color.}
-\textcolor{cyan}{
 The first two panels of Figure~\ref{fig:sdss_mag} show the number of objects
@@
 plots.
-}
 
@@
 blind test sets of size 40,000, 10,000, and 13,278, respectively.
-\RC{ Again the S:G ratio in the data sets and mag and color distributions. Referee will likely ask, so you can put something in here to simplify review process.}
-\textcolor{cyan}{
 Figures~\ref{fig:clens_mag} and \ref{fig:clens_g_r} show the distribution
@@
 and validation sets are almost identical to those of the test set.
-}
 
@@
   \centering
-  \caption{Summary of ConvNet architecture and hyperparameters.
-Note that pooling layers have no learnable parameters.
-\RC{ This might be much easier to understand if it is a flowchart, like we did in INFO490 with Keras.
-Is that possible?
-I say this as it would better  match your toy ANN in  a previous figure.}
-\textcolor{magenta}{
-Please see \url{https://github.com/EdwardJKim/dl4astro/blob/master/paper/figures/layers.png}.
-I can make this one look better and include it, but I would rather not include it if you are OK with it, because I don't think it adds any useful information.
-It seems to me the flowchart is basically each row in the below table connected with arrows.
-}
-  }
+  \caption{Summary of ConvNet architecture and hyperparameters. Note that pooling layers have no learnable parameters.}
   \label{table:hyperparamters}
@@
 
-\RC{ I wonder why? Is this somehow relevant?}
-\textcolor{magenta}{ I don't know.
-I treated regression vs classification problem as just another hyperparamter I have to choose.
-Using classification mode + softmax was simply a better hyperparamter for the problem.
-}
-
 We have performed a manual search to explore more than 200 combinations of different architectures
@@
 
-\RC{You do not talk anywhere on the software you actually use to do this work.
-You should introduce Python, Lasagna, Theano, and any other relevant software.
-You also should cite them.
-Finally, what hardware was used for these tests?}
-\textcolor{cyan}{
 To implement our model, we use Python and the Lasagne
@@
 allows about an order of magnitude faster training than using just the CPU.
-}
 We note that training our network takes about forty hours on an NVIDIA Tesla
@@
 
-\RC{Why 1000 here?}
-\textcolor{magenta}{It's somewhat arbitrary.
-Number of ojbects in the test set / Number of bins in the calibration curve = 15000 / 10 = 1500.
-So about 1000, rounded down.
-But I could have chosen 100 or 10000 or any other number.
-Do you think I need a justification here?}
-
 The problem with a binning approach is either too few or too many bins
@@
 \end{equation}
-where $s=1000$ is the bin length.
+where $s=1000$ is the bin length, which is chosen approximately equal to
+the number of objects in the testing set divided by the number of bins used in
+the calibration curve, \ie $s \approx N / 10$.
 
@@
     (a) A sample $44\times44$ RGB image of a galaxy in the CFHTLenS data set.
-    \textcolor{cyan}{
     The RGB image is created by mapping R $\rightarrow i$ band magnitude,
     G $\rightarrow r$ band magnitude, and B $\rightarrow g$ band magnitude.
-    }
     (b) Activations on the first convolutional layer when a $5\times44\times44$
@@
     output for one of the learned features.
-    \RC{Note that usually R = Red (i-band), G = Green (r-band), and B = Blue (g-band)}
-    \textcolor{magenta}{Fixed}
     }
@@
 and morphology is not a reliable metric for star-galaxy classification.
-
-\RC{I wonder if augmentation hurts us here, since we are populating our training data with more faint, and confusing objects? Mag distribution of stars and galaxies might help clarify this point.}
-\textcolor{magenta}{
-Even if we are populating our training data with fainter objects, augmentation still improves the overall performance on the validation set, so I don't think augmentation hurts us.
-}
 

### 2016-06-25 paper/main.tex
add final draft
added ProfessorBrunner's affiliations

@@
 \author[E. J. Kim and R. J. Brunner]{
-  Edward J.~Kim$^1$\thanks{jkim575@illinois.edu} and Robert J.~Brunner$^{2}$ \\
+  Edward J.~Kim$^1$\thanks{jkim575@illinois.edu} and Robert J.~Brunner$^{1,2,3,4}$ \\
 $^1$Department of Physics, University of Illinois, Urbana, IL 61801 USA\\
-$^2$Department of Astronomy, University of Illinois, Urbana, IL 61801 USA}
+$^2$Department of Astronomy, University of Illinois, Urbana, IL 61801 USA\\
+$^3$Department of Statistics, University of Illinois, Champaign, IL 61820 USA\\
+$^4$National Center for Supercomputing Applications, Urbana, IL 61801 USA
+}
 
@@
 and morphology is not a reliable metric for star-galaxy classification.
+Another possibility is that data augmentation has a negative effect at faint
+magnitudes, as the network may get confused by additional examples of faint
+galaxies that look like point sources.
+Data augmentation however is indispensable, since it improves the overall
+performance greatly.
 

### 2016-08-08 paper/main.tex
[issue 2.3] remove color-color plots

@@
 
+% Use colors for revisions
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\newcommand{\added}[1]{\textcolor{blue}{#1}}
+\newcommand{\changed}[1]{\textcolor{red}{#1}}
+\newcommand{\removed}[1]{\textcolor{gray}{#1}}
+
 \pdfminorversion=5
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{figures/sdss_color_color.pdf}
-  \caption{
-    Hexbin plots showing the color-color space distribution of galaxies (blue, top row) and stars (green, bottom row)
-    in the SDSS data set used in this analysis.
-    It is easy to see that there is significant overlap between stars
-    and galaxies in these color-color spaces. 
-  }
-  \label{fig:sdss_color_color}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=\columnwidth]{figures/sdss_color_color.pdf}
+%  \caption{
+%    Hexbin plots showing the color-color space distribution of galaxies (blue, top row) and stars (green, bottom row)
+%    in the SDSS data set used in this analysis.
+%    It is easy to see that there is significant overlap between stars
+%    and galaxies in these color-color spaces. 
+%  }
+%  \label{fig:sdss_color_color}
+%\end{figure}
 
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
+\removed{
 The $ugriz$ color-color space of the sample is plotted in
 Figure~\ref{fig:sdss_color_color}.
+}
 We randomly split the objects into training, held-out validation,
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{figures/clens_color_color.pdf}
-  \caption{
-    Hexbin plots showing the color-color space distribution of
-    galaxies (blue, top row) and stars (green, bottom row)
-    in the CFHTLenS data set used in this analysis.
-  }
-  \label{fig:clens_color_color}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=\columnwidth]{figures/clens_color_color.pdf}
+%  \caption{
+%    Hexbin plots showing the color-color space distribution of
+%    galaxies (blue, top row) and stars (green, bottom row)
+%    in the CFHTLenS data set used in this analysis.
+%  }
+%  \label{fig:clens_color_color}
+%\end{figure}
 
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
+\removed{
 The $ugriz$ color-color space of the sample is plotted in
 Figure~\ref{fig:clens_color_color}.
+}
 We randomly split the objects into training, held-out validation, and

### 2016-08-08 paper/main.tex
[issue 2.2, 2.3] add introducing sentence before 2.1; remove figures 1 and 2

@@
 
-% Use colors for revisions
+% Use strikethrough and colors for revisions
+\usepackage[normalem]{ulem}
 \definecolor{gray}{rgb}{0.5,0.5,0.5}
-\newcommand{\added}[1]{\textcolor{blue}{#1}}
-\newcommand{\changed}[1]{\textcolor{red}{#1}}
-\newcommand{\removed}[1]{\textcolor{gray}{#1}}
+\newcommand{\added}[1]{\textcolor{red}{#1}}
 
@@
 
+\added{
+To demonstrate the performance of our ConvNet model, we use photometric and
+spectroscopic data sets with different characteristics and compositions.
+In this section, we briefly describe these data sets and the image pre-processing
+steps for retrieving cutout images.
+}
+
 \subsection{Sloan Digital Sky Survey}
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
-\removed{
+\sout{
 The $ugriz$ color-color space of the sample is plotted in
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
-\removed{
+\sout{
 The $ugriz$ color-color space of the sample is plotted in

### 2016-08-08 paper/main.tex
[issue 2.4] remove r < 40 cut

@@
 We exclude some bad photometric observations as follows.
-We consider only objects whose $r$-band magnitude is less than 40;
-there are no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
+We consider only objects
+\sout{
+whose $r$-band magnitude is less than 40; there are
+}
+with no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
 the half-light radius in the $r$ band is less than 30 arc seconds

### 2016-08-08 paper/main.tex
[issue 2.9] change to vectors in eq 4
[issue 2.12] the dominant approch to a power approach

@@
 \begin{equation}
-  L(y_j, \hat{y}_j) = - \frac{1}{N} \sum_{j=1}^{N} \hat{y}_j  \log_2 y_j
+\added{
+  L(\bmath{y}, \hat{\bmath{y}})
+}
+= - \frac{1}{N} \sum_{j=1}^{N} \hat{y}_j  \log_2 y_j
     + (1 - \hat{y}_j)  \log_2 (1 - \hat y_j).
@@
 is a type of deep, feedforward neural network
-that has recently become the dominant approach in the computer vision community.
+that has recently become \added{a popular} approach in the computer vision community.
 In a typical ConvNet, the first few stages are composed of two types of layers: 

### 2016-08-08 paper/main.tex
[issue 2.13] restructure sentence

@@
 
-The input to a convolutional layer is an image with a certain number of color channels
-or \textit{feature maps}.
+\added{
+The input to a convolutional layer is an image, and the output channels of
+each layer are called \textit{feature maps}.
+}
 To produce output feature maps, we convolve each feature map with a set of weights

### 2016-08-08 paper/main.tex
[issue 2.14] change order

@@
 is a type of deep, feedforward neural network
-that has recently become \added{a popular} approach in the computer vision community.
+that has recently become
+\added{
+a popular
+}
+approach in the computer vision community.
 In a typical ConvNet, the first few stages are composed of two types of layers: 
@@
 
-A typical pooling layer computes the maximum of a local $2\times2$ patch in a feature map.
+\added{
+Typically, a
+}
+pooling layer computes the maximum of a local $2\times2$ patch in a feature map.
 Since the pooling layer aggregates the activations of neighboring units from the previous layer,

### 2016-08-08 paper/main.tex
[issue 0.3, 1.2, 2.17] shorten tpc section

@@
 \definecolor{gray}{rgb}{0.5,0.5,0.5}
-\newcommand{\added}[1]{\textcolor{red}{#1}}
+\newcommand{\changed}[1]{\textcolor{red}{#1}}
 
@@
 
-\added{
+\changed{
 To demonstrate the performance of our ConvNet model, we use photometric and
@@
 \begin{equation}
-\added{
+\changed{
   L(\bmath{y}, \hat{\bmath{y}})
@@
 that has recently become
-\added{
+\changed{
 a popular
@@
 
-\added{
+\changed{
 The input to a convolutional layer is an image, and the output channels of
@@
 
-\added{
+\changed{
 Typically, a
@@
 Trees for Probabilistic Classifications (TPC).
-Although a complete description of TPC is beyond the scope of this paper,
-we provide a brief description in this section.
-For more details, we refer the reader to
-\cite{carrascokind2013tpz} and \cite{kim2015hybrid}.
-
 TPC is a parallel, supervised machine learning algorithm
@@
 to produce a star-galaxy classification.
-TPC is a part of a publicly available software package called
-\textsc{MLZ}\footnote{http://pythonhosted.org/MLZ/}
-(Machine Learning for Photo-$z$).
-
-TPC uses classification trees,
-a type of prediction tree that is designed to
-provide a classification or predict a discrete category.
-Prediction trees are built by asking a sequence of questions
-that recursively split the data into branches
-until a terminal leaf is created
-that meets a stopping criterion
-(\eg a minimum leaf size).
-The optimal split dimension is decided by
-choosing the attribute that maximizes
-the \textit{Information Gain} ($I_G$), which is defined as
-
-\begin{equation} \label{eq:information_gain}
-  I_G \left(D_{\rmn{node}}, X\right)
-  = I_d \left( D_{\rmn{node}} \right)
-  - \sum_{x \in \rmn{values}(X)}
-  \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|}
-  I_d \left( D_{\rmn{node}, x} \right),
-\end{equation}
-
-\noindent
-where $D_{\rmn{node}}$ is the training data in a given node,
-$X$ is one of the possible dimensions (\eg magnitudes or colors)
-along which the node is split, and
-$x$ are the possible values of a specific dimension $X$.
-$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data
-and the number of objects in a given subset $x$ within the current node,
-respectively.
-$I_d$ is the impurity degree index,
-and TPC can calculate $I_d$
-from any of the three standard different impurity indices:
-\textit{information entropy}, \textit{Gini impurity},
-and \textit{classification error}.
-In this work, we use the information entropy,
-which is defined similarly to the thermodynamic entropy:
-
-\begin{equation}
-  I_d \left( D \right)
-  = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right),
-\end{equation}
-
-\noindent
-where $f_g$ is the fraction of galaxies in the training data.
-At each node in our tree,
-we scan all dimensions to identify the split point that
-maximizes the information gain as defined by Equation~\ref{eq:information_gain},
-and select the attribute that maximizes the overall impurity index.
-
-In a technique called random forest,
-we create bootstrap samples
-(\ie $N$ randomly selected objects with replacement)
-from the input training data
-by sampling repeatedly from the magnitudes and colors
-using their measurement errors.
-We use these bootstrap samples to construct
-multiple, uncorrelated prediction trees
-whose individual predictions are aggregated to produce
-a star-galaxy classification for each source.
+\changed{
+A complete description of TPC is beyond the scope of this paper, and
+we refer the reader to
+\cite{carrascokind2013tpz} and \cite{kim2015hybrid} for more details.
+}
+
+%TPC is a part of a publicly available software package called
+%\textsc{MLZ}\footnote{http://pythonhosted.org/MLZ/}
+%(Machine Learning for Photo-$z$).
+%
+%TPC uses classification trees,
+%a type of prediction tree that is designed to
+%provide a classification or predict a discrete category.
+%Prediction trees are built by asking a sequence of questions
+%that recursively split the data into branches
+%until a terminal leaf is created
+%that meets a stopping criterion
+%(\eg a minimum leaf size).
+%The optimal split dimension is decided by
+%choosing the attribute that maximizes
+%the \textit{Information Gain} ($I_G$), which is defined as
+%
+%\begin{equation} \label{eq:information_gain}
+%  I_G \left(D_{\rmn{node}}, X\right)
+%  = I_d \left( D_{\rmn{node}} \right)
+%  - \sum_{x \in \rmn{values}(X)}
+%  \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|}
+%  I_d \left( D_{\rmn{node}, x} \right),
+%\end{equation}
+%
+%\noindent
+%where $D_{\rmn{node}}$ is the training data in a given node,
+%$X$ is one of the possible dimensions (\eg magnitudes or colors)
+%along which the node is split, and
+%$x$ are the possible values of a specific dimension $X$.
+%$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data
+%and the number of objects in a given subset $x$ within the current node,
+%respectively.
+%$I_d$ is the impurity degree index,
+%and TPC can calculate $I_d$
+%from any of the three standard different impurity indices:
+%\textit{information entropy}, \textit{Gini impurity},
+%and \textit{classification error}.
+%In this work, we use the information entropy,
+%which is defined similarly to the thermodynamic entropy:
+%
+%\begin{equation}
+%  I_d \left( D \right)
+%  = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right),
+%\end{equation}
+%
+%\noindent
+%where $f_g$ is the fraction of galaxies in the training data.
+%At each node in our tree,
+%we scan all dimensions to identify the split point that
+%maximizes the information gain as defined by Equation~\ref{eq:information_gain},
+%and select the attribute that maximizes the overall impurity index.
+%
+%In a technique called random forest,
+%we create bootstrap samples
+%(\ie $N$ randomly selected objects with replacement)
+%from the input training data
+%by sampling repeatedly from the magnitudes and colors
+%using their measurement errors.
+%We use these bootstrap samples to construct
+%multiple, uncorrelated prediction trees
+%whose individual predictions are aggregated to produce
+%a star-galaxy classification for each source.
 

### 2016-08-08 paper/main.tex
[issue 2.21] remove tpc core hours

@@
 
+\sout{
 We note that TPC is able to utilize parallelization, and parallelized on 64
@@
 for a total of 25 CPU hours.
+}
 

### 2016-08-08 paper/main.tex
[issue 2.25] combine sdss calibration curves

@@
 
-\begin{figure*}
-  \centering
-  \begin{minipage}[c]{0.49\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{figures/sdss_calibration_conv.pdf}
-    \caption{Calibration curve for ConvNet as applied to the SDSS data set.}
-    \label{fig:sdss_calibration_conv}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[c]{0.49\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{figures/sdss_calibration_tpc.pdf}
-    \caption{Calibration curve for $\rmn{TPC}_{\rmn{morph}}$
-      as applied to the SDSS data set.}
-    \label{fig:sdss_calibration_tpc}
-  \end{minipage}
-\end{figure*}
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/sdss_calibration.pdf}
+  \caption{
+    \changed{
+    Calibration curves for ConvNet (red) and $\rmn{TPC}_{\rmn{morph}}$
+    (blue) as applied to the SDSS data set.
+    }
+    }
+  \label{fig:sdss_calibration}
+\end{figure}
 
@@
 
-Figures~\ref{fig:sdss_calibration_conv} and \ref{fig:sdss_calibration_tpc}
-show the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$,
-respectively.
-The calibration curve of ConvNet in Figure~\ref{fig:sdss_calibration_conv}
+\changed{
+Figure~\ref{fig:sdss_calibration} shows
+the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$.
+}
+The calibration curve of ConvNet in Figure~\ref{fig:sdss_calibration}
 is not as well-calibrated as the calibration curve in

### 2016-08-08 paper/main.tex
[issue 2.25] combine clens calibration curves

@@
 fraction of positive examples versus the predicted probability in each bin
-(see Figures~\ref{fig:clens_calibration_conv} and \ref{fig:clens_calibration_tpc}).
+(see Figures~\ref{fig:clens_calibration} and \ref{fig:sdss_calibration}).
 
@@
 
-\begin{figure*}
-  \centering
-  \begin{minipage}[c]{0.49\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{figures/clens_calibration_conv.pdf}
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{figures/clens_calibration.pdf}
   \caption{
-      The calibration curve for ConvNet as applied to the CFHTLenS data set.
+    \changed{
+    The calibration curves for ConvNet (red) and $\rmn{TPC}_{\rmn{morph}}$ (blue)
+    as applied to the CFHTLenS data set.
     $P_{\rmn{gal}}$ is the fraction of objects that are galaxies, and
-      $P_{\rmn{conv}}$ is the probabilistic output generated by ConvNet.
+    $P_{\rmn{class}}$ is the probabilistic outputs generated by the classifiers.
+    }
     The dashed line displays the relationship
@@
     }
-    \label{fig:clens_calibration_conv}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[c]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{figures/clens_calibration_tpc.pdf}
-    \caption{Similar to Figure~\ref{fig:clens_calibration_conv} but for
-      $\rmn{TPC}_{\rmn{morph}}$.
-      $P_{\rmn{tpc}}$ is the probabilistic output generated by $\rmn{TPC}_{\rmn{morph}}$.}
-    \label{fig:clens_calibration_tpc}
-  \end{minipage}
-\end{figure*}
+  \label{fig:clens_calibration}
+\end{figure}
 
@@
 
-Figure~\ref{fig:clens_calibration_conv} shows the calibration curve
-that compares $P_{\rmn{gal}}$,
+\changed{
+Figure~\ref{fig:clens_calibration} shows the calibration curves that compare
+$P_{\rmn{gal}}$,
 the fraction of objects that are galaxies (as determined from their spectra),
-to $P_{\rmn{conv}}$, the probabilistic output that our ConvNet model produces.
-The calibration curve is nearly diagonal, which implies that ConvNet
-is well-calibrated and we can treat $P_{\rmn{conv}}$ as the probability
-that an object is a galaxy.
-Figure~\ref{fig:clens_calibration_tpc} shows the calibration curve
-for the probabilistic output of $\rmn{TPC}_{\rmn{morph}}$,
-which is apparently not as well-calibrated as ConvNet.
+to $P_{\rmn{class}}$, the probabilistic outputs
+produced by ConvNet and $\rmn{TPC}_{\rmn{morph}}$.
+The calibration curve for our ConvNet model is nearly diagonal,
+which implies that ConvNet is well-calibrated and we can treat its probabilistic
+output as the probability that an object is a galaxy.
+In contrast, the calibration curve
+for the probabilistic output of $\rmn{TPC}_{\rmn{morph}}$
+is apparently not as well-calibrated as ConvNet.
+}
 These calibration curves visually confirm the results in

### 2016-08-09 paper/main.tex
[issue 2.19] cmodelmag

@@
 colors, for a total of fifteen dimensions.
-The concentration is defined as the difference between the cmodel
-and PSF magnitude: $\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
+The concentration is defined as the difference between the
+\sout{cmodel and}
+\changed{
+PSF magnitude (psfMag) and the composite model magnitude (cModelMag), \ie
+}
+$\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
 The SDSS pipeline uses a parametric method based on the concentration,

### 2016-08-09 paper/main.tex
[issue 2.18] fifteen to fourteen

@@
 We introduce random Gaussian noise to each pixel values
-by using a similar method to \cite{krizhevsky2012imagenet}. }
+by using a similar method to \cite{krizhevsky2012imagenet}.}
 \end{itemize}
@@
 the concentration parameter in each band in addition to the magnitudes and
-colors, for a total of fifteen dimensions.
+colors, for a total of
+\changed{
+fourteen
+}
+dimensions.
 The concentration is defined as the difference between the

### 2016-08-09 paper/main.tex
[issue 2.28] acknowledgements

@@
 
+\changed{
+The authors thank the referee for a careful reading of the manuscript
+and comments that improved this work.
+}
 We acknowledge support from the 
@@
 ACI-1053575.
+
+\changed{
+This work has made use of the Theano library (http://deeplearning.net/software/theano/),
+the Lasagne library (http://lasagne.readthedocs.io/),
+and the Nolearn library (http://pythonhosted.org/nolearn/).
+}
 

### 2016-08-09 paper/main.tex
[issue 2.24] train and validate

@@
 We also use the same training and validation sets to train
+\changed{
+and validate
+}
 $\rmn{TPC}_{\rmn{morph}}$ and $\rmn{TPC}_{\rmn{phot}}$, and

### 2016-08-10 paper/main.tex
[issue 2.24] tune the hyperparameters

@@
 \changed{
-and validate
+and tune the hyperparameters of 
 }

### 2016-08-10 paper/main.tex
[issue 2.16] mention invariance

@@
 \end{itemize}
-These data augmentation schemes add almost no computational cost,
+\changed{
+In addition to artificially increasing the size of the dataset,
+these data augmentation schemes make the resulting model more invariant to
+rotation, reflection, translation, and small noise in the pixel values.
+We also note that the data augmentation steps
+}
+add almost no computational cost,
 as they are performed on the CPU while the GPU is training the ConvNets on images.

### 2016-08-10 paper/main.tex
[issue 2.10] mini-batch

@@
 where $\eta$ is a small, positive number known as the \textit{learning rate}.
+\changed{
 A common approach to speed up training is to split the training data
-into mini-batches and compute the gradients in
-Equation~\ref{eq:gradient_descent} for each mini-batch separately instead of
-the entire training data.
-This results in much faster convergence, as training examples are usually correlated
-and the gradient computed from a randomly chosen mini-batch is a good approximation
+into mini-batches.
+In mini-batch gradient descent, instead of computing the gradients in
+Equation~\ref{eq:gradient_descent} for the entire training data,
+we only compute the gradient of randomly chosen training examples at each step.
+As training examples are usually correlated,
+the gradient computed from each mini-batch is a good approximation
 of the overall gradient.
+As a result, mini-batch gradient descent results in much faster convergence.
+However, there is a trade-off: the lower the batch size is,
+the lower the convergence rate will be;
+the higher the batch size is,
+the longer it will take to compute the gradient at each step.
+Thus, a moderate batch size, combined with a decaying learning rate, is
+generally used in practice.
+}
+
 We define an \textit{epoch} as a single, complete pass through the training data,

### 2016-08-10 paper/main.tex
[issue 2.1] talk about not explicitly designed features

@@
 such as magnitudes or shape information of an object.
-In a branch of machine learning called \textit{deep learning},
+\changed{
+In a branch of machine learning called \textit{deep learning}~\citep{lecun2015deep},
 features are not designed by human experts;
 they are learned directly from data by deep neural networks.
+Deep learning methods learn multiple levels of features by
+transforming the feature at one level into a more abstract feature at a higher
+level.
+For example, when an array of pixel values is used as input to a deep learning
+method, the features in the first layer might represent locations and orientations
+of edges.
+The second layer could assemble particular arrangements of edges into more
+complex shapes, and subsequent layers would detect objects as
+combinations of low-level features.
+These multiple layers of abstraction progressively amplify aspects of the input
+that are important for classification tasks.
+}
 Deep learning has been applied successfully to galaxy morphological

### 2016-08-10 paper/main.tex
[issue 2.5] luptitudes

@@
 and to center each object in the cutout image.
-We also convert the flux values to inverse hyperbolic sine magnitudes
-\citep[also known as luptitudes;][]{lupton1999modified}.
+{
+Magnitudes in the SDSS photometric catalog are expressed as inverse hyperbolic
+sine magnitudes~\citep[also known as luptitudes;][]{lupton1999modified},
+and we follow the SDSS convention and convert all flux values to luptitudes.
+}
 Finally, in order to account for the effect of Galactic dust,

### 2016-08-10 paper/main.tex
[issue 0.3, 1.2, 2.7] shorten sections

@@
 
+\sout{
 A neuron in the human brain receives signals from other neurons through
@@
 approximately $10^{11}$ neurons firing.
+}
 An artificial neuron in most artificial neural networks is represented
 as a mathematical function that models a biological neural structure
-(Figure~\ref{fig:neuron_a}).
+\changed{
+\citep{aggarwal2014data}.
+A schematic representation is shown in Figure~\ref{fig:neuron_a}.
+}
 Let $\bmath{x}=\left(x_1,x_2,\dots,x_n\right)$ be a vector of inputs to a given neuron,
@@
 where $\sigma$ is the activation function (or \textit{non-linearity}).
-
+\sout{
 The sigmoid function, $\sigma(x)=1/\left(1+e^{-x}\right)$,
@@
 and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$, is generally used instead.
-The most popular non-linearity at present, however, is the rectified linear unit
+}
+The most popular non-linearity at present
+\sout{, however,
+}
+is the rectified linear unit
 \citep[ReLU;][]{nair2010rectified}, $\sigma(x)=\max(0, x)$.
@@
 \changed{
+The gradients can be computed using the backpropagation
+procedure~\citep{rumelhart1988learning}.
 A common approach to speed up training is to split the training data
@@
 
-The gradients in \ref{eq:gradient_descent} can be computed using the
-\textit{backpropagation} procedure~\citep{rumelhart1988learning},
-which is nothing more than an application of the chain rule for derivatives.
-The derivative of the loss function with respect to the input of a unit can be
-computed by working backwards from the gradient with respect to the output of
-the unit.
-At the output layer, the derivative of the loss function with respect to the
-output is given by
-\begin{align}
-  \frac{ \partial L }{ \partial y_i } &= y_i - \hat{y}_i \\
-  \frac{ \partial L }{ \partial x_i } &=
-    \frac{ \partial L }{ \partial y_i }
-    \frac{ \partial y_i }{ \partial x_i }.
-\end{align}
-At each hidden layer, the derivative of the loss function with respect to the
-output of each unit is a weighted sum of the derivatives with respect to the
-inputs of the subsequent layer,
-\begin{align}
-  \frac{ \partial L }{ \partial y_j } &=
-    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}   \\
-  \frac{ \partial L }{ \partial x_j } &=
-    \frac{ \partial L }{ \partial y_j }
-    \frac{ \partial y_j }{ \partial x_j }.
-\end{align}
-Finally, once the gradients $\partial L / \partial x_j$ have been
-computed, it is straightforward to compute the gradients for the weight,
-\begin{equation}
-\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
-\end{equation}
+%The gradients in \ref{eq:gradient_descent} can be computed using the
+%\textit{backpropagation} procedure~\citep{rumelhart1988learning},
+%which is nothing more than an application of the chain rule for derivatives.
+%The derivative of the loss function with respect to the input of a unit can be
+%computed by working backwards from the gradient with respect to the output of
+%the unit.
+%At the output layer, the derivative of the loss function with respect to the
+%output is given by
+%\begin{align}
+%  \frac{ \partial L }{ \partial y_i } &= y_i - \hat{y}_i \\
+%  \frac{ \partial L }{ \partial x_i } &=
+%    \frac{ \partial L }{ \partial y_i }
+%    \frac{ \partial y_i }{ \partial x_i }.
+%\end{align}
+%At each hidden layer, the derivative of the loss function with respect to the
+%output of each unit is a weighted sum of the derivatives with respect to the
+%inputs of the subsequent layer,
+%\begin{align}
+%  \frac{ \partial L }{ \partial y_j } &=
+%    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}   \\
+%  \frac{ \partial L }{ \partial x_j } &=
+%    \frac{ \partial L }{ \partial y_j }
+%    \frac{ \partial y_j }{ \partial x_j }.
+%\end{align}
+%Finally, once the gradients $\partial L / \partial x_j$ have been
+%computed, it is straightforward to compute the gradients for the weight,
+%\begin{equation}
+%\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
+%\end{equation}
 
@@
 
-%TPC is a part of a publicly available software package called
-%\textsc{MLZ}\footnote{http://pythonhosted.org/MLZ/}
-%(Machine Learning for Photo-$z$).
-%
-%TPC uses classification trees,
-%a type of prediction tree that is designed to
-%provide a classification or predict a discrete category.
-%Prediction trees are built by asking a sequence of questions
-%that recursively split the data into branches
-%until a terminal leaf is created
-%that meets a stopping criterion
-%(\eg a minimum leaf size).
-%The optimal split dimension is decided by
-%choosing the attribute that maximizes
-%the \textit{Information Gain} ($I_G$), which is defined as
-%
-%\begin{equation} \label{eq:information_gain}
-%  I_G \left(D_{\rmn{node}}, X\right)
-%  = I_d \left( D_{\rmn{node}} \right)
-%  - \sum_{x \in \rmn{values}(X)}
-%  \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|}
-%  I_d \left( D_{\rmn{node}, x} \right),
-%\end{equation}
-%
-%\noindent
-%where $D_{\rmn{node}}$ is the training data in a given node,
-%$X$ is one of the possible dimensions (\eg magnitudes or colors)
-%along which the node is split, and
-%$x$ are the possible values of a specific dimension $X$.
-%$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data
-%and the number of objects in a given subset $x$ within the current node,
-%respectively.
-%$I_d$ is the impurity degree index,
-%and TPC can calculate $I_d$
-%from any of the three standard different impurity indices:
-%\textit{information entropy}, \textit{Gini impurity},
-%and \textit{classification error}.
-%In this work, we use the information entropy,
-%which is defined similarly to the thermodynamic entropy:
-%
-%\begin{equation}
-%  I_d \left( D \right)
-%  = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right),
-%\end{equation}
-%
-%\noindent
-%where $f_g$ is the fraction of galaxies in the training data.
-%At each node in our tree,
-%we scan all dimensions to identify the split point that
-%maximizes the information gain as defined by Equation~\ref{eq:information_gain},
-%and select the attribute that maximizes the overall impurity index.
-%
-%In a technique called random forest,
-%we create bootstrap samples
-%(\ie $N$ randomly selected objects with replacement)
-%from the input training data
-%by sampling repeatedly from the magnitudes and colors
-%using their measurement errors.
-%We use these bootstrap samples to construct
-%multiple, uncorrelated prediction trees
-%whose individual predictions are aggregated to produce
-%a star-galaxy classification for each source.
+\sout{
+TPC is a part of a publicly available software package called
+\textsc{MLZ}%\footnote{http://pythonhosted.org/MLZ/}
+(Machine Learning for Photo-$z$).
+}
+
+\sout{
+TPC uses classification trees,
+a type of prediction tree that is designed to
+provide a classification or predict a discrete category.
+Prediction trees are built by asking a sequence of questions
+that recursively split the data into branches
+until a terminal leaf is created
+that meets a stopping criterion
+(\eg a minimum leaf size).
+The optimal split dimension is decided by
+choosing the attribute that maximizes
+the \textit{Information Gain} ($I_G$), which is defined as
+}
+
+\sout{ $
+  I_G \left(D_{\rmn{node}}, X\right)
+  = I_d \left( D_{\rmn{node}} \right)
+  - \sum_{x \in \rmn{values}(X)}
+  \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|}
+  I_d \left( D_{\rmn{node}, x} \right),
+$ }
+
+\sout{
+\noindent
+where $D_{\rmn{node}}$ is the training data in a given node,
+$X$ is one of the possible dimensions (\eg magnitudes or colors)
+along which the node is split, and
+$x$ are the possible values of a specific dimension $X$.
+$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data
+and the number of objects in a given subset $x$ within the current node,
+respectively.
+$I_d$ is the impurity degree index,
+and TPC can calculate $I_d$
+from any of the three standard different impurity indices:
+\textit{information entropy}, \textit{Gini impurity},
+and \textit{classification error}.
+In this work, we use the information entropy,
+which is defined similarly to the thermodynamic entropy:
+}
+
+\sout{ $
+  I_d \left( D \right)
+  = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right),
+$ }
+
+\sout{
+\noindent
+where $f_g$ is the fraction of galaxies in the training data.
+At each node in our tree,
+we scan all dimensions to identify the split point that
+maximizes the information gain as defined by Equation~\ref{eq:information_gain},
+and select the attribute that maximizes the overall impurity index.
+}
+
+\sout{
+In a technique called random forest,
+we create bootstrap samples
+(\ie $N$ randomly selected objects with replacement)
+from the input training data
+by sampling repeatedly from the magnitudes and colors
+using their measurement errors.
+We use these bootstrap samples to construct
+multiple, uncorrelated prediction trees
+whose individual predictions are aggregated to produce
+a star-galaxy classification for each source.
+}
 
@@
 is not as well-calibrated as the calibration curve in
-Figure~\ref{fig:clens_calibration_conv},
+Figure~\ref{fig:clens_calibration},
 where the same ConvNet model was applied to the CFHTLenS data set.
@@
 \changed{
-The authors thank the referee for a careful reading of the manuscript
+The authors thank the referees for a careful reading of the manuscript
 and comments that improved this work.

### 2016-08-10 paper/main.tex
[issue 0.3, 1.2, 2.7] shorten sections more

@@
 The $ugriz$ color-color space of the sample is plotted in
-Figure~\ref{fig:sdss_color_color}.
+Figure ?%~\ref{fig:sdss_color_color}.
 }
@@
 The $ugriz$ color-color space of the sample is plotted in
-Figure~\ref{fig:clens_color_color}.
+Figure ?%~\ref{fig:clens_color_color}.
 }
@@
 All layers except the input and output layers are conveniently called hidden layers.
+\sout{
 With multiple hidden layers, deep neural networks can model complex nonlinear
@@
 outperformed computers, such as speech recognition, language processing, and image classification.
+}
 
@@
 
-%The gradients in \ref{eq:gradient_descent} can be computed using the
-%\textit{backpropagation} procedure~\citep{rumelhart1988learning},
-%which is nothing more than an application of the chain rule for derivatives.
-%The derivative of the loss function with respect to the input of a unit can be
-%computed by working backwards from the gradient with respect to the output of
-%the unit.
-%At the output layer, the derivative of the loss function with respect to the
-%output is given by
-%\begin{align}
-%  \frac{ \partial L }{ \partial y_i } &= y_i - \hat{y}_i \\
-%  \frac{ \partial L }{ \partial x_i } &=
-%    \frac{ \partial L }{ \partial y_i }
-%    \frac{ \partial y_i }{ \partial x_i }.
-%\end{align}
-%At each hidden layer, the derivative of the loss function with respect to the
-%output of each unit is a weighted sum of the derivatives with respect to the
-%inputs of the subsequent layer,
-%\begin{align}
-%  \frac{ \partial L }{ \partial y_j } &=
-%    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}   \\
-%  \frac{ \partial L }{ \partial x_j } &=
-%    \frac{ \partial L }{ \partial y_j }
-%    \frac{ \partial y_j }{ \partial x_j }.
-%\end{align}
-%Finally, once the gradients $\partial L / \partial x_j$ have been
-%computed, it is straightforward to compute the gradients for the weight,
-%\begin{equation}
-%\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
-%\end{equation}
+\sout{
+The gradients in Equation~\ref{eq:gradient_descent}
+can be computed using the \textit{backpropagation} procedure%~\citep{rumelhart1988learning},
+which is nothing more than an application of the chain rule for derivatives.
+The derivative of the loss function with respect to the input of a unit can be
+computed by working backwards from the gradient with respect to the output of
+the unit.
+At the output layer, the derivative of the loss function with respect to the
+output is given by
+}
+
+\sout{$
+  \frac{ \partial L }{ \partial y_i } = y_i - \hat{y}_i
+$}
+\sout{$
+  \frac{ \partial L }{ \partial x_i } =
+    \frac{ \partial L }{ \partial y_i }
+    \frac{ \partial y_i }{ \partial x_i }.
+$}
+
+\sout{
+At each hidden layer, the derivative of the loss function with respect to the
+output of each unit is a weighted sum of the derivatives with respect to the
+inputs of the subsequent layer,
+}
+\sout{$
+  \frac{ \partial L }{ \partial y_j } =
+    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}
+$}
+\sout{$
+  \frac{ \partial L }{ \partial x_j } =
+    \frac{ \partial L }{ \partial y_j }
+    \frac{ \partial y_j }{ \partial x_j }.
+$}
+
+\sout{
+Finally, once the gradients $\partial L / \partial x_j$ have been
+computed, it is straightforward to compute the gradients for the weight,
+}
+\sout{$
+\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
+$}
 

### 2016-08-10 paper/main.tex
[issue 0.3, 1.2, 2.7] some citations

@@
 However, ReLU units can sometimes result in dead neurons whose output is always zero.
-To mitigate this problem, we use leaky ReLUs that have a small, non-zero slope
-in the negative region,
+To mitigate this problem, we use leaky ReLUs
+\changed{
+~\citep{maas2013rectifier}
+}
+that have a small, non-zero slope in the negative region,
 \begin{equation}
@@
 A common approach to speed up training is to split the training data
-into mini-batches.
+into mini-batches~\citep{lecun1998efficient}.
 In mini-batch gradient descent, instead of computing the gradients in
@@
 the gradient computed from each mini-batch is a good approximation
-of the overall gradient.
+of the overall gradient~\citep{bottou1998online}.
 As a result, mini-batch gradient descent results in much faster convergence.
@@
 the lower the convergence rate will be;
-the higher the batch size is,
-the longer it will take to compute the gradient at each step.
+the higher the batch size is, the longer it will take to compute the gradient
+at each step~\citep{bousquet2008tradeoffs}.
 Thus, a moderate batch size, combined with a decaying learning rate, is

### 2016-08-10 paper/main.tex
[issue 0.3, 1.2, 2.7] souts in one line

@@
 We consider only objects
-\sout{
-whose $r$-band magnitude is less than 40; there are
-}
+\sout{ whose $r$-band magnitude is less than 40; there are }
 with no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
-\sout{
-The $ugriz$ color-color space of the sample is plotted in
-Figure ?%~\ref{fig:sdss_color_color}.
-}
+\sout{ The $ugriz$ color-color space of the sample is plotted in Figure ?.}
 We randomly split the objects into training, held-out validation,
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
-\sout{
-The $ugriz$ color-color space of the sample is plotted in
-Figure ?%~\ref{fig:clens_color_color}.
-}
+\sout{ The $ugriz$ color-color space of the sample is plotted in Figure ?.}
 We randomly split the objects into training, held-out validation, and
@@
 
-\sout{
-A neuron in the human brain receives signals from other neurons through
-synaptic connections.
-If the combination of these signals exceeds a certain threshold,
-the neuron will fire and send a signal to other neurons.
-Intelligence is believed to be the collective effect of
-approximately $10^{11}$ neurons firing.
+\sout{ A neuron in the human brain receives signals from other neurons through synaptic connections.
+If the combination of these signals exceeds a certain threshold, the neuron will fire and send a signal to other neurons.
+Intelligence is believed to be the collective effect of approximately $10^{11}$ neurons firing.
 }
@@
 where $\sigma$ is the activation function (or \textit{non-linearity}).
-\sout{
-The sigmoid function, $\sigma(x)=1/\left(1+e^{-x}\right)$,
-has frequently been used as an activation function, but it has recently fallen out of favor,
-and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$, is generally used instead.
+\sout{ The sigmoid function, $\sigma(x)=1/\left(1+e^{-x}\right)$, has frequently been used as an activation function, but it has recently fallen out of favor, and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$, is generally used instead.
 }
 The most popular non-linearity at present
-\sout{, however,
-}
+\sout{, however, }
 is the rectified linear unit
@@
 All layers except the input and output layers are conveniently called hidden layers.
-\sout{
-With multiple hidden layers, deep neural networks can model complex nonlinear
-relationships, and they have had great success in multimedia tasks where humans traditionally
-outperformed computers, such as speech recognition, language processing, and image classification.
+\sout{ With multiple hidden layers, deep neural networks can model complex nonlinear relationships, and they have had great success in multimedia tasks where humans traditionally outperformed computers, such as speech recognition, language processing, and image classification.
 }
@@
 given $N$ samples, the output from the network
-$\bmath{y}=\left(y_1, y_2, \dots, y_N \right)$
-approximates the desired output
+$\bmath{y}=\left(y_1, y_2, \dots, y_N \right)$ approximates the desired output
 $\hat{\bmath{y}}=\left(\hat{y}_1, \hat{y}_2, \dots, \hat{y}_N \right)$
@@
 We compute the loss function by taking the average of all cross-entropies in the sample.
-Thus, the loss function becomes
+Thus,
+\changed{
+given $N$ samples,
+}
+the loss function becomes
 \begin{equation}
@@
 
-\sout{
-The gradients in Equation~\ref{eq:gradient_descent}
-can be computed using the \textit{backpropagation} procedure%~\citep{rumelhart1988learning},
-which is nothing more than an application of the chain rule for derivatives.
-The derivative of the loss function with respect to the input of a unit can be
-computed by working backwards from the gradient with respect to the output of
-the unit.
-At the output layer, the derivative of the loss function with respect to the
-output is given by
-}
-
-\sout{$
-  \frac{ \partial L }{ \partial y_i } = y_i - \hat{y}_i
-$}
-\sout{$
-  \frac{ \partial L }{ \partial x_i } =
-    \frac{ \partial L }{ \partial y_i }
-    \frac{ \partial y_i }{ \partial x_i }.
-$}
-
-\sout{
-At each hidden layer, the derivative of the loss function with respect to the
-output of each unit is a weighted sum of the derivatives with respect to the
-inputs of the subsequent layer,
-}
-\sout{$
-  \frac{ \partial L }{ \partial y_j } =
-    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}
-$}
-\sout{$
-  \frac{ \partial L }{ \partial x_j } =
-    \frac{ \partial L }{ \partial y_j }
-    \frac{ \partial y_j }{ \partial x_j }.
-$}
-
-\sout{
-Finally, once the gradients $\partial L / \partial x_j$ have been
-computed, it is straightforward to compute the gradients for the weight,
-}
-\sout{$
-\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
-$}
+\sout{ The gradients in Equation~\ref{eq:gradient_descent} can be computed using the \textit{backpropagation} procedure, which is nothing more than an application of the chain rule for derivatives.
+The derivative of the loss function with respect to the input of a unit can be computed by working backwards from the gradient with respect to the output of the unit.
+At the output layer, the derivative of the loss function with respect to the output is given by }
+
+\sout{$ \frac{ \partial L }{ \partial y_i } = y_i - \hat{y}_i $}
+\sout{$ \frac{ \partial L }{ \partial x_i } = \frac{ \partial L }{ \partial y_i } \frac{ \partial y_i }{ \partial x_i }.  $}
+
+\sout{ At each hidden layer, the derivative of the loss function with respect to the output of each unit is a weighted sum of the derivatives with respect to the inputs of the subsequent layer, }
+\sout{$ \frac{ \partial L }{ \partial y_j } = \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i} $}
+\sout{$ \frac{ \partial L }{ \partial x_j } = \frac{ \partial L }{ \partial y_j } \frac{ \partial y_j }{ \partial x_j }.  $}
+
+\sout{ Finally, once the gradients $\partial L / \partial x_j$ have been computed, it is straightforward to compute the gradients for the weight, }
+\sout{$ \frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.  $}
 
@@
 
-\sout{
-TPC is a part of a publicly available software package called
-\textsc{MLZ}%\footnote{http://pythonhosted.org/MLZ/}
-(Machine Learning for Photo-$z$).
-}
-
-\sout{
-TPC uses classification trees,
-a type of prediction tree that is designed to
-provide a classification or predict a discrete category.
-Prediction trees are built by asking a sequence of questions
-that recursively split the data into branches
-until a terminal leaf is created
-that meets a stopping criterion
-(\eg a minimum leaf size).
-The optimal split dimension is decided by
-choosing the attribute that maximizes
-the \textit{Information Gain} ($I_G$), which is defined as
-}
-
-\sout{ $
-  I_G \left(D_{\rmn{node}}, X\right)
-  = I_d \left( D_{\rmn{node}} \right)
-  - \sum_{x \in \rmn{values}(X)}
-  \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|}
-  I_d \left( D_{\rmn{node}, x} \right),
-$ }
-
-\sout{
-\noindent
-where $D_{\rmn{node}}$ is the training data in a given node,
-$X$ is one of the possible dimensions (\eg magnitudes or colors)
-along which the node is split, and
-$x$ are the possible values of a specific dimension $X$.
-$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data
-and the number of objects in a given subset $x$ within the current node,
-respectively.
-$I_d$ is the impurity degree index,
-and TPC can calculate $I_d$
-from any of the three standard different impurity indices:
-\textit{information entropy}, \textit{Gini impurity},
-and \textit{classification error}.
-In this work, we use the information entropy,
-which is defined similarly to the thermodynamic entropy:
-}
-
-\sout{ $
-  I_d \left( D \right)
-  = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right),
-$ }
-
-\sout{
-\noindent
-where $f_g$ is the fraction of galaxies in the training data.
-At each node in our tree,
-we scan all dimensions to identify the split point that
-maximizes the information gain as defined by Equation~\ref{eq:information_gain},
-and select the attribute that maximizes the overall impurity index.
-}
-
-\sout{
-In a technique called random forest,
-we create bootstrap samples
-(\ie $N$ randomly selected objects with replacement)
-from the input training data
-by sampling repeatedly from the magnitudes and colors
-using their measurement errors.
-We use these bootstrap samples to construct
-multiple, uncorrelated prediction trees
-whose individual predictions are aggregated to produce
-a star-galaxy classification for each source.
+\sout{ TPC is a part of a publicly available software package called \textsc{MLZ}%\footnote{http://pythonhosted.org/MLZ/} (Machine Learning for Photo-$z$).
+}
+
+\sout{ TPC uses classification trees, a type of prediction tree that is designed to provide a classification or predict a discrete category.
+Prediction trees are built by asking a sequence of questions that recursively split the data into branches until a terminal leaf is created that meets a stopping criterion (\eg a minimum leaf size).
+The optimal split dimension is decided by choosing the attribute that maximizes the \textit{Information Gain} ($I_G$), which is defined as }
+
+\sout{ $ I_G \left(D_{\rmn{node}}, X\right) = I_d \left( D_{\rmn{node}} \right) - \sum_{x \in \rmn{values}(X)} \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|} I_d \left( D_{\rmn{node}, x} \right), $ }
+
+\sout{ \noindent where $D_{\rmn{node}}$ is the training data in a given node, $X$ is one of the possible dimensions (\eg magnitudes or colors) along which the node is split, and $x$ are the possible values of a specific dimension $X$.
+$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data and the number of objects in a given subset $x$ within the current node, respectively.
+$I_d$ is the impurity degree index, and TPC can calculate $I_d$ from any of the three standard different impurity indices: \textit{information entropy}, \textit{Gini impurity}, and \textit{classification error}.
+In this work, we use the information entropy, which is defined similarly to the thermodynamic entropy: }
+
+\sout{ $ I_d \left( D \right) = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right), $ }
+
+\sout{ \noindent where $f_g$ is the fraction of galaxies in the training data.
+At each node in our tree, we scan all dimensions to identify the split point that maximizes the information gain as defined by Equation~\ref{eq:information_gain}, and select the attribute that maximizes the overall impurity index.
+}
+
+\sout{ In a technique called random forest, we create bootstrap samples (\ie $N$ randomly selected objects with replacement) from the input training data by sampling repeatedly from the magnitudes and colors using their measurement errors.
+We use these bootstrap samples to construct multiple, uncorrelated prediction trees whose individual predictions are aggregated to produce a star-galaxy classification for each source.
 }
@@
 
-\sout{
-We note that TPC is able to utilize parallelization, and parallelized on 64
-cores of Xeon E5 2.7 GHz processors, it takes 23 minutes to train 500 trees,
-for a total of 25 CPU hours.
-}
+\sout{ We note that TPC is able to utilize parallelization, and parallelized on 64 cores of Xeon E5 2.7 GHz processors, it takes 23 minutes to train 500 trees, for a total of 25 CPU hours.  }
 

### 2016-08-10 paper/main.tex
[issue 0.3, 1.2, 2.7] shorten sections

@@
 \changed{
-In addition to artificially increasing the size of the dataset,
+In addition to artificially increasing the size of the data set,
 these data augmentation schemes make the resulting model more invariant to
@@
 we find that applying BMC still results in a significant increase in performance.
-
-The posterior probability that a source is a galaxy is given by
-\begin{equation} \label{eq:posterior_bmc}
-  P \left(G | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right)
-  = \sum_{e \in \bmath{E}} P \left(G | \bmath{x}, \bmath{M}, e \right)
-  P \left(e | \bmath{D} \right),
-\end{equation}
-where $\bmath{x}$ is the input, $\bmath{D}$ is the data set,
-$\bmath{M}$ is the set of models (\ie different transformations of input images),
-and $e$ is an element in the ensemble space $\bmath{E}$ of possible model combinations.
-By Bayes' Theorem, the posterior probability of $e$ given $\bmath{D}$ is given by
-\begin{equation} \label{eq:p_ensemble}
-  P \left(e | \bmath{D} \right)
-  = \frac{P \left(e \right)}{P \left(\bmath{D} \right)}
-  \prod_{d \in \bmath{D}} P \left( d | e \right)
-  \propto P \left(e\right) \prod_{d \in \bmath{D}} P \left(d | e \right).
-\end{equation}
-Here, $P\left(e \right)$ is the prior probability of $e$,
-which we assume to be uniform.
-The product of $P\left(d | e\right)$ is
-over all individual data $d$ in the training data $\bmath{D}$,
-and $P\left(\bmath{D}\right)$ is merely a normalization factor
-and not important.
-For probabilistic classifiers,
-we can directly use the probabilistic predictions
-and write Equation~\ref{eq:p_ensemble} as
-\begin{equation} \label{eq:p_ensemble_prob}
-  P \left( e | \bmath{D} \right) \propto 
-  P \left( e \right) \prod_{i=1}^{N}
-  \hat{y}_i y_i + 
-  \left(1 - \hat{y}_i\right) \left(1 - y_i\right).
-\end{equation}
-
-Although the space $\bmath{E}$ of potential model combinations
-is in principle infinite,
-we can produce a reasonable finite set
-of potential model combinations by using sampling techniques.
-In our implementation,
-the weights of each combination of the base classifiers
-is obtained by sampling from a Dirichlet distribution.
+\changed{
+Although a complete description of BMC is beyond the scope of this paper,
+we provide a brief description.
+For more details, we refer the reader to \citet{Monteith2011}.
+}
+
+\sout{ The posterior probability that a source is a galaxy is given by }
+\sout{ $ P \left(G | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right) = \sum_{e \in \bmath{E}} P \left(G | \bmath{x}, \bmath{M}, e \right) P \left(e | \bmath{D} \right), $ }
+\sout{ where $\bmath{x}$ is the input, $\bmath{D}$ is the data set, $\bmath{M}$ is the set of models (\ie different transformations of input images), and $e$ is an element in the ensemble space $\bmath{E}$ of possible model combinations.
+By Bayes' Theorem, the posterior probability of $e$ given $\bmath{D}$ is given by }
+\sout{$ P \left(e | \bmath{D} \right) = \frac{P \left(e \right)}{P \left(\bmath{D} \right)} \prod_{d \in \bmath{D}} P \left( d | e \right) \propto P \left(e\right) \prod_{d \in \bmath{D}} P \left(d | e \right).
+$}
+\sout{Here, $P\left(e \right)$ is the prior probability of $e$, which we assume to be uniform.
+The product of $P\left(d | e\right)$ is over all individual data $d$ in the training data $\bmath{D}$, and $P\left(\bmath{D}\right)$ is merely a normalization factor and not important.
+For probabilistic classifiers, we can directly use the probabilistic predictions and write Equation~\ref{eq:p_ensemble} as}
+\sout{ $ P \left( e | \bmath{D} \right) \propto P \left( e \right) \prod_{i=1}^{N} \hat{y}_i y_i + \left(1 - \hat{y}_i\right) \left(1 - y_i\right), $}
+
+\sout{Although the space $\bmath{E}$ of potential model combinations is in principle infinite, we can produce a reasonable finite set of potential model combinations by using sampling techniques.
+In our implementation, the weights of each combination of the base classifiers is obtained by sampling from a Dirichlet distribution.
 We first set all alpha values of a Dirichlet distribution to unity.
-We then sample this distribution $q$ times
-to obtain $q$ sets of weights.
-For each combination,
-we assume a uniform prior and
-calculate $P\left(e|\bmath{D}\right)$ using
-Equation~\ref{eq:p_ensemble_prob}.
-We select the combination with the highest $P\left(e|\bmath{D}\right)$,
-and update the alpha values by
-adding the weights of the most probable combination
-to the current alpha values.
-The next $q$ sets of weights are drawn
-using the updated alpha values.
-
-We continue the sampling process until
-we reach a predefined number of combinations,
-and we finally use Equation~\ref{eq:posterior_bmc} to compute
-the posterior probability that a source is a star (or a galaxy).
-In this paper, we use a $q$ value of three,
-and we consider a total of 1,000 model combinations.
+We then sample this distribution $q$ times to obtain $q$ sets of weights.
+For each combination, we assume a uniform prior and calculate $P\left(e|\bmath{D}\right)$ using Equation~\ref{eq:p_ensemble_prob}.
+We select the combination with the highest $P\left(e|\bmath{D}\right)$, and update the alpha values by adding the weights of the most probable combination to the current alpha values.
+The next $q$ sets of weights are drawn using the updated alpha values.}
+
+\sout{We continue the sampling process until we reach a predefined number of combinations, and we finally use Equation~\ref{eq:posterior_bmc} to compute the posterior probability that a source is a star (or a galaxy).
+In this paper, we use a $q$ value of three, and we consider a total of 1,000 model combinations.}
 

### 2016-08-10 paper/main.tex
minor fixes

@@
 We compute the loss function by taking the average of all cross-entropies in the sample.
-Thus,
-\changed{
-given $N$ samples,
-}
-the loss function becomes
+Thus, the loss function becomes
 \begin{equation}
@@
 \changed{
-Although a complete description of BMC is beyond the scope of this paper,
-we provide a brief description.
-For more details, we refer the reader to \citet{Monteith2011}.
+For a thorough discussion of BMC, we refer the reader to \citet{Monteith2011}.
 }

### 2016-08-10 paper/main.tex
[issue 2.6] introducing sentence in section 3
[issue 2.7] add some references

@@
 
+\changed{
+In this section, we first provide a brief overview of deep neural networks,
+including convolutional neural networks (ConvNets).
+We then describe the precise network architecture and the details of key
+hyperparamters.
+}
+
 \subsection{Neural Networks}
@@
 Then, the output of the neuron is
+\changed{
+\citep{rosenblatt1961principles}
+}
 \begin{equation}
@@
 over the training data.
-In this work, we use \textit{cross-entropy},
+In this work, we use \textit{cross-entropy}
+\changed{
+\citep{murphy2012machine},
+}
 \begin{equation}
@@
 }
-pooling layer computes the maximum of a local $2\times2$ patch in a feature map.
+pooling layer computes the maximum of a local $2\times2$ patch in a feature map
+\changed{
+\citep{krizhevsky2012imagenet}.
+}
 Since the pooling layer aggregates the activations of neighboring units from the previous layer,

### 2016-08-10 paper/main.tex
[issue 2.8] cross-entropy is for binary classification

@@
 \changed{
-\citep{murphy2012machine},
-}
+\citep[also called log loss;][]{murphy2012machine} as the loss function.
+For binary classification, the cross-entropy per sample is given by
 \begin{equation}
@@
 \end{equation}
+}
 where $\hat{y}_j$ is the actual truth value (\eg 0 or 1) of the $j$-th data, and

### 2016-08-11 paper/main.tex
[issue 2.15] greater depth

@@
 convolutional layer leads to worse performance.
-This result is in agreement with \citet{simonyan2014very},
-which features an extremely homogeneous architecture that only performs
+This result is in agreement with
+\changed{
+the network of \citet{simonyan2014very}, which has become known as ``VGGNet".
+}
+VGGNet features an extremely homogeneous architecture that only performs
 $3\times3$ convolutions.
@@
 a stack of two $3\times3$ convolutional layers increases the validation error,
-but we still follow \citet{simonyan2014very} and add many
-$3\times3$ convolutions (with zero-padding) in the remaining layers.
+\changed{
+and thus use a $5\times5$ convolution in the first layer.
+}
+
+\changed{
+In the remaining layers, we still follow VGGNet and add many
+$3\times3$ convolutions (with zero-padding of size 1 pixel).
+Note that with the padding of 1 pixel for $3\times3$ convolutional layers,
+the spatial resolution will be preserved after convolution.
+Such preservation of spatial resolution allows us to build relatively deep
+networks, as shown in Table~\ref{table:hyperparamters}.
+The main contribution of VGGNet is in showing that the depth plays an important
+role in good performance.
+In our case, we start with four convolutional layers and progressively add more
+layers, while monitoring the validation loss;
+we stop at eight convolutoinal layers after we find that adding more layers
+leads to worse performance.
+We conjecture that a greater depth and hence larger number of parameters
+lead to overfitting in our case.
+}
 

### 2016-08-11 paper/main.tex
[issue 2.17] why tpc, not sklearn rf?

@@
 \cite{carrascokind2013tpz} and \cite{kim2015hybrid} for more details.
+While other random forest implementations exist, we have chosen TPC, because
+it is tailored specifically for astronomical use~\citep{carrascokind2013tpz};
+it has been tested for astronomical use cases, including
+photometric redshift estimation~\citep{sanchez2014photometric}
+and star-galaxy classification~\citep{kim2015hybrid};
+it adds an extra layer of randomness by perturbing the measured attributes by
+their uncertainties;
+and it uses parallelism to handle large data sets on distributed memory systems.
 }

### 2016-08-11 paper/main.tex
[issue 2.29] reduce self reference

@@
 Machine learning techniques have been a popular tool
-in many areas of astronomy~\citep{ball2007robust,ball2008robust,
+in many areas of astronomy~\citep{ball2008robust,
 banerji2010galaxy,
-carrascokind2013tpz,carrascokind2014somz,carrascokind2014exhausting,
+carrascokind2013tpz,
 ivezic2014statistics,
-kamdar2016machine1,kamdar2016machine2}. 
+kamdar2016machine1}. 
 Artificial neural networks were first applied to the problem of star-galaxy

### 2016-08-11 paper/main.tex
[issue 2.23] log loss

@@
   $\mid\Delta N_g\mid / N_g$ & Absolute error in number of galaxies\\
+\changed{
+log loss
+}
+&
+\changed{
+Cross-entropy
+}
+\\
   \hline
@@
   \centering
-  \begin{tabular}{l c c c c c c}
+  \begin{tabular}{l c c c c c c c}
     \hline
-    classifier & AUC & MSE & $p_{g}(c_g=0.96)$ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ \\
+    classifier & AUC & MSE & $p_{g}(c_g=0.96)$ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ &
+\changed{
+log loss
+}
+\\
     \hline
-    ConvNet                       & \textbf{0.9948} & 0.0112          & \textbf{0.9972} & 0.8971          & \textbf{0.0197}  & \textbf{0.0029} \\
-    TPC${}_{\rmn{morph}}$         & 0.9924          & \textbf{0.0109} & 0.9963          & \textbf{0.9268} & 0.0245           & 0.0056 \\
-    TPC${}_{\rmn{phot}}$          & 0.9876          & 0.0189          & 0.9927          & 0.8044          & 0.0266           & 0.0101 \\
+    ConvNet                       & \textbf{0.9948} & 0.0112          & \textbf{0.9972} & 0.8971          & \textbf{0.0197}  & \textbf{0.0029} &
+\changed{
+\textbf{0.0441}
+}
+\\
+    TPC${}_{\rmn{morph}}$         & 0.9924          & \textbf{0.0109} & 0.9963          & \textbf{0.9268} & 0.0245           & 0.0056 &
+\changed{
+0.0809
+}
+\\
+    TPC${}_{\rmn{phot}}$          & 0.9876          & 0.0189          & 0.9927          & 0.8044          & 0.0266           & 0.0101 &
+\changed{
+0.1085
+}
+\\
     \hline
@@
 The bold entries highlight the best technique for any particular metric.
-ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ in four metrics (AUC, $p_g$, CAL,
-and $|\Delta N_g|/N_g$), while $\rmn{TPC}_{\rmn{morph}}$ performs better in
-two metrics (MSE and $c_g$).
+ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ in \changed{five} metrics
+(AUC, $p_g$, CAL, $|\Delta N_g|/N_g$, \changed{and log loss}),
+while $\rmn{TPC}_{\rmn{morph}}$ performs better in two metrics (MSE and $c_g$).
 It is not surprising that $\rmn{TPC}_{\rmn{phot}}$, which is trained on only
@@
 $\rmn{TPC}_{\rmn{phot}}$.
-As Figure~\ref{fig:clens_color_color} shows, there is significant overlap
-between stars and galaxies in color-color space.
+\sout{ As Figure~\ref{fig:clens_color_color} shows, there is significant overlap between stars and galaxies in color-color space.  }
 Thus, magnitudes and colors alone are not sufficient to separate stars from

### 2016-08-11 paper/main.tex
[issue 2.23] log loss

@@
   \centering
-  \begin{tabular}{l c c c c c c}
+  \begin{tabular}{l c c c c c c c}
     \hline
-    classifier & AUC & MSE & $p_{g}(c_g=0.96) $ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ \\
+    classifier & AUC & MSE & $p_{g}(c_g=0.96) $ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ & \changed{log loss} \\
     \hline
-    ConvNet               & 0.9952          & 0.0182          & 0.9915          & 0.9500          & \textbf{0.0243} & 0.0157          \\
-    TPC${}_{\rmn{morph}}$ & \textbf{0.9967} & \textbf{0.0099} & \textbf{0.9977} & \textbf{0.9810} & 0.0254          & \textbf{0.0044} \\
-    TPC${}_{\rmn{phot}}$  & 0.9886          & 0.0283          & 0.9819          & 0.8879          & 0.0316          & 0.0160 \\
+    ConvNet               & 0.9952          & 0.0182          & 0.9915          & 0.9500          & \textbf{0.0243} & 0.0157 & \changed{\textbf{0.0731}} \\
+    TPC${}_{\rmn{morph}}$ & \textbf{0.9967} & \textbf{0.0099} & \textbf{0.9977} & \textbf{0.9810} & 0.0254          & \textbf{0.0044} & \changed{0.0914} \\
+    TPC${}_{\rmn{phot}}$  & 0.9886          & 0.0283          & 0.9819          & 0.8879          & 0.0316          & 0.0160 & \changed{0.1372} \\
     \hline
@@
 it is apparent that $\rmn{TPC}_{\rmn{morph}}$ outperforms ConvNet
-in all metrics except $\rmn{CAL}$.
+in all metrics except $\rmn{CAL}$
+\changed{
+and cross-entropy.
+}
 Both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ still outperform

### 2016-08-11 paper/main.tex
[issue 2.27] add sdss feature maps

@@
 \end{figure}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_galaxy_original.pdf}
+    \caption{Input (5 bands$\times44\times44$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_galaxy_conv11.pdf}
+    \caption{Layer 1 (32 maps$\times40\times40$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_galaxy_conv21.pdf}
+    \caption{Layer 3 (64 maps$\times20\times20$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_galaxy_conv31.pdf}
+    \caption{Layer 6 (128 maps$\times10\times10$)}
+  \end{subfigure}
+  \caption{
+\changed{
+    Similar to Figure~\ref{fig:galaxy_activations} but for a galaxy in the
+    SDSS data set.
+}
+    }
+  \label{fig:sdss_galaxy_activations}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_star_original.pdf}
+    \caption{Input (5 bands$\times44\times44$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_star_conv11.pdf}
+    \caption{Layer 1 (32 maps$\times40\times40$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_star_conv21.pdf}
+    \caption{Layer 3 (64 maps$\times20\times20$)}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[c]{0.24\linewidth}
+  \centering
+    \includegraphics[width=\textwidth]{figures/sdss_star_conv31.pdf}
+    \caption{Layer 6 (128 maps$\times10\times10$)}
+  \end{subfigure}
+  \caption{
+\changed{
+    Similar to Figure~\ref{fig:sdss_galaxy_activations} but for a star in the
+    SDSS data set.
+}
+    }
+  \label{fig:sdss_star_activations}
+\end{figure*}
 
@@
 
+\changed{
+Figures~\ref{fig:sdss_galaxy_activations} and \ref{fig:sdss_star_activations}
+show the activations when images of a galaxy and a star are fed into the network. 
+Similarly to Figures~\ref{fig:galaxy_activations} and \ref{fig:star_activations}
+in Section~\ref{sec:results_cfht},
+the feature maps show hierarchical abstraction from low-level features in the
+first convolutional layer to high-level features in the subsequent layers.
+This hierarchical abstraction is what enables ConvNets to learn morphological
+features automatically from images.
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-08-11 paper/main.tex
[issue 1.3] include multilayer perceptron

@@
 neural network architectures.
+\changed{
+Futhermore, future work could compare the performance of other deep learning
+variants, such as deep belief networks~\citep{hinton2006fast},
+deep Boltzmann machines~\citep{salakhutdinov2009deep}, and
+multilayer perceptrons~\citep{wasserman1988neural}.
+}
 
@@
 predictive performance.
+
+\changed{
+Finally, we are currently exploring different strategies for including objects
+that are neither stars nor galaxies (\eg quasars).
+The results of this multi-class problem will be presented in subsequent papers.
+}
 

### 2016-08-12 paper/main.tex
[issue 2.22] add probability thresholds

--- 2016-08-11 paper/main.tex
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2015}
+\pubyear{2016}
 
@@
 which is trained on both morphological and photometric attributes.
+
+\changed{
+Note that $p_{g}(c_g=0.96)$ and $c_{s}(p_s=0.97)$ require adjusting
+threshold values (\ie probability cuts), while other metrics do not.
+To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
+0.9972, 0.9963, and 0.9927 for ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$,
+respectively;
+for star purity $p_s=0.97$, we choose 0.6990, 0.5297, and 0.8570 for
+ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$, respectively.
+In Table ? and ?, we present example.
+}
 
@@
 neural network architectures.
+\changed{
+Futhermore, future work could compare the performance of other deep learning
+variants, such as deep belief networks~\citep{hinton2006fast},
+deep Boltzmann machines~\citep{salakhutdinov2009deep}, or
+multilayer perceptrons~\citep{wasserman1988neural}.
+}
 

### 2016-08-12 paper/main.tex
[issue 0.3] shorten section 6.1

@@
 Support Vector Machines~\citep{Fadely2012}, and
-classifier combination strategies~\citep{kim2015hybrid}.
+classifier combination strategies~\citep*{kim2015hybrid}.
 
@@
 
-Probabilistic classification models can be considered as
-functions that output a probability estimate of each source
-to be in one of the classes (\eg a star or a galaxy).
-The simplest way to use the probability output is to
-convert it into a class label by using a threshold (a probability cut).
-Although many studies often choose the threshold by setting it to a fixed value,
-such as $P_{\rmn{cut}} = 0.5$ \citep[\eg][]{henrion2011bayesian, Fadely2012},
-choosing $0.5$ as a threshold is not the best choice
-for an unbalanced data set, where galaxies outnumber stars.
-Furthermore, setting a fixed threshold ignores the operating condition 
-(\eg science requirements, stellar distribution, misclassification costs)
-where the model will be applied.
+\changed{
+Probabilistic classifiers, rather than only assigning discrete labels to each
+source, produce a continuous probability distribution of whether each source is
+a star or a galaxy.
+To evaluate the performance of probabilistic classifiers,
+many studies~\citep[\eg][]{henrion2011bayesian, Fadely2012} convert
+probability estimates into class labels by choosing a probability
+threshold, \eg a source is classified as a star if $P_{\rmn{class}} < 0.5$,
+and a galaxy if $P_{\rmn{class}} > 0.5$.
+However, using a fixed threshold ignores the model's operating conditions,
+such as science requirements, misclassification costs, and stellar distribution.
+Furthermore, the probability threshold of 0.5 is not necessarily optimal for
+an unbalanced data set, where galaxies outnumber stars.
+Following \citet{kim2015hybrid}, we use performance metrics that are well-suited
+for probabilistic classifiers: Area Under the Curve (AUC)
+for the Receiver Operating Characteristic (ROC) curve, completeness and purity,
+and the Mean Squared Error (MSE).
+To evaluate 
+we also use the calibration error and the absolute error in the estimation
+of number of galaxies as performance metrics.
+}
 
@@
 
-When we have no information about the operating condition
-when evaluating the performance of classifiers,
-there are effective tools such as
-the Receiver Operating Characteristic (ROC) curve
-\citep*{swets2000better}.
-An ROC curve is a graphical plot that illustrates the true positive rate
-versus the false positive rate of a binary classifier
-as its classification threshold is varied.
-The Area Under the Curve (AUC) summarizes the curve information
-in a single number,
-and can be used as an assessment of the overall performance.
+\changed{
+A Receiver Operating Characteristic (ROC) curve is the
+most commonly used method for evaluating the overall performance of a binary
+classifier~\citep*{swets2000better}.
+In an ROC curve, we plot the true positive rate as a function of the false
+positive rate by varying the classification threshold.
+The Area Under the Curve (AUC) quantifies the overall performance in a single
+number.
+}
 
 \subsubsection{Completeness and Purity}
-
-In astronomical applications,
-the operating condition usually translates to
-the completeness and purity requirements of the star or galaxy sample.
-We define the galaxy \textit{completeness}
-$c_g$ (also known as recall or sensitivity) as
-the fraction of the number of true galaxies classified as galaxies
-out of the total number of true galaxies,
-\begin{equation}
-c_g = \frac{N_g}{N_g + M_g},
-\end{equation}
-
-\noindent
-where $N_g$ is the number of true galaxies classified as galaxies,
-and $M_g$ is the number of true galaxies classified as stars.
-We define the galaxy \textit{purity} $p_g$ (also known as precision
-or positive predictive value)
-as the fraction of the number of true galaxies classified as galaxies
-out of the total number of objects classified as galaxies, 
-\begin{equation}
-p_g = \frac{N_g}{N_g + M_s},
-\end{equation}
-
-\noindent
-where $M_s$ is the number of true stars classified as galaxies.
-Star completeness and purity are defined in a similar manner.
-
-One of the advantages of a probabilistic classification is
-that the threshold can be adjusted to produce
-a more complete but less pure sample,
-or a less complete but more pure one.
-We can compare the performance of different classification techniques
-by assuming an arbitrary operating condition.
-For example, weak lensing science measurements
-of the DES require $c_g > 0.960$ and $p_g > 0.778$
-to control both the statistical and systematic errors
-on the cosmological parameters,
-and $c_s > 0.250$ and $p_s > 0.970$
-for stellar Point Spread Function (PSF) calibration
-\citep{soumagnac2013star}.
-Although these values will likely be different
-for the science cases of the CFHTLenS data,
-we adopt these values to compare the classification performance
-at a reasonable operating condition.
-Thus, we compute $p_{g}$ at $c_g=0.960$
-and $c_{s}$ at $p_s=0.970$.
 

### 2016-08-13 paper/main.tex
update paper

@@
 $^3$Department of Statistics, University of Illinois, Champaign, IL 61820 USA\\
-$^4$National Center for Supercomputing Applications, Urbana, IL 61801 USA
-}
+$^4$National Center for Supercomputing Applications, Urbana, IL 61801 USA }
 
@@
 
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=\columnwidth]{figures/sdss_color_color.pdf}
-%  \caption{
-%    Hexbin plots showing the color-color space distribution of galaxies (blue, top row) and stars (green, bottom row)
-%    in the SDSS data set used in this analysis.
-%    It is easy to see that there is significant overlap between stars
-%    and galaxies in these color-color spaces. 
-%  }
-%  \label{fig:sdss_color_color}
-%\end{figure}
-
 The Sloan Digital Sky Survey~\citep[SDSS;][]{york2000sloan}
@@
 and to center each object in the cutout image.
-{
+\changed{
 Magnitudes in the SDSS photometric catalog are expressed as inverse hyperbolic
@@
 
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=\columnwidth]{figures/clens_color_color.pdf}
-%  \caption{
-%    Hexbin plots showing the color-color space distribution of
-%    galaxies (blue, top row) and stars (green, bottom row)
-%    in the CFHTLenS data set used in this analysis.
-%  }
-%  \label{fig:clens_color_color}
-%\end{figure}
-
 We also use photometric data from
@@
 \changed{
-In this section, we first provide a brief overview of deep neural networks,
-including convolutional neural networks (ConvNets).
+In this section, we first provide a brief overview of deep neural networks
+including convolutional neural networks.
 We then describe the precise network architecture and the details of key
@@
 Many deep learning models use feedforward neural network architectures with multiple layers,
-where each neuron in one layer is connected to the neurons of the subsequent layer.
+where each neuron in one layer is connected to the neurons of the subsequent
+layer~\citep{lecun2015deep}.
 A schematic representation is shown in Figure~\ref{fig:neuron_b}.
@@
 
-The goal of learning is to find a set of weights and biases such that,
+\changed{
+We
+}
+find a set of weights and biases such that,
 given $N$ samples, the output from the network
@@
 it reduces the dimensionality of the feature maps and
-makes the model invariant to small shifts and distortions.
+makes the model invariant to small shifts and distortions
+\changed{
+\citep{boureau2010theoretical}
+}
+.
 Two or more layers of convolution and pooling are stacked,
@@
 \changed{
-For a thorough discussion of BMC, we refer the reader to \citet{Monteith2011}.
+For a thorough discussion of BMC, we refer the reader to \citet{Monteith2011}
+(See also \citet{carrascokind2014exhausting} for application of BMC to
+photometric estimation, and \citet{kim2015hybrid} for combining star-galaxy
+classifiers).
 }
@@
 and it uses parallelism to handle large data sets on distributed memory systems.
-}
-
-\sout{ TPC is a part of a publicly available software package called \textsc{MLZ}%\footnote{http://pythonhosted.org/MLZ/} (Machine Learning for Photo-$z$).
 }
@@
 an unbalanced data set, where galaxies outnumber stars.
+}
+
+\changed{
 Following \citet{kim2015hybrid}, we use performance metrics that are well-suited
@@
 and the Mean Squared Error (MSE).
-To evaluate 
+A good probabilistic classifier should also provide well-calibrated
+posterior probabilities.
+Thus, to evaluate calibration performance,
 we also use the calibration error and the absolute error in the estimation
@@
 \subsubsection{Completeness and Purity}
+
+\changed{
+Let $N_g$ be the number of true galaxies classified as galaxies,
+and $M_g$ the number of true galaxies classified as stars.
+Then the galaxy \textit{completeness} $c_g$ (also called recall or sensitivity)
+is given by
+}
+\begin{equation}
+c_g = \frac{N_g}{N_g + M_g}.
+\end{equation}
+\changed{
+Let $M_s$ be the number of true stars classified as galaxies.
+Then the galaxy \textit{purity} $p_g$ (also called precision or positive
+predictive value) is given by
+}
+\begin{equation}
+p_g = \frac{N_g}{N_g + M_s}.
+\end{equation}
+\changed{
+We define the star completeness and purity in a similar way.
+As discussed in our previous work~\citep{kim2015hybrid},
+we adopt weak lensing science requirements of the DES~\citep{soumagnac2013star},
+and compute $p_g$ at $c_g=0.960$ and $c_s$ at $p_s=0.970$.
+}
 
@@
     The bold entries highlight the best performance values within each column.
+\changed{
+    Note that $p_{g}(c_g=0.96)$ and $c_{s}(p_s=0.97)$ require adjusting
+    threshold values (\ie probability cuts), while other metrics do not.
+    To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
+    0.9972, 0.9963, and 0.9927 for ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$,
+    respectively;
+    for star purity $p_s=0.97$, we choose 0.6990, 0.5297, and 0.8570 for
+    ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$, respectively.
+}
   }
@@
 
-\changed{
-Note that $p_{g}(c_g=0.96)$ and $c_{s}(p_s=0.97)$ require adjusting
-threshold values (\ie probability cuts), while other metrics do not.
-To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
-0.9972, 0.9963, and 0.9927 for ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$,
-respectively;
-for star purity $p_s=0.97$, we choose 0.6990, 0.5297, and 0.8570 for
-ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$, respectively.
-In Table ? and ?, we present example.
-}
-
 In Figure~\ref{fig:clens_mag}, we compare the galaxy purity
@@
     as applied to the SDSS data.
+\changed{
+    To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
+    0.7558, 0.9989, and 0.9360 for ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$,
+    respectively;
+    for star purity $p_s=0.97$, we choose 0.6046, 0.0547, and 0.7449 for
+    ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$, respectively.
+}
   }
@@
 \changed{
+Furthermore, our ConvNet is a supervised algorithm; and one of the criticisms
+of supervised techniques is their difficulty in extrapolating past the limits
+of available spectroscopic training data.
+Since it is difficult to assess the classification performance without a deeper
+spectroscopic sample, we have evaluated the performance on a test set
+that is drawn from the same underlying distribution as the spectroscopic sample.
+However, when our ConvNet model
+---trained on sources from a spectroscopic sample---
+is applied to a photometric sample
+---which is often fainter than our training set--- 
+the performance of ConvNet will be less reliable.
+Combining our ConvNet model with unsupervised methods (\eg a template fitting
+method) in this meta-classification framework will help improve the efficacy of
+star-galaxy classification beyond the limits of spectroscopic training data.
+}
+
+\changed{
 Finally, we are currently exploring different strategies for including objects
@@
 \changed{
-This work has made use of the Theano library (http://deeplearning.net/software/theano/),
-the Lasagne library (http://lasagne.readthedocs.io/),
-and the Nolearn library (http://pythonhosted.org/nolearn/).
+This work has made use of the Theano library
+(\href{http://deeplearning.net/software/theano/}{http://deeplearning.net/software/theano/}),
+the Lasagne library
+(\href{http://lasagne.readthedocs.io/)}{http://lasagne.readthedocs.io/}),
+and the Nolearn library
+(\href{http://pythonhosted.org/nolearn/}{http://pythonhosted.org/nolearn/}).
 }
@@
 \bibliographystyle{mnras}
-\bibliography{sg_paper}
-}
+\bibliography{sg_paper} }
 

### 2016-08-14 paper/main.tex
update paper

@@
 \usepackage{natbib}
-%\usepackage{url}
-\usepackage{hyperref}
+\usepackage{url}
+%\usepackage{hyperref}
 \usepackage{placeins}
@@
 \changed{
-In this section, we first provide a brief overview of deep neural networks
-including convolutional neural networks.
-We then describe the precise network architecture and the details of key
-hyperparamters.
+Neural networks have many hyperparameters, including those that specify the
+network itself (\eg the size and non-linearity of each layer)
+and those that specify how the network is trained
+(\eg the mini-batch size or the learning rate).
+Furthermore, the architecture of a neural network can have a
+significant impact on its performance.
+In this section, we provide a brief description of key hyperparameters in our
+ConvNet model, and also present the network architecture.
 }
@@
 Thus, a moderate batch size, combined with a decaying learning rate, is
-generally used in practice.
+generally used in practice. We use a batch size of 128 in this work.
 }
@@
 In the interest of scientific reproducibility, we make all our code available
-at \href{https://github.com/EdwardJKim/dl4astro}{https://github.com/EdwardJKim/dl4astro}.
+at \mbox{\url{https://github.com/EdwardJKim/dl4astro}}.
 
@@
 (See also \citet{carrascokind2014exhausting} for application of BMC to
-photometric estimation, and \citet{kim2015hybrid} for combining star-galaxy
-classifiers).
+photometric redshift estimation,
+and \citet{kim2015hybrid} for combining star-galaxy classifiers).
 }
@@
 we also use the calibration error and the absolute error in the estimation
-of number of galaxies as performance metrics.
+of number of galaxies.
 }
@@
     To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
-    0.9972, 0.9963, and 0.9927 for ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$,
-    respectively;
+    0.9972, 0.9963, and 0.9927 for ConvNet, TPC${}_{\rmn{morph}}$, and 
+    TPC${}_{\rmn{phot}}$, respectively;
     for star purity $p_s=0.97$, we choose 0.6990, 0.5297, and 0.8570 for
-    ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$, respectively.
+    ConvNet, TPC${}_{\rmn{morph}}$, and TPC${}_{\rmn{phot}}$, respectively.
 }
@@
 The bold entries highlight the best technique for any particular metric.
-ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ in \changed{five} metrics
-(AUC, $p_g$, CAL, $|\Delta N_g|/N_g$, \changed{and log loss}),
+ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ in
+\changed{
+five
+}
+metrics
+(AUC, $p_g$, CAL, $|\Delta N_g|/N_g$, 
+\changed{
+and log loss
+}
+),
 while $\rmn{TPC}_{\rmn{morph}}$ performs better in two metrics (MSE and $c_g$).
@@
     To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
-    0.7558, 0.9989, and 0.9360 for ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$,
-    respectively;
+    0.7558, 0.9989, and 0.9360 for ConvNet, TPC${}_{\rmn{morph}}$, and
+    TPC${}_{\rmn{phot}}$, respectively;
     for star purity $p_s=0.97$, we choose 0.6046, 0.0547, and 0.7449 for
-    ConvNet, TPC${}_{\rmn{morph}}$, TPC${}_{\rmn{phot}}$, respectively.
+    ConvNet, TPC${}_{\rmn{morph}}$, and TPC${}_{\rmn{phot}}$, respectively.
 }
@@
     \hline
-    classifier & AUC & MSE & $p_{g}(c_g=0.96) $ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ & \changed{log loss} \\
+    classifier & AUC & MSE & $p_{g}(c_g=0.96) $ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ &
+\changed{
+log loss
+}
+\\
     \hline
-    ConvNet               & 0.9952          & 0.0182          & 0.9915          & 0.9500          & \textbf{0.0243} & 0.0157 & \changed{\textbf{0.0731}} \\
-    TPC${}_{\rmn{morph}}$ & \textbf{0.9967} & \textbf{0.0099} & \textbf{0.9977} & \textbf{0.9810} & 0.0254          & \textbf{0.0044} & \changed{0.0914} \\
-    TPC${}_{\rmn{phot}}$  & 0.9886          & 0.0283          & 0.9819          & 0.8879          & 0.0316          & 0.0160 & \changed{0.1372} \\
+    ConvNet               & 0.9952          & 0.0182          & 0.9915          & 0.9500          & \textbf{0.0243} & 0.0157 &
+\changed{
+\textbf{0.0731}
+}
+\\
+    TPC${}_{\rmn{morph}}$ & \textbf{0.9967} & \textbf{0.0099} & \textbf{0.9977} & \textbf{0.9810} & 0.0254          & \textbf{0.0044} & 
+\changed{
+0.0914
+}
+\\
+    TPC${}_{\rmn{phot}}$  & 0.9886          & 0.0283          & 0.9819          & 0.8879          & 0.0316          & 0.0160 & 
+\changed{
+0.1372
+}
+\\
     \hline
@@
 \changed{
-Furthermore, our ConvNet is a supervised algorithm; and one of the criticisms
+Our ConvNet model is a supervised algorithm, and one of the criticisms
 of supervised techniques is their difficulty in extrapolating past the limits
@@
 Since it is difficult to assess the classification performance without a deeper
-spectroscopic sample, we have evaluated the performance on a test set
+spectroscopic sample, we evaluated the performance using a test set
 that is drawn from the same underlying distribution as the spectroscopic sample.
@@
 Combining our ConvNet model with unsupervised methods (\eg a template fitting
-method) in this meta-classification framework will help improve the efficacy of
-star-galaxy classification beyond the limits of spectroscopic training data.
+method) in the aforementioned meta-classification framework will
+help improve the efficacy of star-galaxy classification
+beyond the limits of spectroscopic training data.
 }
@@
 
-\changed{
-The authors thank the referees for a careful reading of the manuscript
-and comments that improved this work.
-}
 We acknowledge support from the 
@@
 This work has made use of the Theano library
-(\href{http://deeplearning.net/software/theano/}{http://deeplearning.net/software/theano/}),
+(http://deeplearning.net/software/theano/),
 the Lasagne library
-(\href{http://lasagne.readthedocs.io/)}{http://lasagne.readthedocs.io/}),
+(http://lasagne.readthedocs.io/),
 and the Nolearn library
-(\href{http://pythonhosted.org/nolearn/}{http://pythonhosted.org/nolearn/}).
+(http://pythonhosted.org/nolearn/).
 }
@@
 
-\footnotesize{
 \bibliographystyle{mnras}
-\bibliography{sg_paper} }
+\bibliography{sg_paper}
 

### 2016-08-15 paper/main.tex
remove sout and red text

@@
 such as magnitudes or shape information of an object.
-\changed{
 In a branch of machine learning called \textit{deep learning}~\citep{lecun2015deep},
@@
 that are important for classification tasks.
-}
 Deep learning has been applied successfully to galaxy morphological
@@
 
-\changed{
 To demonstrate the performance of our ConvNet model, we use photometric and
@@
 steps for retrieving cutout images.
-}
 
@@
 We consider only objects
-\sout{ whose $r$-band magnitude is less than 40; there are }
 with no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
@@
 and to center each object in the cutout image.
-\changed{
 Magnitudes in the SDSS photometric catalog are expressed as inverse hyperbolic
@@
 and we follow the SDSS convention and convert all flux values to luptitudes.
-}
 Finally, in order to account for the effect of Galactic dust,
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
-\sout{ The $ugriz$ color-color space of the sample is plotted in Figure ?.}
 We randomly split the objects into training, held-out validation,
@@
 and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
-\sout{ The $ugriz$ color-color space of the sample is plotted in Figure ?.}
 We randomly split the objects into training, held-out validation, and
@@
 
-\changed{
 Neural networks have many hyperparameters, including those that specify the
@@
 ConvNet model, and also present the network architecture.
-}
 
@@
 
-\sout{ A neuron in the human brain receives signals from other neurons through synaptic connections.
-If the combination of these signals exceeds a certain threshold, the neuron will fire and send a signal to other neurons.
-Intelligence is believed to be the collective effect of approximately $10^{11}$ neurons firing.
-}
 An artificial neuron in most artificial neural networks is represented
 as a mathematical function that models a biological neural structure
-\changed{
 \citep{aggarwal2014data}.
 A schematic representation is shown in Figure~\ref{fig:neuron_a}.
-}
 Let $\bmath{x}=\left(x_1,x_2,\dots,x_n\right)$ be a vector of inputs to a given neuron,
@@
 Then, the output of the neuron is
-\changed{
 \citep{rosenblatt1961principles}
-}
 \begin{equation}
@@
 where $\sigma$ is the activation function (or \textit{non-linearity}).
-\sout{ The sigmoid function, $\sigma(x)=1/\left(1+e^{-x}\right)$, has frequently been used as an activation function, but it has recently fallen out of favor, and the hyperbolic tangent function, $\sigma(x)=\tanh(x)$, is generally used instead.
-}
 The most popular non-linearity at present
-\sout{, however, }
 is the rectified linear unit
@@
 To mitigate this problem, we use leaky ReLUs
-\changed{
 ~\citep{maas2013rectifier}
-}
 that have a small, non-zero slope in the negative region,
@@
 All layers except the input and output layers are conveniently called hidden layers.
-\sout{ With multiple hidden layers, deep neural networks can model complex nonlinear relationships, and they have had great success in multimedia tasks where humans traditionally outperformed computers, such as speech recognition, language processing, and image classification.
-}
-
-\changed{
+
 We
-}
 find a set of weights and biases such that,
@@
 In this work, we use \textit{cross-entropy}
-\changed{
 \citep[also called log loss;][]{murphy2012machine} as the loss function.
@@
 \end{equation}
-}
 where $\hat{y}_j$ is the actual truth value (\eg 0 or 1) of the $j$-th data, and
@@
 \begin{equation}
-\changed{
   L(\bmath{y}, \hat{\bmath{y}})
-}
 = - \frac{1}{N} \sum_{j=1}^{N} \hat{y}_j  \log_2 y_j
@@
 where $\eta$ is a small, positive number known as the \textit{learning rate}.
-\changed{
 The gradients can be computed using the backpropagation
@@
 generally used in practice. We use a batch size of 128 in this work.
-}
 
@@
 
-\sout{ The gradients in Equation~\ref{eq:gradient_descent} can be computed using the \textit{backpropagation} procedure, which is nothing more than an application of the chain rule for derivatives.
-The derivative of the loss function with respect to the input of a unit can be computed by working backwards from the gradient with respect to the output of the unit.
-At the output layer, the derivative of the loss function with respect to the output is given by }
-
-\sout{$ \frac{ \partial L }{ \partial y_i } = y_i - \hat{y}_i $}
-\sout{$ \frac{ \partial L }{ \partial x_i } = \frac{ \partial L }{ \partial y_i } \frac{ \partial y_i }{ \partial x_i }.  $}
-
-\sout{ At each hidden layer, the derivative of the loss function with respect to the output of each unit is a weighted sum of the derivatives with respect to the inputs of the subsequent layer, }
-\sout{$ \frac{ \partial L }{ \partial y_j } = \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i} $}
-\sout{$ \frac{ \partial L }{ \partial x_j } = \frac{ \partial L }{ \partial y_j } \frac{ \partial y_j }{ \partial x_j }.  $}
-
-\sout{ Finally, once the gradients $\partial L / \partial x_j$ have been computed, it is straightforward to compute the gradients for the weight, }
-\sout{$ \frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.  $}
-
 \subsection{Convolutional Neural Networks}
@@
 that has recently become
-\changed{
 a popular
-}
 approach in the computer vision community.
@@
 
-\changed{
 The input to a convolutional layer is an image, and the output channels of
 each layer are called \textit{feature maps}.
-}
 To produce output feature maps, we convolve each feature map with a set of weights
@@
 
-\changed{
 Typically, a
-}
 pooling layer computes the maximum of a local $2\times2$ patch in a feature map
-\changed{
 \citep{krizhevsky2012imagenet}.
-}
 Since the pooling layer aggregates the activations of neighboring units from the previous layer,
@@
 makes the model invariant to small shifts and distortions
-\changed{
 \citep{boureau2010theoretical}
-}
 .
@@
 This result is in agreement with
-\changed{
 the network of \citet{simonyan2014very}, which has become known as ``VGGNet".
-}
 VGGNet features an extremely homogeneous architecture that only performs
@@
 a stack of two $3\times3$ convolutional layers increases the validation error,
-\changed{
 and thus use a $5\times5$ convolution in the first layer.
-}
-
-\changed{
+
 In the remaining layers, we still follow VGGNet and add many
@@
 lead to overfitting in our case.
-}
 
@@
 \end{itemize}
-\changed{
 In addition to artificially increasing the size of the data set,
@@
 We also note that the data augmentation steps
-}
 add almost no computational cost,
@@
 we find that applying BMC still results in a significant increase in performance.
-\changed{
 For a thorough discussion of BMC, we refer the reader to \citet{Monteith2011}
@@
 and \citet{kim2015hybrid} for combining star-galaxy classifiers).
-}
-
-\sout{ The posterior probability that a source is a galaxy is given by }
-\sout{ $ P \left(G | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right) = \sum_{e \in \bmath{E}} P \left(G | \bmath{x}, \bmath{M}, e \right) P \left(e | \bmath{D} \right), $ }
-\sout{ where $\bmath{x}$ is the input, $\bmath{D}$ is the data set, $\bmath{M}$ is the set of models (\ie different transformations of input images), and $e$ is an element in the ensemble space $\bmath{E}$ of possible model combinations.
-By Bayes' Theorem, the posterior probability of $e$ given $\bmath{D}$ is given by }
-\sout{$ P \left(e | \bmath{D} \right) = \frac{P \left(e \right)}{P \left(\bmath{D} \right)} \prod_{d \in \bmath{D}} P \left( d | e \right) \propto P \left(e\right) \prod_{d \in \bmath{D}} P \left(d | e \right).
-$}
-\sout{Here, $P\left(e \right)$ is the prior probability of $e$, which we assume to be uniform.
-The product of $P\left(d | e\right)$ is over all individual data $d$ in the training data $\bmath{D}$, and $P\left(\bmath{D}\right)$ is merely a normalization factor and not important.
-For probabilistic classifiers, we can directly use the probabilistic predictions and write Equation~\ref{eq:p_ensemble} as}
-\sout{ $ P \left( e | \bmath{D} \right) \propto P \left( e \right) \prod_{i=1}^{N} \hat{y}_i y_i + \left(1 - \hat{y}_i\right) \left(1 - y_i\right), $}
-
-\sout{Although the space $\bmath{E}$ of potential model combinations is in principle infinite, we can produce a reasonable finite set of potential model combinations by using sampling techniques.
-In our implementation, the weights of each combination of the base classifiers is obtained by sampling from a Dirichlet distribution.
-We first set all alpha values of a Dirichlet distribution to unity.
-We then sample this distribution $q$ times to obtain $q$ sets of weights.
-For each combination, we assume a uniform prior and calculate $P\left(e|\bmath{D}\right)$ using Equation~\ref{eq:p_ensemble_prob}.
-We select the combination with the highest $P\left(e|\bmath{D}\right)$, and update the alpha values by adding the weights of the most probable combination to the current alpha values.
-The next $q$ sets of weights are drawn using the updated alpha values.}
-
-\sout{We continue the sampling process until we reach a predefined number of combinations, and we finally use Equation~\ref{eq:posterior_bmc} to compute the posterior probability that a source is a star (or a galaxy).
-In this paper, we use a $q$ value of three, and we consider a total of 1,000 model combinations.}
 
@@
 to produce a star-galaxy classification.
-\changed{
 A complete description of TPC is beyond the scope of this paper, and
@@
 and it uses parallelism to handle large data sets on distributed memory systems.
-}
-
-\sout{ TPC uses classification trees, a type of prediction tree that is designed to provide a classification or predict a discrete category.
-Prediction trees are built by asking a sequence of questions that recursively split the data into branches until a terminal leaf is created that meets a stopping criterion (\eg a minimum leaf size).
-The optimal split dimension is decided by choosing the attribute that maximizes the \textit{Information Gain} ($I_G$), which is defined as }
-
-\sout{ $ I_G \left(D_{\rmn{node}}, X\right) = I_d \left( D_{\rmn{node}} \right) - \sum_{x \in \rmn{values}(X)} \frac{|D_{\rmn{node}, x}|}{|D_{\rmn{node}}|} I_d \left( D_{\rmn{node}, x} \right), $ }
-
-\sout{ \noindent where $D_{\rmn{node}}$ is the training data in a given node, $X$ is one of the possible dimensions (\eg magnitudes or colors) along which the node is split, and $x$ are the possible values of a specific dimension $X$.
-$|D_{\rmn{node}}|$ and $|D_{\rmn{node}, x}|$ are the size of the total training data and the number of objects in a given subset $x$ within the current node, respectively.
-$I_d$ is the impurity degree index, and TPC can calculate $I_d$ from any of the three standard different impurity indices: \textit{information entropy}, \textit{Gini impurity}, and \textit{classification error}.
-In this work, we use the information entropy, which is defined similarly to the thermodynamic entropy: }
-
-\sout{ $ I_d \left( D \right) = - f_g \log_{2} f_g - \left(1 - f_g\right) \log_{2} \left(1 - f_g\right), $ }
-
-\sout{ \noindent where $f_g$ is the fraction of galaxies in the training data.
-At each node in our tree, we scan all dimensions to identify the split point that maximizes the information gain as defined by Equation~\ref{eq:information_gain}, and select the attribute that maximizes the overall impurity index.
-}
-
-\sout{ In a technique called random forest, we create bootstrap samples (\ie $N$ randomly selected objects with replacement) from the input training data by sampling repeatedly from the magnitudes and colors using their measurement errors.
-We use these bootstrap samples to construct multiple, uncorrelated prediction trees whose individual predictions are aggregated to produce a star-galaxy classification for each source.
-}
 
@@
 colors, for a total of
-\changed{
 fourteen
-}
 dimensions.
 The concentration is defined as the difference between the
-\sout{cmodel and}
-\changed{
 PSF magnitude (psfMag) and the composite model magnitude (cModelMag), \ie
-}
 $\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
@@
 for a total of twelve dimensions.
-
-\sout{ We note that TPC is able to utilize parallelization, and parallelized on 64 cores of Xeon E5 2.7 GHz processors, it takes 23 minutes to train 500 trees, for a total of 25 CPU hours.  }
 
@@
   $\mid\Delta N_g\mid / N_g$ & Absolute error in number of galaxies\\
-\changed{
 log loss
-}
 &
-\changed{
 Cross-entropy
-}
 \\
@@
 
-\changed{
 Probabilistic classifiers, rather than only assigning discrete labels to each
@@
 an unbalanced data set, where galaxies outnumber stars.
-}
-
-\changed{
+
 Following \citet{kim2015hybrid}, we use performance metrics that are well-suited
@@
 of number of galaxies.
-}
 
@@
 
-\changed{
 A Receiver Operating Characteristic (ROC) curve is the
@@
 number.
-}
 
@@
 
-\changed{
 Let $N_g$ be the number of true galaxies classified as galaxies,
@@
 is given by
-}
 \begin{equation}
@@
 \end{equation}
-\changed{
 Let $M_s$ be the number of true stars classified as galaxies.
@@
 predictive value) is given by
-}
 \begin{equation}
@@
 \end{equation}
-\changed{
 We define the star completeness and purity in a similar way.
@@
 and compute $p_g$ at $c_g=0.960$ and $c_s$ at $p_s=0.970$.
-}
 
@@
     The bold entries highlight the best performance values within each column.
-\changed{
     Note that $p_{g}(c_g=0.96)$ and $c_{s}(p_s=0.97)$ require adjusting
@@
   }
-  }
   \centering
@@
     classifier & AUC & MSE & $p_{g}(c_g=0.96)$ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ &
-\changed{
 log loss
-}
 \\
@@
     ConvNet                       & \textbf{0.9948} & 0.0112          & \textbf{0.9972} & 0.8971          & \textbf{0.0197}  & \textbf{0.0029} &
-\changed{
 \textbf{0.0441}
-}
 \\
     TPC${}_{\rmn{morph}}$         & 0.9924          & \textbf{0.0109} & 0.9963          & \textbf{0.9268} & 0.0245           & 0.0056 &
-\changed{
 0.0809
-}
 \\
     TPC${}_{\rmn{phot}}$          & 0.9876          & 0.0189          & 0.9927          & 0.8044          & 0.0266           & 0.0101 &
-\changed{
 0.1085
-}
 \\
@@
   \caption{
-\changed{
     The calibration curves for ConvNet (red) and $\rmn{TPC}_{\rmn{morph}}$ (blue)
@@
     $P_{\rmn{class}}$ is the probabilistic outputs generated by the classifiers.
-}
     The dashed line displays the relationship
@@
 We also use the same training and validation sets to train
-\changed{
 and tune the hyperparameters of 
-}
 $\rmn{TPC}_{\rmn{morph}}$ and $\rmn{TPC}_{\rmn{phot}}$, and
@@
 ConvNet outperforms $\rmn{TPC}_{\rmn{morph}}$ in
-\changed{
 five
-}
 metrics
 (AUC, $p_g$, CAL, $|\Delta N_g|/N_g$, 
-\changed{
 and log loss
-}
 ),
@@
 $\rmn{TPC}_{\rmn{phot}}$.
-\sout{ As Figure~\ref{fig:clens_color_color} shows, there is significant overlap between stars and galaxies in color-color space.  }
 Thus, magnitudes and colors alone are not sufficient to separate stars from
@@
 
-\changed{
 Figure~\ref{fig:clens_calibration} shows the calibration curves that compare
@@
 is apparently not as well-calibrated as ConvNet.
-}
 These calibration curves visually confirm the results in
@@
     as applied to the SDSS data.
-\changed{
     To obtain a galaxy completeness of $c_g=0.96$, we choose the threshold values
@@
     classifier & AUC & MSE & $p_{g}(c_g=0.96) $ & $c_{s}(p_s=0.97)$ & CAL & $ |\Delta N_g|/N_g$ &
-\changed{
 log loss
-}
 \\
@@
     ConvNet               & 0.9952          & 0.0182          & 0.9915          & 0.9500          & \textbf{0.0243} & 0.0157 &
-\changed{
 \textbf{0.0731}
-}
 \\
     TPC${}_{\rmn{morph}}$ & \textbf{0.9967} & \textbf{0.0099} & \textbf{0.9977} & \textbf{0.9810} & 0.0254          & \textbf{0.0044} & 
-\changed{
 0.0914
-}
 \\
     TPC${}_{\rmn{phot}}$  & 0.9886          & 0.0283          & 0.9819          & 0.8879          & 0.0316          & 0.0160 & 
-\changed{
 0.1372
-}
 \\
@@
   \caption{
-\changed{
     Calibration curves for ConvNet (red) and $\rmn{TPC}_{\rmn{morph}}$
@@
     }
-    }
   \label{fig:sdss_calibration}
@@
   \caption{
-\changed{
     Similar to Figure~\ref{fig:galaxy_activations} but for a galaxy in the
@@
     }
-    }
   \label{fig:sdss_galaxy_activations}
@@
   \caption{
-\changed{
     Similar to Figure~\ref{fig:sdss_galaxy_activations} but for a star in the
     SDSS data set.
-}
     }
@@
 in all metrics except $\rmn{CAL}$
-\changed{
 and cross-entropy.
-}
 Both ConvNet and $\rmn{TPC}_{\rmn{morph}}$ still outperform
@@
 
-\changed{
 Figure~\ref{fig:sdss_calibration} shows
 the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$.
-}
 The calibration curve of ConvNet in Figure~\ref{fig:sdss_calibration}
@@
 
-\changed{
 Figures~\ref{fig:sdss_galaxy_activations} and \ref{fig:sdss_star_activations}
@@
 features automatically from images.
-}
 
@@
 neural network architectures.
-\changed{
 Futhermore, future work could compare the performance of other deep learning
@@
 multilayer perceptrons~\citep{wasserman1988neural}.
-}
 
@@
 
-\changed{
 Our ConvNet model is a supervised algorithm, and one of the criticisms
@@
 beyond the limits of spectroscopic training data.
-}
-
-\changed{
+
 Finally, we are currently exploring different strategies for including objects
@@
 The results of this multi-class problem will be presented in subsequent papers.
-}
 
@@
 
-\changed{
 This work has made use of the Theano library
@@
 (http://pythonhosted.org/nolearn/).
-}
 

### 2016-09-29 paper/main.tex
change filename of bib
acknowledge and thank referees
fix typos

@@
 
-Using the CasJobs server, we randomly select a total of 65,000 sources, which are either stars or galaxies.
+Using the CasJobs server, we randomly select a total of 65,000 sources,
+which are either stars or galaxies.
+\changed{
+We exclude quasars, as they clearly are neither stars nor galaxies and many of
+them have one or more saturated pixels in the images.
+}
 We exclude some bad photometric observations as follows.
@@
 layers, while monitoring the validation loss;
-we stop at eight convolutoinal layers after we find that adding more layers
+we stop at eight 
+\changed{
+convolutional
+}
+layers after we find that adding more layers
 leads to worse performance.
@@
 and star-galaxy classification~\citep{kim2015hybrid};
+\sout{
 it adds an extra layer of randomness by perturbing the measured attributes by
 their uncertainties;
+}
 and it uses parallelism to handle large data sets on distributed memory systems.
@@
     (d) Activations on the sixth convolutional layer.
-    Each image in (a), (b), and (c) is a feature map corresponding to the
+    Each image in 
+\changed{
+(b), (c), and (d)
+}
+is a feature map corresponding to the
     output for one of the learned features.
@@
 
+The authors thank the referee for a careful reading of the manuscript
+and comments that improved this work.
 We acknowledge support from the 
@@
 \bibliographystyle{mnras}
-\bibliography{sg_paper}
+\bibliography{main}
 

### 2016-10-04 paper/main.tex
add footnote on qsos

@@
 the star-galaxy classification problem include decision 
-trees~\citep{weir1995automated,suchkov2005census,ball2006robust,sevilla2015effect}, 
+trees~\citep{weir1995automated,suchkov2005census,ball2006robust,vasconcellos2011decision,sevilla2015effect}, 
 Support Vector Machines~\citep{Fadely2012}, and
@@
 Using the CasJobs server, we randomly select a total of 65,000 sources,
-which are either stars or galaxies.
+which are either stars or galaxies.\footnote{
 \changed{
-We exclude quasars, as they clearly are neither stars nor galaxies and many of
-them have one or more saturated pixels in the images.
+We exclude objects that clearly are neither stars nor galaxies.
+Most of the excluded objects are QSOs or quasars.
+Quasars appear as point sources, rather than resolved sources similar to
+galaxies,
+and many of them have one or more saturated pixels in the images.
+They are also different from galaxies because of their intrinsic variability on
+a wide range of time scales, which may be due to variation in the accretion rate
+or instabilities of the accretion disk around the black hole
+\citep{popovic2012photocentric}.
+However, unlike any known stars, their spectra show strong and broad emission
+lines.
+Thus, many studies exclude quasars in the binary star-galaxy classification
+scheme
+\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
+Expanding the historical star-galaxy classification problem to include
+other classes may have advantanges~\citep{ball2006robust}, and we defer
+the results of this multi-class problem to a future paper.}
 }

### 2016-10-04 paper/main.tex
update paper

@@
 Using the CasJobs server, we randomly select a total of 65,000 sources,
-which are either stars or galaxies.\footnote{
+which are either stars or galaxies.
 \changed{
-We exclude objects that clearly are neither stars nor galaxies.
+In this work, we exclude objects that clearly are neither stars nor galaxies.
 Most of the excluded objects are QSOs or quasars.
@@
 and many of them have one or more saturated pixels in the images.
-They are also different from galaxies because of their intrinsic variability on
-a wide range of time scales, which may be due to variation in the accretion rate
-or instabilities of the accretion disk around the black hole
-\citep{popovic2012photocentric}.
 However, unlike any known stars, their spectra show strong and broad emission
 lines.
+Quasars are also different from galaxies because of their intrinsic variability
+on a wide range of time scales, which may be due to variation in the accretion
+rate or instabilities of the accretion disk around the black hole
+\citep{popovic2012photocentric}.
 Thus, many studies exclude quasars in the binary star-galaxy classification
-scheme
-\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
+scheme~\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
 Expanding the historical star-galaxy classification problem to include
-other classes may have advantanges~\citep{ball2006robust}, and we defer
-the results of this multi-class problem to a future paper.}
+additional classes, \eg \textit{nsng} (neither star nor galaxy),
+may have advantanges~\citep{ball2006robust}, and we plan to present
+the results of this multi-class problem in a future paper.
 }
-We exclude some bad photometric observations as follows.
+
+We also exclude some bad photometric observations as follows.
 We consider only objects

### 2016-10-04 paper/main.tex
update paper

@@
 additional classes, \eg \textit{nsng} (neither star nor galaxy),
-may have advantanges~\citep{ball2006robust}, and we plan to present
+may have advantages~\citep{ball2006robust}, and we plan to present
 the results of this multi-class problem in a future paper.

### 2016-10-05 paper/main.tex
remove colors and strikeout

@@
 which are either stars or galaxies.
-\changed{
 In this work, we exclude objects that clearly are neither stars nor galaxies.
@@
 the results of this multi-class problem in a future paper.
-}
 
@@
 layers, while monitoring the validation loss;
-we stop at eight 
-\changed{
-convolutional
-}
-layers after we find that adding more layers
+we stop at eight convolutional layers after we find that adding more layers
 leads to worse performance.
@@
 and star-galaxy classification~\citep{kim2015hybrid};
-\sout{
-it adds an extra layer of randomness by perturbing the measured attributes by
-their uncertainties;
-}
 and it uses parallelism to handle large data sets on distributed memory systems.
@@
     (d) Activations on the sixth convolutional layer.
-    Each image in 
-\changed{
-(b), (c), and (d)
-}
-is a feature map corresponding to the
+    Each image in (b), (c), and (d) is a feature map corresponding to the
     output for one of the learned features.
